% Coherence Calculus -- main document

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[expansion=false]{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,calc,matrix}
\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{booktabs}
\usepackage{xcolor}

\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}
\newcolumntype{P}[1]{>{\RaggedRight\arraybackslash}p{#1}}

\makeatletter
\def\toclevel@section{2}
\def\toclevel@subsection{3}
\def\toclevel@subsubsection{4}
\renewcommand*\l@part[2]{%
  \ifnum \c@tocdepth >-2\relax
    \addpenalty{-\@highpenalty}%
    \addvspace{1.0em \@plus\p@}%
    \begingroup
      \parindent\z@
      \rightskip \@pnumwidth
      \parfillskip -\@pnumwidth
      \leavevmode
      \bfseries #1\hfil \hb@xt@\@pnumwidth{\hss #2}\par
    \endgroup
  \fi
}
\makeatother

% ---------------------------
% TikZ diagram styles (monochrome, compact)
% ---------------------------
\tikzset{
  ccnode/.style={draw, rounded corners=2pt, inner sep=4pt, font=\small},
  ccbox/.style={draw, rectangle, rounded corners=2pt, inner sep=5pt, font=\small},
  ccarrow/.style={-{Latex[length=2mm]}, thin},
  ccdarrow/.style={-{Latex[length=2mm]}, dashed, thin},
  ccband/.style={draw, fill=black!8, rounded corners=1pt},
  cclabel/.style={font=\scriptsize, midway},
}

% ---------------------------
% Theorem environments
% ---------------------------
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{law}{Law}
\newtheorem{example}{Example}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
% Diophantine foundations
\theoremstyle{definition}
\newtheorem{primitive}{Primitive}
\newtheorem{axiom}{Axiom}

% ---------------------------
% Notation shortcuts
% ---------------------------
\newcommand{\HBC}{\textsc{hbc}}
\newcommand{\Obs}{\mathrm{Obs}}
\newcommand{\Sh}{\mathrm{Sh}}
\newcommand{\id}{\mathrm{id}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\Ker}{\mathrm{Ker}}
\newcommand{\Img}{\mathrm{Im}}
\newcommand{\Span}{\mathrm{span}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbN}{\mathbb{N}}
\newcommand{\bbQ}{\mathbb{Q}}
\newcommand{\bbZ}{\mathbb{Z}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cX}{\mathcal{X}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cB}{\mathcal{B}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COHERENCE CALCULUS MACRO API (DO NOT INLINE OPERATIONS)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% All core operations must use these macros for consistency.
% Direct notation like \Pi_h, \bar\Pi_h, d_h, etc. should NOT appear in math mode.
%
% --- A) Horizon projections / complements / increments ---
\newcommand{\CCPi}[1]{\Pi_{#1}}                      % horizon projection
\newcommand{\CCPibar}[1]{\bar{\Pi}_{#1}}             % shadow projection (complement)
\newcommand{\CCDelta}[1]{\Delta_{#1}}                % increment projector
\newcommand{\CCHobs}[1]{\cH_{\le #1}}                % observable subspace at h
\newcommand{\CCHsh}[1]{\cH_{> #1}}                   % shadow subspace at h
%
% --- B) Observed/restricted operator constructors ---
\newcommand{\CCRestr}[2]{\CCPi{#2}\, #1 \,\CCPi{#2}} % horizon restriction: Pi_h A Pi_h
\newcommand{\CCObs}[2]{#1_{#2}}                      % observed operator notation: d_h
%
% --- C) Leakage / defect / energies ---
\newcommand{\CCLeak}[2]{B_{#2}}                      % leakage operator: B_h = \bar\Pi_h d \Pi_h
\newcommand{\CCLeakExpr}[2]{\CCPibar{#2}\, #1 \,\CCPi{#2}} % explicit leakage expression
\newcommand{\CCDefect}[2]{\delta_{#2}}               % defect operator: delta_h
\newcommand{\CCDefectExpr}[2]{\CCPi{#2}\, #1 \,\CCPibar{#2}\, #1 \,\CCPi{#2}} % explicit
\newcommand{\CCDefEnergy}[2]{\Gamma_{#1}(#2)}        % defect energy: Gamma_h(x)
\newcommand{\CCDefOp}[2]{L_{#2}}                     % defect operator L_h = B_h^* B_h
%
% --- D) Coherence defect for maps ---
\newcommand{\CCTau}[3]{\tau_{#1}(#2;\, #3)}          % tau_h(F; x)
\newcommand{\CCTauBi}[4]{\tau_{#1}(#2;\, #3, #4)}    % tau_h(B; x, y) for bilinear
%
% --- E) Tower calculus (scale index, derivative, antiderivative) ---
\newcommand{\CCIndexOp}{N}                           % scale index operator
\newcommand{\CCDer}[1]{\partial(#1)}                 % tower derivative: partial(A)
\newcommand{\CCComm}[2]{[#1,\, #2]}                  % commutator: [X, Y]
\newcommand{\CCDiag}[1]{\mathrm{Diag}(#1)}           % diagonal part
\newcommand{\CCOffDiag}[1]{\mathrm{OffDiag}(#1)}     % off-diagonal part
\newcommand{\CCInt}[1]{\mathcal{I}(#1)}              % tower antiderivative
\newcommand{\CCBlock}[3]{#1_{#2 #3}}                 % block notation: A_{hk}
%
% --- F) Horizon flow (finite difference, distinct from increment projector) ---
\newcommand{\CCFlow}[2]{\nabla_{#2} #1}              % horizon flow: nabla_h A
%
% --- G) Schur complement / resolvent ---
\newcommand{\CCSigma}[2]{\Sigma_{#1}(#2)}            % Schur correction: Sigma_h(z)
\newcommand{\CCRes}[2]{(I - #2 \cdot #1)^{-1}}       % resolvent: (I - zA)^{-1}
%
% --- H) Traces ---
\newcommand{\CCHTrace}[2]{\mathrm{Tr}_{#1}(#2)}      % horizon trace: Tr_h(A)
%
% --- I) Shadow commutator ---
\newcommand{\CCShadowComm}[2]{\mathcal{S}_{#2}(#1)}  % shadow commutator: S_h(A)
%
% --- J) Leakage correction for products ---
\newcommand{\CCLeakCorr}[3]{\mathrm{Leak}_{#1}(#2,\, #3)} % Leak_h(A, B)
%
% --- K) Solver layer (Hilbert complexes, Hodge, Green, homotopy) ---
\newcommand{\CCLap}[1]{\mathcal{L}_{#1}}                   % Hodge Laplacian at degree k (script L avoids collision with \CCDelta)
\newcommand{\CCGreen}[1]{G_{#1}}                          % Green operator at degree k
\newcommand{\CCHom}[1]{K_{#1}}                            % Homotopy/integration operator
\newcommand{\CCHarm}[1]{P_{\mathrm{harm},#1}}             % Harmonic projector at degree k
\newcommand{\CCCoh}[1]{H^{#1}}                            % Cohomology at degree k
\newcommand{\CCCohRel}[2]{H^{#1}(#2)}                     % Relative cohomology H^k(D,R)
%
% --- L) Field-induced horizons and split transform ---
\newcommand{\CCField}{\mathsf{F}}                          % Field operator (self-adjoint)
\newcommand{\CCSpProj}[2]{\mathbf{1}_{#2}(#1)}            % Spectral projector: 1_S(F)
\newcommand{\CCComp}{Q}                                    % Complement projector (I - P)
\newcommand{\CCBlockPP}[1]{#1_{PP}}                       % PP block
\newcommand{\CCBlockPQ}[1]{#1_{PQ}}                       % PQ block (P -> Q transport)
\newcommand{\CCBlockQP}[1]{#1_{QP}}                       % QP block (Q -> P transport)
\newcommand{\CCBlockQQ}[1]{#1_{QQ}}                       % QQ block
\newcommand{\CCSigmaP}[2]{\Sigma_{#1}(#2)}                % Schur correction for projection P: Sigma_P(z)
\newcommand{\CCAeff}[2]{#1_{\mathrm{eff},#2}}             % Effective operator: A_{eff,P}
\newcommand{\CCSplit}[3]{\mathrm{Split}_{#1}(#2;\,#3)}    % Split transform: Split_P(A; z)
\newcommand{\CCGrass}[1]{\mathcal{P}_{#1}}                % Grassmannian of rank-r projections
\newcommand{\CCDesign}[1]{J(#1)}                          % Design objective functional
%
% --- M) Residual signature ---
\newcommand{\CCTransIn}[1]{T_{\mathrm{in}}^{#1}}          % Transport in: A_PQ
\newcommand{\CCTransOut}[1]{T_{\mathrm{out}}^{#1}}        % Transport out: A_QP
%
% --- N) Certificate labels (for cross-referencing) ---
\newcommand{\CertA}{\textbf{(Cert-A)}}                    % Perfect coherence / zero residual
\newcommand{\CertB}{\textbf{(Cert-B)}}                    % Solver exactness H^k(D)=0
\newcommand{\CertC}{\textbf{(Cert-C)}}                    % Holographic saturation
%
% --- O) Lean 4 formalization references ---
% These macros link LaTeX definitions/theorems to their Lean counterparts.
% Usage: \lean{CoherenceCalculus.HorizonTower} after a \label{}
% Usage: \uses{def:horizon, def:shadow} to declare dependencies
\newif\ifshowleanlabels
\showleanlabelsfalse
% Set \showleanlabelstrue for internal audit builds that should render Lean tags.
\newcommand{\lean}[1]{\ifshowleanlabels\marginpar{\tiny\textsf{Lean: \detokenize{#1}}}\fi}
\newcommand{\leaninline}[1]{\ifshowleanlabels{\footnotesize\textsf{[Lean: \detokenize{#1}]}}\fi}
\newcommand{\uses}[1]{}                                    % Dependencies (parsed by dashboard)
\newcommand{\leanstatus}[1]{%                              % Status indicator
  \ifx#1p\textcolor{green!70!black}{$\checkmark$}\fi%      % p = proved
  \ifx#1s\textcolor{orange}{$\circ$}\fi%                   % s = sorry
  \ifx#1a\textcolor{blue}{$\bullet$}\fi%                   % a = axiom
}
\newcommand{\manuscriptchapter}[2]{%
  \clearpage
  \phantomsection
  \pdfbookmark[1]{#2}{chap.#1}%
  \addtocontents{toc}{\protect\contentsline {section}{Chapter #1: #2}{\thepage}{\csname @currentHref\endcsname}}%
  \begin{center}
    \Large\bfseries Chapter #1: #2
  \end{center}
  \vspace{0.5em}
}
\newcommand{\manuscriptpart}[2]{%
  \clearpage
  \phantomsection
  \pdfbookmark[0]{#1}{#2}%
  \addtocontents{toc}{\protect\contentsline {part}{#1}{\thepage}{\csname @currentHref\endcsname}}%
  \begin{center}
    \LARGE\bfseries #1
  \end{center}
  \vspace{0.75em}
}
\newcommand{\manuscriptappendix}[1]{%
  \clearpage
  \refstepcounter{section}%
  \setcounter{subsection}{0}%
  \setcounter{subsubsection}{0}%
  \setcounter{paragraph}{0}%
  \setcounter{subparagraph}{0}%
  \phantomsection
  \pdfbookmark[1]{Appendix \thesection: #1}{appendix.\thesection}%
  \addtocontents{toc}{\protect\contentsline {section}{\protect\numberline{\thesection}#1}{\thepage}{\csname @currentHref\endcsname}}%
  \begingroup
    \edef\x{\endgroup
      \noexpand\gdef\noexpand\@currentlabelname{#1}}%
  \x
  \begin{center}
    \Large\bfseries Appendix \thesection: #1
  \end{center}
  \vspace{0.5em}
}
%
% --- Legacy aliases (for transition; avoid in new code) ---
\newcommand{\PiH}{\CCPi{h}}
\newcommand{\PiHp}{\CCPi{h'}}
\newcommand{\PibarH}{\CCPibar{h}}
\newcommand{\PibarHp}{\CCPibar{h'}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Git version (injected by build.sh; not shown in rendered PDF)
\ifdefined\githash\else\def\githash{dev}\fi

\title{Coherence Calculus:\\
An Operator Calculus for Finite Observability under Horizon Projections}
\author{Charles Rodbourn Cook}
\date{April 2026 - v0.9}

\begin{document}
\maketitle

\begin{abstract}
This monograph studies operator application under finite observability: when a
system is restricted to a horizon, what visible law survives, what defect is
returned from the hidden complement, and which closure classes are forced by
that projection? It develops \emph{Coherence Calculus} as a horizon-based
operator calculus for elimination, returned defect, and scale-law closure. Its
formal spine starts from the stated bedrock declarations and develops the
structural elimination and closure theory on that basis.

Part~I proves the structural calculus and continuum bridge. Starting from the
bedrock declarations, it derives the counting and boundary layers, the
horizon/tower calculus, Schur elimination, solver and selection interfaces,
the horizon complex as the native object of the theory, the carrier-forcing
results, and the continuum bridge culminating in the temporal interface
carried by the unique \(D=3\) residual.

Part~II assumes the explicit three-law physical hypothesis and proves its
carrier-level consequences. The three laws are temporal realization on the
faithful selected cut, terminal exactification on fixed selected bridges, and
endpoint completion on the fixed four-state local assembly. From that
hypothesis it derives the coherent selected-cut
realization and the exact physical field. Under the later endpoint-rigidity
and representative hypotheses used for carrier identification, it further
derives the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
Einstein equations as carrier realizations of one common selected state-field
law on one same selected realization, together with the classification theorem
that the complete fundamental set on the present intrinsic family consists of
the three primitive direct channels together with the unique geometric lift of
the primitive \(3\)-channel. Those equations are proved on one same selected
realization, not as four independent starting laws. Hydrodynamic and
thermodynamic laws are then read as
effective closures of unresolved return.

These standard equation forms are proved conditionally on the explicit
three-law Part~II hypothesis and the later endpoint-rigidity and
representative hypotheses used for carrier identification, not from Part~I
alone and not from the first two laws alone. A separate Lean~4 development
certifies the rebuilt bedrock-and-tower spine and audits the separate PartIII
and PartIV developments independently. The present scope does not yet include
coupling constants, mass ratios, or the particle spectrum.
\end{abstract}

\begin{tcolorbox}[colback=white, colframe=black!70, title={Claim Boundary}]
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabularx}{\linewidth}{@{}P{0.40\linewidth}Y@{}}
\textbf{Layer} & \textbf{Status} \\
\midrule
Part~I structural spine & proved from the stated bedrock declarations, up to the explicit hypotheses that remain local in the counting-to-terminality bridge and the later continuum interfaces \\
Part~II physical hypothesis & assumed as the explicit three-law hypothesis of temporal realization, terminal exactification, and endpoint completion \\
Part~II derived consequences & proved from that three-law hypothesis: coherent selected-cut realization, fixed-bridge exactification, endpoint-complete microscopic structure, and the exact physical field; with the later endpoint-rigidity and representative hypotheses used for carrier identification, one common selected state-field law on one same selected realization and the recognizable carrier-level equation forms as realizations of that same law \\
Fundamental/effective boundary & proved on the current intrinsic family: the three primitive direct laws together with the unique geometric lift are fundamental, while hydrodynamic and thermodynamic laws are effective closures \\
Auxiliary completion-side formulation & retained as an alternative completion-side formulation on the same selected data; it is not the hypothesis of the proved Part~II theorems and the standard equations no longer depend on it \\
Open items & whether endpoint completion is independent of the first two laws, and the quantitative data of coupling constants, mass ratios, and particle spectrum \\
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[colback=white, colframe=black!70, title={First-Pass Synopsis}]
\footnotesize
\begin{description}[leftmargin=1.9em, itemsep=0.3em]
\item[Core object.] The recurring object is the horizon complex together with
      the visible law induced on an observed bundle after eliminating the
      hidden complement.
\item[Part~I proves.] The structural calculus and continuum bridge: counting
      and boundary layers, horizon/tower calculus, Schur elimination, the
      horizon complex, carrier forcing, and the temporal interface carried by
      the unique \(D=3\) residual.
\item[Part~II assumes.] The explicit three-law physical hypothesis: temporal
      realization, terminal exactification, and endpoint completion.
\item[Part~II proves.] The coherent selected-cut realization, the exact
      physical field, and, with the later endpoint-rigidity and
      representative hypotheses used for carrier identification, one common
      selected state-field law on one same selected realization, the
      recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and Einstein
      forms as carrier realizations of that same law, and the scoped
      complete-fundamental-set theorem on the present intrinsic family.
\item[Not claimed.] The Part~II theorems are not derived from Part~I alone and
      not from the first two laws alone. The present scope does not yet derive
      coupling constants, mass ratios, the particle spectrum, or any named
      phenomenology for nonzero returned remainders.
\item[Dependency spine.] Bedrock declarations \(\to\) structural calculus
      \(\to\) carrier forcing \(\to\) continuum bridge \(\to\) explicit
      three-law physical hypothesis \(\to\) selected-cut realization and exact
      physical field \(\to\) carrier realizations and the scoped
      complete-fundamental-set theorem.
\end{description}
\end{tcolorbox}

\begin{tcolorbox}[colback=white, colframe=black!70, title={Falsifiability, Empirical Stakes, and Portability}]
\footnotesize
\begin{description}[leftmargin=1.9em, itemsep=0.3em]
\item[Structural falsifiers.] On the present scope, the framework is falsified
      by any genuinely fourth primitive direct carrier, any geometric law
      algebraically independent of the unique lift of the primitive
      \(3\)-channel, any primitive visible creation on a closed selected
      sector, or any fluid law that is fundamental rather than effective.
\item[Model-dependent predictions.] Once a concrete realized cut is fixed, the
      returned-remainder theorems furnish exact correction slots around the
      leading Schr\"odinger, wave/Klein--Gordon, Maxwell, Einstein, and
      hydrodynamic forms.
\item[Not yet claimed.] The present scope does not yet give universal
      numerical values for coupling constants, mass ratios, or the particle
      spectrum, and it does not identify named phenomenology for nonzero
      returned remainders in advance.
\item[Portability.] The Part~II law surface is stated at the exported
      interface level: any external host realizing the same ordered-persistence
      datum, faithful cut class, selected visible law, and residual-return
      grammar carries the same Part~II law-side interpretation.
\end{description}
\end{tcolorbox}

\section*{Reader's Guide}
This is an archival monograph. It is not meant to be read linearly on a first
pass.

\begin{description}[leftmargin=1.9em, itemsep=0.35em]
\item[Core object.] The recurring object is the horizon complex together with
      the visible law induced on an observed bundle after eliminating the
      hidden complement. Schur elimination, returned defect, closure
      transport, and the later carrier realizations are all organized around
      that object.
\item[Boundary.] Part~I proves the structural calculus and continuum bridge.
      Part~II assumes the explicit three-law physical hypothesis and proves
      its carrier-level consequences on one same selected realization.
      Hydrodynamic and thermodynamic laws are treated here as effective
      closures, not as additional fundamental laws.
\item[Read first.] For a first pass, read the abstract, this claim-boundary
      table, the first-pass synopsis, Chapters~5--6 for elimination and defect
      transport, Chapter~9 for the continuum bridge, Chapter~10 for the
      Part~II hypothesis and closure theorem, Chapter~12 for the carrier
      realizations and classification theorem, and Chapter~16, especially the
      falsifiability and empirical-stakes subsection.
\item[Can skip first.] On a first pass, the longer appendix decompositions, the
      more detailed carrier-specific derivations, and the Lean tags may be
      deferred. The tags are audit metadata, not part of the mathematical
      prose.
\item[What remains open.] The main structural open problem is whether endpoint
      completion is independent of temporal realization and terminal
      exactification. The main quantitative open problems are coupling
      constants, mass ratios, and the particle spectrum.
\end{description}

\tableofcontents

% ============================================================
% PART I: MATHEMATICS FROM LOGICAL BEDROCK
% ============================================================
\manuscriptpart{Part I: Mathematics from Logical Bedrock}{part.i}

Part~I develops the structural calculus used later, but it does so without
assuming a physical law. Chapters~1--4 derive the counting and boundary
layers: signed-count arithmetic, the canonical finite realization, the
boundary operator~$d$ with $d^2=0$, the horizon tower, and the intrinsic
$1{+}2{+}3$ decomposition under the~$S_4$ action. Chapters~5--6 develop the
horizon/tower calculus, Schur elimination, solver and selection interfaces,
and the horizon complex as the native object on which the later bridge and
physical fields live. Chapters~7--9 then force the carrier taxonomy, close the
intrinsic carrier grammar, and complete the continuum bridge culminating in
the derived temporal interface.

\manuscriptchapter{1}{Distinction}
\input{sections/ch1_distinction}

\manuscriptchapter{2}{From Distinction to Counting}
\input{sections/ch2_counting}

\manuscriptchapter{3}{From Composites to $\partial^2=0$}
\input{sections/ch3_boundary}

\manuscriptchapter{4}{From the Balanced Dimension to $K_4$}
\input{sections/ch4_balanced_dimension}

\manuscriptchapter{5}{The Operator Interface}
\input{sections/orientation}
\input{sections/positioning}
\input{sections/bedrock}
\input{sections/foundational_lemmas}
\input{sections/hft}
\input{sections/tower_calculus}
\input{sections/defect_rules}
\input{sections/constraint_compiler}
\input{sections/admissibility}

\manuscriptchapter{6}{Elimination and Solvers}
\input{sections/field_induced_horizons}
\input{sections/resolvent_defect}
\input{sections/observable_relative_closure}
\input{sections/realization_calculus}
\input{sections/solver_layer}
\input{sections/targets}
\input{sections/projector_calculus}
\input{sections/complex_compatibility}
\input{sections/holographic_defect}
\input{sections/coherence_gap}
\input{sections/log_periodic}

\manuscriptchapter{7}{From $\partial^2=0$ to the Carrier Taxonomy and Persistence Modes}
\input{sections/ch7_carrier_forcing}

\manuscriptchapter{8}{The Intrinsic Carriers}
\section{Intrinsic Laws on the Selected Cut}
\label{sec:intrinsic-visible-laws}
This chapter treats the intrinsic visible laws whose leading form is already
fixed once the earlier carrier-forcing and endpoint-rigidity theorems are in
place: the three primitive channels (local-state, propagative, and
comparative) together with the canonical geometric lift of the primitive
\(3\)-channel. Their full physical reading is taken up in Part~II; here the
focus is the intrinsic carrier-level normal forms themselves rather than any
effective constitutive closure.
\input{sections/flagship_quantum}
\input{sections/flagship_wave}
\input{sections/flagship_gauge}
\input{sections/flagship_geometry}

\manuscriptchapter{9}{From the Discrete to the Continuum}
\input{sections/classical_limit_bridge}
\input{sections/continuum_identification}

% ============================================================
% PART II: PHYSICAL DYNAMICS FROM THE TEMPORAL REALIZATION LAW
% ============================================================
\manuscriptpart{Part II: Physical Dynamics under the Three-Law Physical Hypothesis}{part.ii}

Part~I proves the structural calculus and continuum bridge. Part~II assumes
the explicit three-law physical hypothesis and proves its carrier-level
consequences. The three laws are temporal realization on the faithful visible
cut, terminal exactification on fixed selected bridges, and endpoint
completion on the fixed four-state local assembly. Chapter~10 states that
hypothesis and derives the coherent realization, fixed-bridge exactification,
and endpoint-complete microscopic structures that it determines.
Chapter~11 records the common selected-cut structure and the universal
consequences that already follow before any carrier-specific realization is
taken. Chapter~12 identifies the canonical carrier realizations and proves the
scoped complete-fundamental-set theorem: within the current intrinsic family,
the only fundamental laws are the three primitive direct channels together
with the unique geometric lift.
Chapter~13 supplies the characteristic realization of that same structure.
Chapter~14 collects the hydrodynamic and thermodynamic effective closures.
Chapter~15 isolates the external interface on which the same Part~II
hypothesis may be read.

The temporal interface derived in Part~I becomes causal before/after on the
realized cut class. On that class one selected observed bundle carries one
exact visible law, visible source is interpreted only as balanced exchange or
returned residual of that same bundle, and no independent constitutive
completion is admitted. Terminal exactification then fixes the bridge-local
exactified assembly, and endpoint completion closes that same assembly with no
further hidden stage. The recognizable Schr\"odinger, wave/Klein--Gordon,
Maxwell, and Einstein equations are proved under that explicit three-law
hypothesis. The auxiliary completion-side normal form gives an alternative
presentation on the same selected data, while the
fundamental/effective classification theorem states what is intrinsic and what
remains effective on the present scope.

\manuscriptchapter{10}{The Three-Law Physical Hypothesis: Temporal Realization, Terminal Exactification, and Endpoint Completion}
\input{sections/ch10_physical_dynamics}

\manuscriptchapter{11}{Selected-Cut Consequences of the Three-Law Hypothesis}
\input{sections/ch11_temporal_realization}

\manuscriptchapter{12}{Endpoint Completion, Carrier Realizations, and Classification}
\input{sections/ch12_carrier_faces}

\manuscriptchapter{13}{Characteristic Realization}
\input{sections/bridge_program}

\manuscriptchapter{14}{Hydrodynamic and Thermodynamic Effective Closures}
\section{Effective Closures and Thermodynamic Forms}
\label{sec:effective-constitutive-closures}
This section collects the laws whose recognizable forms appear only after an
unresolved hierarchy has been compressed to a selected-cut endpoint. They are
therefore effective rather than fundamental on the present scope. The
hydrodynamic law is the main example: the exact object is the
collision-invariant moment hierarchy, while the Navier--Stokes form is its
isotropic endpoint closure after higher-moment return has been integrated out.
On the same selected bundle, residual-return bookkeeping forces a canonical
thermodynamic state space on the selected tower, together with
entropy-production and equilibrium laws. Both theories are physical, but neither
introduces a new primitive direct channel or a new intrinsic lift.
\input{sections/flagship_hydrodynamics}
\input{sections/flagship_thermodynamics}

\manuscriptchapter{15}{External Realizations of the Pre-Dynamical Interface}
\input{sections/interface_portability}

% ============================================================
% CONCLUSION
% ============================================================
\manuscriptchapter{16}{Synthesis and Open Frontier}
\input{sections/discussion}

% ============================================================
% APPENDICES
% ============================================================
\appendix
\makeatletter
\def\toclevel@subsection{2}
\def\toclevel@subsubsection{3}
\makeatother
\manuscriptpart{Appendices}{part.appendices}

The first group of appendices (A--G) collects proofs that have been moved from
the main text to keep the derivation chain readable. Each proof is labeled and
cross-referenced from the theorem statement it supports. The second group
collects supplementary operator-theoretic extensions and the formal
certification boundary.

\manuscriptappendix{Foundations Proofs (Chapters 1--2)}
\input{sections/appendix_foundations_proofs}

\manuscriptappendix{Topology and Dimension Proofs (Chapters 3--4)}
\input{sections/appendix_topology_dimension_proofs}

\manuscriptappendix{Tower Calculus Proofs (Chapter 5)}
\input{sections/appendix_tower_proofs}

\manuscriptappendix{Elimination and Solver Proofs (Chapter 6)}
\input{sections/appendix_elimination_proofs}

\manuscriptappendix{Carrier Forcing Proofs (Chapters 7--8)}
\input{sections/appendix_carrier_proofs}

\manuscriptappendix{Part I Continuum Bridge Proofs (Chapter 9)}
\input{sections/appendix_continuum_proofs}

\manuscriptappendix{Part II Physical Dynamics Proofs (Chapters 10--16)}
\input{sections/appendix_dynamics_proofs}

\manuscriptappendix{Advanced Operators}
\input{sections/advanced_operators}
\manuscriptappendix{Advanced Operators II: Symmetry, Entropy, Topology, Stability}
\input{sections/advanced_operators_ii}
\manuscriptappendix{Advanced Operators III: Principal Angles, Field Filters, Unitary Splittings}
\input{sections/advanced_operators_iii}
\manuscriptappendix{Advanced Operators IV: Orthogonality, Shadow Commutators, Interference}
\input{sections/advanced_operators_iv}
\manuscriptappendix{Kernel Defect and Constraint Maps}
\input{sections/boundary}
\manuscriptappendix{Oblique Horizons (Petrov--Galerkin Observation)}
\input{sections/appendix_oblique_horizons}
\manuscriptappendix{Continuous Resolution via Spectral Horizon Families}
\input{sections/appendix_continuous_spectral_horizons}
\manuscriptappendix{Trace-Level Coherence Laws}
\input{sections/appendix_trace_level_coherence_laws}
\manuscriptappendix{Formal Certification Boundary and Separate Lean/mathlib Validation Realizations}
\input{sections/appendix_formal_certification}

\clearpage
\phantomsection
\addcontentsline{toc}{part}{References}
\input{sections/references}

\end{document}
