% Appendix F: Part I Continuum Bridge Proofs (Chapter 9)
\label{sec:appendix-continuum}

% --- Proofs from classical_limit_bridge.tex ---

\begin{proof}[Proof of Proposition~\ref{prop:faithful-operator-recovery}]
\label{proof:prop:faithful-operator-recovery}
Fix $x\in\mathcal D(d)$ and set $y_h:=d\CCPi{h}x$. By hypothesis,
$y_h\to y:=dx$. Since each $\CCPi{h}$ is an orthogonal projection,
\[
\|\CCPibar{h}y_h\|
\le
\|\CCPibar{h}(y_h-y)\|+\|\CCPibar{h}y\|
\le
\|y_h-y\|+\|\CCPibar{h}y\|.
\]
The first term tends to zero because $y_h\to y$, and the second tends to zero
by faithfulness applied to $y\in\cH$. Hence
\[
\|\CCPibar{h}d\CCPi{h}x\|=\|\CCPibar{h}y_h\|\to 0.
\]
Now
\[
\CCObs{d}{h}x-dx
=
\CCPi{h}d\CCPi{h}x-dx
=
(y_h-y)-\CCPibar{h}y_h,
\]
so
\[
\|\CCObs{d}{h}x-dx\|
\le
\|y_h-y\|+\|\CCPibar{h}y_h\|
\to 0.
\]
This proves both claims.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:hilbert-completion}]
\label{proof:thm:hilbert-completion}
The compatible inner products make $\cH_{\mathrm{alg}}$ into a pre-Hilbert
space, whose completion is a separable Hilbert space because it is the closure
of a countable union of finite-dimensional stages. This proves (i), and (ii) is
the standard extension of isometric inclusions to the completion.

For (iii), the nested stage structure implies
\[
\CCHobs{h}\subseteq \CCHobs{h'}
\qquad(h\le h'),
\]
so orthogonal projection satisfies
\[
\CCPi{h}\CCPi{h'}=\CCPi{\min(h,h')}.
\]
Thus $(\CCPi{h})$ is a transitive horizon tower in the sense of
Definition~\ref{def:horizon-tower}.

For (iv), if $x\in\cH_{\mathrm{alg}}$, then $x$ belongs to some stage
$\CCHobs{h_0}$, hence $\CCPi{h}x=x$ for all $h\ge h_0$. Density of
$\cH_{\mathrm{alg}}$ in $\cH_\infty$ and uniform boundedness of orthogonal
projections then imply $\CCPi{h}x\to x$ for every $x\in\cH_\infty$.
\end{proof}

% --- Proofs from continuum_identification.tex ---

\begin{proof}[Proof of Theorem~\ref{thm:continuum-identification}]
\label{proof:thm:continuum-identification}
For (i), let $u\in\cX_0$. By asymptotic consistency,
\[
Lu=\lim_{n\to\infty}E_nL_nP_nu=L'u.
\]
Hence $L=L'$ on $\cX_0$.

For (ii), fix $u\in\cX_0$. Using asymptotic consistency together with the
intertwining hypotheses,
\begin{align*}
SLu
&=
S\Bigl(\lim_{n\to\infty}E_nL_nP_nu\Bigr) \\
&=
\lim_{n\to\infty}SE_nL_nP_nu \\
&=
\lim_{n\to\infty}E_nS_nL_nP_nu \\
&=
\lim_{n\to\infty}E_nL_nS_nP_nu \\
&=
\lim_{n\to\infty}E_nL_nP_n(Su) \\
&=
LSu.
\end{align*}
So any symmetry transported through the discrete family survives the continuum
identification.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:refinement-coherent-core-realization}]
\label{proof:thm:refinement-coherent-core-realization}
Fix \(u\in\cX_0\) and \(n\le m\). By refinement coherence,
\[
P_m u = J_{n,m}P_nu
\qquad\text{and}\qquad
E_n = E_mJ_{n,m}.
\]
Using the intertwining relation from
Definition~\ref{def:refinement-compatible-family},
\[
J_{n,m}L_n = L_mJ_{n,m},
\]
we obtain
\[
E_mL_mP_mu
=
E_mL_mJ_{n,m}P_nu
=
E_mJ_{n,m}L_nP_nu
=
E_nL_nP_nu.
\]
This proves (i).

Statement (i) shows that the formula
\[
L_\sharp u:=E_nL_nP_nu
\]
is independent of \(n\), so \(L_\sharp:\cX_0\to\cX\) is well defined. For
every \(u\in\cX_0\), the sequence \((E_nL_nP_nu)_{n\in\bbN}\) is constant, so
it converges to \(L_\sharp u\). Hence \(L_\sharp\) is asymptotically
consistent with \(\mathcal F\). If \(L:\cX_0\to\cX\) is any other
asymptotically consistent operator, then
Theorem~\ref{thm:continuum-identification}(i) gives \(L=L_\sharp\) on
\(\cX_0\). This proves (ii).

Assume now that \(L_\sharp\) is bounded on \(\cX_0\). Then for every
\(u\in\cX_0\) and every \(n\),
\[
\|E_nL_nP_nu\|_{\cX}
=
\|L_\sharp u\|_{\cX}
\le
\|L_\sharp\|\,\|u\|_{\cX},
\]
so \(\mathcal F\) is stable. Also, for every \(n\),
\[
E_{n+1}L_{n+1}P_{n+1}u-E_nL_nP_nu=0,
\]
so \(\mathcal F\) is summably refinement-consistent with
\(\varepsilon_n=0\). Because \(L_\sharp\) is bounded on the dense subspace
\(\cX_0\), it extends uniquely to a bounded operator \(L_\infty:\cX\to\cX\).
This proves (iii).
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:one-stage-bounded-exact-core-forcing}]
\label{proof:thm:one-stage-bounded-exact-core-forcing}
By Theorem~\ref{thm:refinement-coherent-core-realization}, the exact core law
\[
L_\sharp u:=E_nL_nP_nu
\qquad (u\in\cX_0)
\]
is already well defined and independent of \(n\). In particular, for every
\(u\in\cX_0\),
\[
L_\sharp u
=
E_{n_\ast}L_{n_\ast}P_{n_\ast}u.
\]
The assumed bound at the single stage \(n_\ast\) therefore gives
\[
\|L_\sharp u\|_{\cX}
=
\|E_{n_\ast}L_{n_\ast}P_{n_\ast}u\|_{\cX}
\le
C\|u\|_{\cX}
\qquad (u\in\cX_0).
\]
Thus \(L_\sharp\) is bounded on \(\cX_0\), proving item \emph{(i)}.

Now apply item \emph{(iii)} of
Theorem~\ref{thm:refinement-coherent-core-realization}: because \(L_\sharp\) is
bounded on the dense core, it extends uniquely to a bounded operator
\(L_\infty:\cX\to\cX\), and the family is stable and summably
refinement-consistent with zero refinement defect. Since \(L_\infty\) agrees
with \(L_\sharp\) on \(\cX_0\), the exact identity
\[
E_nL_nP_nu=L_\infty u
\qquad (u\in\cX_0,\ n\in\bbN)
\]
holds for every reconstructed stage. This proves item \emph{(ii)}.

If \(L:\cX_0\to\cX\) is any asymptotically consistent operator, then
Theorem~\ref{thm:continuum-identification}(i) applied to \(L\) and
\(L_\infty|_{\cX_0}\) gives
\[
L=L_\infty|_{\cX_0}.
\]
This proves item \emph{(iii)}.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:exact-core-graph-completion}]
\label{proof:thm:exact-core-graph-completion}
By Theorem~\ref{thm:refinement-coherent-core-realization}, the exact core law
\[
L_\sharp u:=E_nL_nP_nu
\qquad (u\in\cX_0)
\]
is well defined and independent of \(n\). Endow \(\cX_0\) with the graph norm
\[
\|u\|_{\mathrm{gr}}=\|u\|_{\cX}+\|L_\sharp u\|_{\cX},
\]
let \(\cX_{\mathrm{gr}}\) be its Banach completion, and let
\(\iota_{\mathrm{gr}}:\cX_0\to\cX_{\mathrm{gr}}\) be the canonical dense
embedding.

For every \(u\in\cX_0\),
\[
\|u\|_{\cX}\le \|u\|_{\mathrm{gr}}.
\]
Hence the identity map \(u\mapsto u\) from \((\cX_0,\|\cdot\|_{\mathrm{gr}})\)
to \(\cX\) is bounded with norm at most \(1\), so it extends uniquely to a
bounded map
\[
I_{\mathrm{gr}}:\cX_{\mathrm{gr}}\to\cX
\]
with \(\|I_{\mathrm{gr}}\|\le 1\) and
\[
I_{\mathrm{gr}}\iota_{\mathrm{gr}}u=u
\qquad (u\in\cX_0).
\]
This proves item \emph{(i)}.

Similarly,
\[
\|L_\sharp u\|_{\cX}\le \|u\|_{\mathrm{gr}}
\qquad (u\in\cX_0),
\]
so \(L_\sharp:(\cX_0,\|\cdot\|_{\mathrm{gr}})\to\cX\) is bounded with norm at
most \(1\). It therefore extends uniquely to a bounded map
\[
\overline L:\cX_{\mathrm{gr}}\to\cX
\]
with \(\|\overline L\|\le 1\) and
\[
\overline L\,\iota_{\mathrm{gr}}u=L_\sharp u
\qquad (u\in\cX_0).
\]
Because \(L_\sharp u=E_nL_nP_nu\) for every \(n\), item \emph{(ii)} follows.

Now assume \(Y\), \(J\), \(C\), \(I\), and \(G\) satisfy the hypotheses of
item \emph{(iii)}. The inequality
\[
\|Ju\|_Y\le C\|u\|_{\mathrm{gr}}
\qquad (u\in\cX_0)
\]
shows that \(J:(\cX_0,\|\cdot\|_{\mathrm{gr}})\to Y\) is bounded. Hence it
extends uniquely to a bounded map
\[
U:\cX_{\mathrm{gr}}\to Y
\]
with
\[
U\iota_{\mathrm{gr}}=J.
\]
For every \(u\in\cX_0\),
\[
I\,U\,\iota_{\mathrm{gr}}u=IJu=u=I_{\mathrm{gr}}\iota_{\mathrm{gr}}u,
\]
so \(I\,U=I_{\mathrm{gr}}\) by density of \(\iota_{\mathrm{gr}}(\cX_0)\).
Likewise,
\[
G\,U\,\iota_{\mathrm{gr}}u=GJu=L_\sharp u
=\overline L\,\iota_{\mathrm{gr}}u,
\]
hence \(G\,U=\overline L\). Uniqueness of \(U\) again follows from density.
This proves item \emph{(iii)}.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:finite-exact-stage-closes-continuum-bridge}]
\label{proof:cor:finite-exact-stage-closes-continuum-bridge}
Because \(\cH_{n_\ast}\) is finite-dimensional, every linear map on
\(\cH_{n_\ast}\) is bounded. In particular, there exists \(M_\ast\ge 0\) such
that
\[
\|L_{n_\ast}x\|_{\cH_{n_\ast}}\le M_\ast\|x\|_{\cH_{n_\ast}}
\qquad (x\in\cH_{n_\ast}).
\]
By Definition~\ref{def:continuum-reconstruction-datum}, the sampling and
reconstruction maps are bounded, so there exist constants \(A_\ast,B_\ast\ge0\)
with
\[
\|P_{n_\ast}u\|_{\cH_{n_\ast}}\le A_\ast\|u\|_{\cX}
\qquad (u\in\cX_0),
\]
\[
\|E_{n_\ast}y\|_{\cX}\le B_\ast\|y\|_{\cH_{n_\ast}}
\qquad (y\in\cH_{n_\ast}).
\]
Therefore
\[
\|E_{n_\ast}L_{n_\ast}P_{n_\ast}u\|_{\cX}
\le
B_\ast M_\ast A_\ast \|u\|_{\cX}
\qquad (u\in\cX_0).
\]
This is exactly the one-stage bound required by
Theorem~\ref{thm:one-stage-bounded-exact-core-forcing}, which then yields the
unique bounded continuum law on \(\cX\).
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:exact-continuum-realization-no-ambiguity}]
\label{proof:cor:exact-continuum-realization-no-ambiguity}
Item \emph{(i)} is exactly
Theorem~\ref{thm:exact-core-graph-completion}(iii).

For item \emph{(ii)}, let \(L_\infty:\cX\to\cX\) be the bounded continuum law
given by Theorem~\ref{thm:one-stage-bounded-exact-core-forcing}. By that
theorem,
\[
L_\infty u=L_\sharp u
\qquad (u\in\cX_0),
\]
where \(L_\sharp\) is the exact core law of
Theorem~\ref{thm:refinement-coherent-core-realization}. Apply
Theorem~\ref{thm:exact-core-graph-completion}(iii) with
\[
Y:=\cX,
\qquad
J:=\mathrm{id}_{\cX_0},
\qquad
I:=\mathrm{id}_{\cX},
\qquad
G:=L_\infty.
\]
The required bound holds because
\[
\|Ju\|_{\cX}=\|u\|_{\cX}\le \|u\|_{\mathrm{gr}}
\qquad (u\in\cX_0),
\]
and the intertwining identities hold because
\[
IJu=u,
\qquad
GJu=L_\infty u=L_\sharp u
\qquad (u\in\cX_0).
\]
Therefore there exists a unique bounded map
\[
U:\cX_{\mathrm{gr}}\to\cX
\]
such that
\[
U\iota_{\mathrm{gr}}=J,
\qquad
I\,U=I_{\mathrm{gr}},
\qquad
G\,U=\overline L.
\]
Since \(I=\mathrm{id}_{\cX}\), the identity \(I\,U=I_{\mathrm{gr}}\) gives
\[
U=I_{\mathrm{gr}}.
\]
Substituting into \(G\,U=\overline L\) yields
\[
L_\infty I_{\mathrm{gr}}=\overline L.
\]
Thus the bounded original-space law is exactly the unique descent of the
canonical graph-completed realization.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:selected-family-continuum-realization}]
\label{proof:thm:selected-family-continuum-realization}
Fix $u\in\cX_0$. For $m>n$, telescoping gives
\[
E_mL_mP_mu-E_nL_nP_nu
=
\sum_{j=n}^{m-1}
\bigl(E_{j+1}L_{j+1}P_{j+1}u-E_jL_jP_ju\bigr).
\]
Hence
\[
\|E_mL_mP_mu-E_nL_nP_nu\|_{\cX}
\le
\Bigl(\sum_{j=n}^{m-1}\varepsilon_j\Bigr)\|u\|_{\cX}.
\]
Because \(\sum_j\varepsilon_j<\infty\), the sequence
\((E_nL_nP_nu)_{n\in\bbN}\) is Cauchy in the Banach space \(\cX\), hence
convergent. This proves (i).

Define
\[
L_\infty u:=\lim_{n\to\infty}E_nL_nP_nu
\qquad (u\in\cX_0).
\]
Linearity follows from linearity of each \(E_nL_nP_n\). Stability gives
\[
\|L_\infty u\|_{\cX}
=
\lim_{n\to\infty}\|E_nL_nP_nu\|_{\cX}
\le
C\|u\|_{\cX}
\qquad (u\in\cX_0).
\]
So \(L_\infty\) is bounded on the dense subspace \(\cX_0\), hence extends
uniquely to a bounded operator \(\cX\to\cX\), still denoted \(L_\infty\). By
construction, the restriction \(L_\infty|_{\cX_0}\) is asymptotically
consistent with \(\mathcal F\). This proves (ii).

If \(L:\cX_0\to\cX\) is any other asymptotically consistent operator, then
Theorem~\ref{thm:continuum-identification}(i) applied to
\(L\) and \(L_\infty|_{\cX_0}\) gives
\[
L=L_\infty|_{\cX_0}
\]
on \(\cX_0\). This proves (iii).
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:stencil-forcing-principle}]
\label{proof:thm:stencil-forcing-principle}
Theorem~\ref{thm:forced-discrete-families} records that the discrete selected
law is already forced at each refinement stage of \(\mathcal F\). By
Theorem~\ref{thm:selected-family-continuum-realization}, hypotheses
\emph{(ii)}--\emph{(iii)} then produce a unique bounded operator
\[
L_\infty:\cX\to\cX
\]
whose restriction to \(\cX_0\) is asymptotically consistent with
\(\mathcal F\). The same theorem also says that no second operator on
\(\cX_0\) can be asymptotically consistent with the same reconstructed
selected laws. Therefore the continuum law carried by \(\mathcal F\) is
forced.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:exact-stencil-forcing-principle}]
\label{proof:thm:exact-stencil-forcing-principle}
Theorem~\ref{thm:forced-discrete-families} records that the discrete selected
law is already forced at each refinement stage of \(\mathcal F\). By
Theorem~\ref{thm:one-stage-bounded-exact-core-forcing}, hypothesis
\emph{(ii)} upgrades the refinement-coherent reconstructed family directly to a
unique bounded operator
\[
L_\infty:\cX\to\cX
\]
whose restriction to \(\cX_0\) is asymptotically consistent with
\(\mathcal F\), and no second asymptotically consistent operator can exist on
\(\cX_0\). Therefore the continuum law encoded by the selected family is
forced on the exact branch.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:continuous-effective-flow}]
\label{proof:thm:continuous-effective-flow}
The map $\ell\mapsto A_{QQ}(\ell)$ is $C^1$ by
Lemma~\ref{lem:continuous-block-derivatives}. Since inversion is $C^1$ on the
open set of invertible operators, the uniform resolvent hypothesis gives
\[
\frac{d}{d\ell}R_{Q,\ell}(z)
=
z\,R_{Q,\ell}(z)\,\frac{d}{d\ell}A_{QQ}(\ell)\,R_{Q,\ell}(z).
\]
Now differentiate
\[
A_{\mathrm{eff},\ell}(z)
=
A_{PP}(\ell)+zA_{PQ}(\ell)R_{Q,\ell}(z)A_{QP}(\ell)
\]
using the product rule and substitute the derivative of the shadow resolvent.
This yields exactly the stated formula.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:characteristic-scale-promotion}]
\label{proof:thm:characteristic-scale-promotion}
For (i), Theorem~\ref{thm:nonlinear-shadow-elimination} identifies full
solutions of $F(u)=0$ in the graph of $\Psi$ with observed solutions of the
effective law
\[
F_{\mathrm{eff}}(p)=PF(u_p)=0.
\]
Since
\[
PF(u_p)=P\mathcal D_\chi u_p + PN(u_p)=F_{\mathrm{prom},P}(p),
\]
the reduced equation is exactly the promoted observed law.

For (ii), let $g\in \mathrm{Ran}(P)$ be smooth. Because $P$ is orthogonal and
$Pg=g$,
\[
\int_U (P\mathcal D_\chi u_p)\,g\,\nu
=
\int_U \mathcal D_\chi u_p\,(Pg)\,\nu
=
\int_U \mathcal D_\chi u_p\,g\,\nu.
\]
Applying Theorem~\ref{thm:characteristic-ibp} with $f=u_p$ gives
\[
\int_U \mathcal D_\chi u_p\,g\,\nu
=
\int_{\partial U}u_p g\,\iota_{\widetilde V}\nu
-
\int_U u_p(\mathcal D_\chi g)\,\nu.
\]
Adding the term $\int_U K_P(p)\,g\,\nu$ yields the stated identity.

Statement (iii) is the special case of (ii) in which $\mathcal D_\chi g=0$.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:admissible-promotion}]
\label{proof:cor:admissible-promotion}
By Theorem~\ref{thm:characteristic-scale-promotion}, each admissible horizon
cut produces a canonically defined promoted observed law. Assumptions (i)--(iii)
place that promoted law inside the finite selection interface of
Theorem~\ref{thm:selection-interface}, and
Corollary~\ref{cor:selection-to-forcing} then yields uniqueness up to
horizon-preserving equivalence at that step. Because $\mathfrak C$ is closed
under promotion, the same argument applies again after each finite number of
steps. An induction on the length of the horizon chain proves the recursive
statement.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:inherited-minimal-order-closure-class}]
\label{proof:cor:inherited-minimal-order-closure-class}
For each \(n\), Corollary~\ref{cor:realized-transport-order-forcing} forces the
distinguished admissible transport-order class on the transport-order
disciplined realized class carrying \(R_n\). Since the minimal-order
admissible subclass is singleton modulo the chosen realized equivalence
relation in that definition, the selected law \(L_n\) lies in that
distinguished class. This proves (a).

Now restrict attention to the refinement-compatible families whose levelwise
selected laws lie in those distinguished admissible minimal-order subclasses.
By part (a), the family \(\mathcal F\) already belongs to that restricted
class. Hypotheses (ii) and (iii) therefore place that restricted family inside
the scope of Theorem~\ref{thm:selected-family-continuum-realization}, which
produces a unique bounded operator \(L_\infty:\cX\to\cX\) asymptotically
consistent with the distinguished minimal-order selected laws. Because the
restricted family was defined using exactly those minimal-order subclasses,
\(L_\infty|_{\cX_0}\) belongs to the inherited distinguished minimal-order
closure class generated by \(\mathcal F\). This proves (b). The uniqueness
statement (c) is the uniqueness clause of
Theorem~\ref{thm:selected-family-continuum-realization} applied to the same
restricted family.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:primitive-support-continuum-spectral-defect}]
\label{proof:cor:primitive-support-continuum-spectral-defect}
Definition~\ref{def:primitive-support-spectral-defect-family} already places
\(\mathcal F_{\mathrm{prim}}\) inside the scope of the selected-family
continuum realization theorem. Hypotheses \emph{(ii)}--\emph{(iii)} are
exactly the stability and summable refinement-consistency assumptions of
Theorem~\ref{thm:selected-family-continuum-realization}, so there is a unique
bounded operator \(L_{\infty}^{\mathrm{prim}}:\cX\to\cX\) asymptotically
consistent with the reconstructed primitive-support family. Hypothesis
\emph{(iv)} says that every reconstructed stage law is self-adjoint and
positive semidefinite; these properties pass to the limit on the dense test
domain \(\cX_0\). Therefore the displayed quadratic form is well defined and is
the continuum spectral defect form forced by the primitive-support tower.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:scalar-recursion-identifies-continuum-generator}]
\label{proof:thm:scalar-recursion-identifies-continuum-generator}
Apply Theorem~\ref{thm:selected-family-continuum-realization} to the discrete
operator family
\[
\Theta_n=\varepsilon_n^{-2}(B_n-2I_{F_n})
\]
with reconstruction datum
\((\mathcal T,\mathcal T_0,\{P_n^{\mathcal T}\},\{E_n^{\mathcal T}\})\).
Hypotheses \emph{(ii)}--\emph{(iii)} are exactly the stability and summable
refinement-consistency conditions required there, so the theorem produces a
unique bounded operator \(\Theta:\mathcal T\to\mathcal T\) satisfying
\[
E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u\to \Theta u
\qquad (u\in\mathcal T_0).
\]

Now let \(x^{(n)}=(x_m^{(n)})_{m\in\bbZ}\) be a selected transport sequence
with \(x_0^{(n)}=P_n^{\mathcal T}u\) and recursion law
\[
x_{m+1}^{(n)}=B_nx_m^{(n)}-x_{m-1}^{(n)}.
\]
Evaluating at \(m=0\) gives
\[
x_1^{(n)}-2x_0^{(n)}+x_{-1}^{(n)}
=(B_n-2I_{F_n})x_0^{(n)}
=(B_n-2I_{F_n})P_n^{\mathcal T}u.
\]
After dividing by \(\varepsilon_n^2\) and applying \(E_n^{\mathcal T}\), the
left-hand side becomes exactly
\[
E_n^{\mathcal T}\frac{x_1^{(n)}-2x_0^{(n)}+x_{-1}^{(n)}}{\varepsilon_n^2},
\]
while the right-hand side is \(E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u\).
The already proved convergence to \(\Theta u\) therefore yields the second
statement.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:one-stage-bounded-exact-scalar-recursion-forces-generator}]
\label{proof:thm:one-stage-bounded-exact-scalar-recursion-forces-generator}
Fix \(u\in\mathcal T_0\) and \(n\le m\). By hypothesis \emph{(ii)},
\[
P_m^{\mathcal T}u=J_{n,m}^{\mathcal T}P_n^{\mathcal T}u
\qquad\text{and}\qquad
E_n^{\mathcal T}=E_m^{\mathcal T}J_{n,m}^{\mathcal T},
\]
while the exact recursion-generator family satisfies
\[
J_{n,m}^{\mathcal T}\Theta_n=\Theta_mJ_{n,m}^{\mathcal T}.
\]
Therefore
\[
E_m^{\mathcal T}\Theta_mP_m^{\mathcal T}u
=
E_m^{\mathcal T}\Theta_mJ_{n,m}^{\mathcal T}P_n^{\mathcal T}u
=
E_m^{\mathcal T}J_{n,m}^{\mathcal T}\Theta_nP_n^{\mathcal T}u
=
E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u.
\]
So
\[
\Theta_\sharp u:=E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u
\qquad (u\in\mathcal T_0)
\]
is well defined and independent of \(n\).

Taking \(n=n_\ast\) in the displayed identity and using hypothesis
\emph{(iii)} gives
\[
\|\Theta_\sharp u\|_{\mathcal T}
=
\|E_{n_\ast}^{\mathcal T}\Theta_{n_\ast}P_{n_\ast}^{\mathcal T}u\|_{\mathcal T}
\le
C\|u\|_{\mathcal T}
\qquad (u\in\mathcal T_0).
\]
Hence \(\Theta_\sharp\) is bounded on the dense subspace \(\mathcal T_0\), so
it extends uniquely to a bounded operator \(\Theta:\mathcal T\to\mathcal T\).
Because \(\Theta\) agrees with \(\Theta_\sharp\) on \(\mathcal T_0\), one has
\[
E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u=\Theta u
\qquad (u\in\mathcal T_0,\ n\in\bbN).
\]

Now let \(x^{(n)}=(x_m^{(n)})_{m\in\bbZ}\) be any selected transport sequence
with \(x_0^{(n)}=P_n^{\mathcal T}u\) and
\[
x_{m+1}^{(n)}=B_nx_m^{(n)}-x_{m-1}^{(n)}.
\]
Evaluating at \(m=0\) gives
\[
x_1^{(n)}-2x_0^{(n)}+x_{-1}^{(n)}
=(B_n-2I_{F_n})P_n^{\mathcal T}u
=
\varepsilon_n^2\Theta_nP_n^{\mathcal T}u.
\]
After dividing by \(\varepsilon_n^2\) and applying \(E_n^{\mathcal T}\), the
previous exact identity yields
\[
E_n^{\mathcal T}\frac{x_1^{(n)}-2x_0^{(n)}+x_{-1}^{(n)}}{\varepsilon_n^2}
=
\Theta u.
\]

Finally, if \(L:\mathcal T_0\to\mathcal T\) is any asymptotically consistent
operator for the same exact recursive family, then for each \(u\in\mathcal T_0\)
the sequence \((E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u)_{n\in\bbN}\) is
constant with value \(\Theta_\sharp u=\Theta u\). Its limit is therefore
\(\Theta u\), so \(L=\Theta|_{\mathcal T_0}\). This proves uniqueness.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:exact-scalar-recursion-graph-realization}]
\label{proof:thm:exact-scalar-recursion-graph-realization}
Fix \(u\in\mathcal T_0\) and \(n\le m\). By hypothesis,
\[
P_m^{\mathcal T}u=J_{n,m}^{\mathcal T}P_n^{\mathcal T}u
\qquad\text{and}\qquad
E_n^{\mathcal T}=E_m^{\mathcal T}J_{n,m}^{\mathcal T},
\]
while
\[
J_{n,m}^{\mathcal T}\Theta_n=\Theta_mJ_{n,m}^{\mathcal T}.
\]
Therefore
\[
E_m^{\mathcal T}\Theta_mP_m^{\mathcal T}u
=
E_m^{\mathcal T}\Theta_mJ_{n,m}^{\mathcal T}P_n^{\mathcal T}u
=
E_m^{\mathcal T}J_{n,m}^{\mathcal T}\Theta_nP_n^{\mathcal T}u
=
E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u.
\]
So
\[
\Theta_\sharp u:=E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u
\qquad (u\in\mathcal T_0)
\]
is well defined and independent of \(n\).

Endow \(\mathcal T_0\) with the graph norm
\[
\|u\|_{\Theta,\mathrm{gr}}
=
\|u\|_{\mathcal T}+\|\Theta_\sharp u\|_{\mathcal T},
\]
let \(\mathcal T_{\Theta,\mathrm{gr}}\) be its completion, and let
\(\iota_\Theta:\mathcal T_0\to\mathcal T_{\Theta,\mathrm{gr}}\) be the
canonical dense embedding. Then
\[
\|u\|_{\mathcal T}\le \|u\|_{\Theta,\mathrm{gr}}
\qquad\text{and}\qquad
\|\Theta_\sharp u\|_{\mathcal T}\le \|u\|_{\Theta,\mathrm{gr}}
\qquad (u\in\mathcal T_0).
\]
Hence the identity map \(u\mapsto u\) and the operator
\(u\mapsto \Theta_\sharp u\) are both bounded from the graph normed core to
\(\mathcal T\), each with norm at most \(1\). They therefore extend uniquely
to bounded maps
\[
I_\Theta,\overline\Theta:\mathcal T_{\Theta,\mathrm{gr}}\to\mathcal T
\]
with \(\|I_\Theta\|\le 1\), \(\|\overline\Theta\|\le 1\), and
\[
I_\Theta\iota_\Theta u=u,
\qquad
\overline\Theta\,\iota_\Theta u=\Theta_\sharp u
\qquad (u\in\mathcal T_0).
\]
Since \(\Theta_\sharp u=E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u\) for every
\(n\), this proves item \emph{(i)}.

If \(L:\mathcal T_0\to\mathcal T\) is any asymptotically consistent operator
for the same exact recursive family, then for every \(u\in\mathcal T_0\) the
sequence \((E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u)_{n\in\bbN}\) is
constant with value \(\Theta_\sharp u\). Therefore its limit is
\(\Theta_\sharp u\), so \(L=\Theta_\sharp\) on \(\mathcal T_0\). This proves
item \emph{(ii)}.

Item \emph{(iii)} is the same graph-completion argument as
Theorem~\ref{thm:exact-core-graph-completion}, applied to the exact recursive
core operator \(\Theta_\sharp\): any graph-norm continuous Banach realization
of the same exact family factors uniquely through
\((\mathcal T_{\Theta,\mathrm{gr}},I_\Theta,\overline\Theta)\).
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:finite-exact-channel-stage-forces-bounded-generator}]
\label{proof:cor:finite-exact-channel-stage-forces-bounded-generator}
Because \(F_{n_\ast}\) is finite-dimensional, every linear map on \(F_{n_\ast}\)
is bounded. In particular, there exists \(M_\ast\ge 0\) such that
\[
\|\Theta_{n_\ast}x\|_{F_{n_\ast}}\le M_\ast\|x\|_{F_{n_\ast}}
\qquad (x\in F_{n_\ast}).
\]
Because \(P_{n_\ast}^{\mathcal T}\) and \(E_{n_\ast}^{\mathcal T}\) are
bounded, there exist constants \(A_\ast,B_\ast\ge 0\) such that
\[
\|P_{n_\ast}^{\mathcal T}u\|_{F_{n_\ast}}
\le
A_\ast\|u\|_{\mathcal T}
\qquad (u\in\mathcal T_0),
\]
\[
\|E_{n_\ast}^{\mathcal T}y\|_{\mathcal T}
\le
B_\ast\|y\|_{F_{n_\ast}}
\qquad (y\in F_{n_\ast}).
\]
Hence
\[
\|E_{n_\ast}^{\mathcal T}\Theta_{n_\ast}P_{n_\ast}^{\mathcal T}u\|_{\mathcal T}
\le
B_\ast M_\ast A_\ast\|u\|_{\mathcal T}
\qquad (u\in\mathcal T_0).
\]
This is exactly hypothesis \emph{(iii)} of
Theorem~\ref{thm:one-stage-bounded-exact-scalar-recursion-forces-generator}, so
that theorem applies and yields the unique bounded operator
\(\Theta:\mathcal T\to\mathcal T\).
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:exact-recursive-transport-yields-temporal-interface}]
\label{proof:thm:exact-recursive-transport-yields-temporal-interface}
Because \(\mathcal F\) is anchored to the canonical closure-balance
realization, Corollary~\ref{cor:residual-localization-on-d3} again localizes
the unique residual mediation layer at \(D=3\). This gives item (i) of
Definition~\ref{def:temporal-interface-datum}.

Next fix \(n\). Hypothesis \emph{(ii)} places the selected channel system at
level \(n\) in the scope of
Corollary~\ref{cor:transport-generation-yields-scalar-recursive}. Hence that
selected channel system is scalar-recursive, so every bi-infinite selected
transport sequence satisfies
\[
x_{m+1}=B_nx_m-x_{m-1}.
\]
This is item (ii) of
Definition~\ref{def:temporal-interface-datum}.

Now fix \(u\in\mathcal T_0\) and \(n\le m\). By hypothesis \emph{(iii)},
\[
P_m^{\mathcal T}u=J^{\mathcal T}_{n,m}P_n^{\mathcal T}u
\qquad\text{and}\qquad
E_n^{\mathcal T}=E_m^{\mathcal T}J^{\mathcal T}_{n,m},
\]
while the rescaled recursion-generator family satisfies
\[
J^{\mathcal T}_{n,m}\Theta_n=\Theta_mJ^{\mathcal T}_{n,m}.
\]
Therefore
\[
E_m^{\mathcal T}\Theta_mP_m^{\mathcal T}u
=
E_m^{\mathcal T}\Theta_mJ^{\mathcal T}_{n,m}P_n^{\mathcal T}u
=
E_m^{\mathcal T}J^{\mathcal T}_{n,m}\Theta_nP_n^{\mathcal T}u
=
E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u.
\]
Thus
\[
\Theta_\sharp u:=E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u
\]
is independent of \(n\), so it defines an operator
\[
\Theta_\sharp:\mathcal T_0\to\mathcal T.
\]
The sequence \((E_n^{\mathcal T}\Theta_nP_n^{\mathcal T}u)_{n\in\bbN}\) is
constant for every \(u\in\mathcal T_0\), hence asymptotically consistent with
\(\Theta_\sharp\). If \(L:\mathcal T_0\to\mathcal T\) is any other
asymptotically consistent operator for the same rescaled family, then both
\(\Theta_\sharp u\) and \(Lu\) are limits of the same sequence, so
\(L=\Theta_\sharp\) on \(\mathcal T_0\). Therefore the selected recursive
transport determines a unique continuum-equivalence class \([\Theta_\sharp]\),
which is item (iii) of Definition~\ref{def:temporal-interface-datum}.

The three items together are exactly a temporal interface datum, and each
component is unique. Hence \(\mathcal F\) carries a unique temporal interface
datum.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:exact-recursive-transport-forces-graph-temporal-generator}]
\label{proof:cor:exact-recursive-transport-forces-graph-temporal-generator}
Hypothesis \emph{(ii)} of
Theorem~\ref{thm:exact-recursive-transport-yields-temporal-interface} places
every selected channel system in the scope of
Corollary~\ref{cor:transport-generation-yields-scalar-recursive}, so the
scalar-recursive hypothesis of
Theorem~\ref{thm:exact-scalar-recursion-graph-realization} is satisfied.
Hypothesis \emph{(iii)} of
Theorem~\ref{thm:exact-recursive-transport-yields-temporal-interface} is
exactly the recursive comparison and reconstruction datum required there.
Therefore
Theorem~\ref{thm:exact-scalar-recursion-graph-realization} applies directly.
Its core operator \(\Theta_\sharp\) is the same operator constructed in the
proof of
Theorem~\ref{thm:exact-recursive-transport-yields-temporal-interface}, so its
graph completion represents the generator component of that unique temporal
interface datum.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:finite-exact-channel-stage-yields-bounded-temporal-generator}]
\label{proof:cor:finite-exact-channel-stage-yields-bounded-temporal-generator}
The hypotheses of
Corollary~\ref{cor:exact-recursive-transport-forces-graph-temporal-generator}
place the exact recursive family inside the scope of
Theorem~\ref{thm:exact-scalar-recursion-graph-realization}. The additional
finite-dimensionality hypothesis on \(F_{n_\ast}\) is exactly the extra
hypothesis of
Corollary~\ref{cor:finite-exact-channel-stage-forces-bounded-generator}.
Therefore that corollary applies and yields the unique bounded operator on
\(\mathcal T\) representing the generator component of the temporal interface.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:certified-local-ray-recursion-closes-temporal-bridge}]
\label{proof:cor:certified-local-ray-recursion-closes-temporal-bridge}
By Proposition~\ref{prop:word-local-ray-stencil}, the global word-local ray
carrier comes equipped with refinement comparison maps and a refinement-
coherent reconstruction datum for its selected observed law. By hypothesis,
the rescaled recursion-generator family \(\Theta_n\) is exactly that selected
observed law. Therefore hypothesis \emph{(iii)} of
Theorem~\ref{thm:exact-recursive-transport-yields-temporal-interface} is
satisfied, and the temporal-interface conclusion follows directly from that
theorem. The same data also satisfy
Corollary~\ref{cor:exact-recursive-transport-forces-graph-temporal-generator},
which gives the canonical graph-completed continuum realization of the
generator component.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:temporal-interface-from-d3}]
\label{proof:thm:temporal-interface-from-d3}
Hypotheses \emph{(i)}--\emph{(iii)} are exactly the hypotheses of
Theorem~\ref{thm:exact-recursive-transport-yields-temporal-interface}. That
theorem therefore applies directly and yields a unique temporal interface
datum. The appended statement on the graph-completed generator is then exactly
Corollary~\ref{cor:exact-recursive-transport-forces-graph-temporal-generator}.
\end{proof}
