% ============================================================
\section{The Three-Law Physical Hypothesis: Temporal Realization, Terminal Exactification, and Endpoint Completion}
\label{sec:compiled-law-classes}
% ============================================================

Part~I proves the structural calculus and continuum bridge. Part~II assumes
the explicit three-law physical hypothesis and proves its carrier-level
consequences. This chapter is the entry point to that Part~II theorem
surface. It states the three laws already fixed in the front claim boundary:
temporal realization on the faithful visible cut class, terminal
exactification on fixed selected bridges, and endpoint completion on the fixed
four-state local assembly. From those hypotheses it derives the selected-cut
realization data, the bridge-local exactified assembly, and the
endpoint-complete microscopic structure used later in the carrier
classification. In particular, the later Schr\"odinger,
wave/Klein--Gordon, Maxwell, and Einstein forms are not treated as
independent starting laws: on one same selected realization, later chapters
read them as carrier realizations of one common selected state-field law on
\(\mathrm{State}\).

Physical time is read here as the faithful visible realization of ordered
persistence on one observed bundle. The temporal interface, the unique
continuum ordering carried by the $D=3$ residual interface under
scalar-recursive faithful transport, becomes causal before/after on the
realized cut class. Corollary~\ref{cor:temporal-interface-precedes-physical-time}
furnishes that interface. The horizon complex constructed in Part~I remains
the ambient object, and the concrete carrier \(\mathrm{State}\) is its local
coordinate fiber on the selected bundle.

Later chapters use the structures derived here to identify the canonical
carrier realizations and to separate fundamental laws from effective closures.

\begin{tcolorbox}[colback=white, colframe=black!75, boxrule=0.9pt, title={Chapter 10 at a glance}]
\begin{description}[leftmargin=1.7em, itemsep=0.25em]
\item[Assumes.] The temporal realization law, the terminal exactification
      law, and the endpoint completion law.
\item[Proves.] The coherent selected-cut realization theorem, the
      bridge-local exactification and recurrence data, the fixed-generator
      exactified assembly, the endpoint-complete microscopic structure on
      the same fixed bridge, and the selected state-field law on which the
      later standard equations are jointly realized.
\item[Open.] Whether endpoint completion is an independent third law or is
      already forced by temporal realization and terminal exactification
      through a sharper intrinsic completion theorem on the fixed assembly.
\end{description}
\end{tcolorbox}

\begin{law}[Temporal realization law]
\label{law:temporal-realization}\lean{ClosureCurrent.TemporalRealizationLaw, ClosureCurrent.TemporalRealizationLaw.realizationSurface, ClosureCurrent.TemporalRealizationLaw.closureTransportSurface, ClosureCurrent.TemporalRealizationLaw.exchangeReturnSurface, ClosureCurrent.TemporalRealizationLaw.selectedCutCompletionSurface}
Physical time is the faithful visible realization of ordered persistence on a
coherent bundle. Accordingly, a closure-stable local event is physically
realized on a unique faithful cut class \(\mathfrak C_{\mathrm{time}}\), up to
horizon-preserving equivalence. For any representative \(P_h\) of that class,
the observed bundle
\[
\mathcal X_h:=P_h\cH^\bullet
\]
carries one exact visible law
\[
\mathcal L_h(z):=P_hA_{\mathrm{coh}}P_h+\Sigma_h(z),
\qquad
\Sigma_h(z):=z\,\CCSigmaP{P_h}{z},
\]
where \(\Sigma_h(z)\) is the returned-residual correction induced by internal
elimination of the hidden complement, and the induced continuum-closure class
is common across the whole realized class \(\mathfrak C_{\mathrm{time}}\).
Every admissible visible source on \(\mathfrak C_{\mathrm{time}}\) is
exchange-boundary reentry or returned residual of that same coherent bundle,
every closed realized system has no net internal visible creation, and no
independent constitutive completion is admissible.
\end{law}

\begin{tcolorbox}[colback=white, colframe=black!75, boxrule=0.9pt, title={Compact form on a representative cut}]
\[
\mathfrak C_{\mathrm{time}}=[P_h]_{\sim_{\mathrm{hor}}},
\qquad
\mathcal X_h=P_h\cH^\bullet,
\qquad
\mathcal L_h(z)=P_hA_{\mathrm{coh}}P_h+\Sigma_h(z),
\qquad
\Sigma_h(z)=z\,\CCSigmaP{P_h}{z}.
\]
\end{tcolorbox}

\begin{law}[Terminal exactification law]
\label{law:terminal-exactification}\lean{ClosureCurrent.TerminalExactificationLaw, ClosureCurrent.TerminalExactificationLaw.surface, ClosureCurrent.TerminalExactificationLaw.fixedPointOnExactifiedState}
On any fixed selected bridge datum carried by \(\mathfrak C_{\mathrm{time}}\),
the law-native local event carries one explicit signed readout \(r_e\) and one
genuine four-leg frame \(F_e\). These determine an assembled local state
\[
x_e(J):=\operatorname{Asm}_{r_e,F_e}(J)
\]
from the hidden pair current \(J\), where \(\operatorname{Asm}_{r_e,F_e}\)
denotes the assembled-state readout carried by that readout/frame pair. If
\(\mathsf E_e\) denotes the local exactifier and \(G_h\) the matched selected
generator on that bridge, then
\[
x_e(\mathsf E_e J)=G_h(x_e(J)),
\qquad
\mathsf E_e(\mathsf E_e J)=\mathsf E_e J.
\]
Thus exact local closure is terminal: once local content is exactly closed,
re-exactification does nothing further, the exactified assembled state is
fixed by the same selected generator, and only returned defect remains active
as visible residual.
\end{law}

\begin{law}[Endpoint completion law]
\label{law:endpoint-completion}\lean{ClosureCurrent.EndpointCompletionLaw}
After terminal exactification on a fixed selected bridge, a local interaction
is microscopically complete on that same bridge and physical principle. No
further hidden stage is admissible, no exogenous constitutive completion is
admissible, and the remaining endpoint response is carried intrinsically by
the exactified local assembly. Equivalently, the fixed four-state local
assembly admits a no-stage boundary completion on that same bridge, and the
remaining endpoint response closes there through the canonical direct response
and the canonical symmetric-response lift of that assembly.
\end{law}

\begin{theorem}[Exactified local states are generator-fixed]
\label{thm:exactified-local-states-are-generator-fixed}\lean{ClosureCurrent.TerminalExactificationLaw.fixedPointOnExactifiedState}
Assume the terminal exactification law. Then every exactified assembled local
state on that fixed selected bridge is a fixed point of the matched selected
generator.
\end{theorem}

\begin{proof}
Apply the exactifier/generator intertwining identity to an already exactified
current and then use idempotence of exactification. The result is exactly the
claimed fixed-point identity.
\end{proof}

\begin{theorem}[Terminal exactification determines the discrete bridge-local recurrence]
\label{thm:terminal-exactification-determines-the-discrete-bridge-local-recurrence}\lean{ClosureCurrent.TerminalExactificationLaw.coordinateTransport, ClosureCurrent.TerminalExactificationLaw.hiddenTrajectory_initialStateOf, ClosureCurrent.TerminalExactificationLaw.observedTrajectory_initialStateOf, ClosureCurrent.TerminalExactificationLaw.recursiveTrajectorySurface}
Assume the terminal exactification law on one fixed selected bridge. Then the
same bridge already carries an exact discrete recurrence on the reduced hidden
three-coordinate carrier. If \(\rho_e(J)\) denotes the reduced hidden
coordinate read from the local pair current \(J\), and if
\(\rho_e^{(n)}(J)\) denotes the coordinate obtained after \(n\) exactification
steps, then
\[
\rho_e(\mathsf E_e J)=\mathcal T_{G_h}\rho_e(J),
\qquad
\rho_e^{(n)}(J)=\mathcal T_{G_h}^{\,n}\rho_e(J),
\]
where \(\mathcal T_{G_h}\) is the reduced transport induced by the matched
selected generator \(G_h\). The selected observed trajectory is therefore read
exactly from that same reduced hidden orbit by the selected projection. Thus,
once the readout/frame pair is fixed, no separate recurrence datum remains on
that bridge.
\end{theorem}

\begin{proof}
The terminal exactification law already carries the exactifier/generator
intertwining law on the assembled local state. The reduced hidden coordinate is
just the three-coordinate quotient of that assembled state, so the one-step
transport identity follows immediately. Iterating this identity yields the full
\(n\)-step reduced hidden trajectory, and the observed trajectory is then read
from that same reduced hidden orbit by the selected projection. Hence the
discrete recurrence is already fixed on the bridge by the two-law surface.
\end{proof}

\begin{theorem}[Terminal exactification reads the hidden state from the six pair slots]
\label{thm:terminal-exactification-reads-the-hidden-state-from-the-six-pair-slots}\lean{ClosureCurrent.TerminalExactificationLaw.localSlotCoordinateSurface}
Assume the terminal exactification law on one fixed selected bridge. Then the
reduced hidden state is already read from the canonical six pair slots of the
framed local event. If
\[
\sigma_{12},\sigma_{13},\sigma_{14},\sigma_{23},\sigma_{24},\sigma_{34}
\]
denote the signed readouts of the six unordered pair slots on the framed local
event, then the reduced hidden coordinate is
\[
\rho_e(J)=
\bigl(
\sigma_{12}+\sigma_{13}+\sigma_{14},\,
-\sigma_{12}+\sigma_{23}+\sigma_{24},\,
-\sigma_{13}-\sigma_{23}+\sigma_{34}
\bigr).
\]
So the bridge-local hidden state is not an extra carrier placed above the pair
current. It is the direct readout of the finite diophantine pair carrier
\(\binom{4}{2}=6\) assembled onto the first three framed legs.
\end{theorem}

\begin{proof}
Fix the signed readout and four-leg frame carried by the terminal
exactification law. Those data determine the six signed pair-slot readouts of
the framed local current. The reduced hidden coordinate is, by definition, the
first three leg-flux coordinates of the assembled state, and each leg-flux is
exactly the corresponding signed sum of incident pair-slot readouts. This is
the displayed formula.
\end{proof}

\begin{theorem}[Bare temporal kernel carried by the temporal realization law]
\label{thm:bare-temporal-kernel-carried-by-the-primitive-temporal-surface}\lean{ClosureCurrent.TemporalRealizationLaw.toTemporalRealizationKernel, ClosureCurrent.TemporalRealizationKernel.surface}
Assume the temporal realization law. Then the same realized datum already
carries a bare temporal kernel: one exact visible law on one coherent bundle,
observer-covariance on the realized class, exchange/return as the whole visible
source grammar, exact internal elimination of the hidden complement, and no
independent constitutive completion.
\end{theorem}

\begin{proof}
The temporal realization law is already the primitive temporal realization
theorem. The bare temporal kernel is that same public law read with the
least-motion selector clause and the sharper interface-localization clause
suppressed.
\end{proof}

\begin{theorem}[Coherent realization from the temporal realization law]
\label{thm:coherent-realization-surface-from-the-temporal-realization-law}\lean{ClosureCurrent.TemporalRealizationLaw.toTemporalRealizationKernel, ClosureCurrent.TemporalRealizationKernel.coherentRealizationSurface, ClosureCurrent.TemporalRealizationLaw.coherentRealizationSurface}
Assume the temporal realization law. Then the same realized class already
carries coherent realization: one exact visible law on one
observed coherent bundle, observer-covariance on that class, exchange/return
as the whole visible source grammar, no net internal visible creation on
closed realized systems, and no independent constitutive completion.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:bare-temporal-kernel-carried-by-the-primitive-temporal-surface},
the temporal realization law first yields the bare temporal kernel on the same
class. The coherent realization claim is exactly that kernel read as one
exact visible law on one coherent bundle with observer-covariance,
exchange/return source grammar, and no independent constitutive completion.
\end{proof}

\begin{theorem}[Canonical representative of the realized class]
\label{thm:canonical-representative-of-the-realized-class}\lean{ClosureCurrent.TemporalRealizationLaw.canonicalRepresentativeSurface}
Assume the temporal realization law. Then the realized faithful cut class has
one canonical representative, and that representative is the least-motion cut.
\end{theorem}

\begin{proof}
The temporal realization law already carries observer-covariance across the
realized class together with uniqueness of the least-motion faithful
representative. Together these facts identify the least-motion cut as the
canonical representative of the realized class.
\end{proof}

\begin{theorem}[Selected-cut closure from the temporal realization law]
\label{thm:selected-cut-closure-from-the-temporal-realization-law}\lean{ClosureCurrent.TemporalRealizationLaw.toTemporalRealizationKernel, ClosureCurrent.TemporalRealizationKernel.selectedCutCompletionSurface, ClosureCurrent.TemporalRealizationLaw.selectedCutCompletionSurface}
Assume the temporal realization law. Then the same realized data already
carry the full selected-cut completion statement of Part~II before any
endpoint witness hypothesis is added.
\end{theorem}

\begin{proof}
The bare temporal kernel already supplies exact visibility and the absence of
independent constitutive completion on the realized data. The temporal
realization law itself strengthens that kernel by the least-motion-selected
closure clause and the returned-residual identification of all apparent
constitutive terms. That is exactly the selected-cut completion statement
claimed here.
\end{proof}

\begin{theorem}[The temporal law already fixes the auxiliary constructive clauses and closure transport]
\label{thm:temporal-law-already-fixes-detached-constructive-clauses}\lean{ClosureCurrent.TemporalRealizationLaw.constructiveClauseSurface, ClosureCurrent.TemporalRealizationLaw.originReadoutClosureSurface, ClosureCurrent.MicroscopicClosureLaw.trivialOriginReadoutAnchorTarget, ClosureCurrent.TemporalRealizationLaw.originReadoutTargetSurface, ClosureCurrent.TemporalRealizationLaw.originClosureSurface, ClosureCurrent.TemporalRealizationLaw.originTargetSurface, ClosureCurrent.TemporalRealizationLaw.originTargetSurfaceOfConstructiveAnchorCurrentTarget, ClosureCurrent.TemporalRealizationLaw.constructiveMicroscopicTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.TemporalRealizationLaw.originTargetSurfaceOfConstructiveCurrentTarget, ClosureCurrent.TemporalRealizationLaw.constructiveMicroscopicTargetOfConstructiveCurrentTarget}
Assume the temporal realization law, and let one auxiliary microscopic closure
law carry that same physical principle. Then the common grammar and
bundle-intrinsicity clauses on that auxiliary microscopic law are already fixed
by the temporal realization law itself, and the common selected-cut
continuum-closure transport is fixed there as well. Consequently, if that
auxiliary microscopic law is placed on that same physical principle, then the
selected-anchor target is already canonical and the selected-bundle forcing
statement follows with no extra origin-side data at all. If instead the
stronger selected-anchor current target is
supplied, then the bundled constructive microscopic target is recovered as
well. In particular, the same stronger conclusion holds a fortiori from the
constructive current target.
\end{theorem}

\begin{proof}
Once the auxiliary microscopic law is fixed on the same physical principle, the
temporal realization law already supplies the common same-bundle grammar,
return-side localization, selected visible realization, no-exogenous-closure
clause, and the bundle-intrinsicity clauses required by the auxiliary
constructive law. Because the law is stated on a faithful cut class up to
horizon-preserving equivalence, it also already carries the common
continuum-closure transport on that class. Moreover, the remaining
selected-anchor target is canonical: it asks only for one selected
anchor carrier/current object, and a trivial such object exists
without adding any new auxiliary hypothesis. Therefore the selected-bundle
forcing statement now follows directly from the temporal law itself once the
auxiliary microscopic law is placed on that same physical
principle. For the sharper completion-side constructive route one still needs
the stronger selected-anchor current target, because that route must also
carry the exactifier and slot-count bookkeeping. Once that stronger target is
supplied, the bundled constructive microscopic target follows as well; the
constructive current target gives the same stronger conclusion by immediate
specialization.
\end{proof}

\begin{theorem}[On a fixed selected bridge, the temporal law closes the current-side microscopic seam]
\label{thm:temporal-law-closes-current-side-microscopic-seam-on-a-fixed-bridge}\lean{ClosureCurrent.TemporalRealizationLaw.microscopicClosureLawOnBridge, ClosureCurrent.TemporalRealizationLaw.microscopicClosureLawOnBridge_samePhysicalPrinciple, ClosureCurrent.TemporalRealizationLaw.constructiveCurrentTargetOnBridge, ClosureCurrent.TemporalRealizationLaw.constructiveMicroscopicTargetOnBridge, ClosureCurrent.TemporalRealizationLaw.constructiveMicroscopicLawOnBridge, ClosureCurrent.TemporalRealizationLaw.constructiveMicroscopicLawOnBridge_samePhysicalPrinciple, ClosureCurrent.TemporalRealizationLaw.constructiveMicroscopicLawOnBridge_toMicroscopicClosureLaw, ClosureCurrent.TemporalRealizationLaw.originClosureWitnessOnBridge, ClosureCurrent.TemporalRealizationLaw.localEventObjectOnBridge, ClosureCurrent.TemporalRealizationLaw.originClosureTargetOnBridge, ClosureCurrent.TemporalRealizationLaw.originTargetSurfaceOnBridge}
Assume the temporal realization law, and fix selected bridge data
on that same realized cut. Then the law canonically determines a microscopic
closure law on that bridge, using that same physical principle, and already
forces there the exact constructive current target and hence the bundled
constructive microscopic target. More sharply, it canonically determines on
that bridge the full constructive microscopic law itself, the
selected-bundle witness, and the concrete local-event object carried
by that law. Consequently, once the selected bridge data are fixed, no
separate current-side or origin-side supplement remains: the selected-bundle
forcing statement already follows on that same bridge.
\end{theorem}

\begin{proof}
The selected bridge data fix the selected cut, the matched selected visible
law, and the selected generator on one common realized class. The temporal
realization law already fixes the same physical principle and the common
selected-cut closure transport on that class. So one can build the current
side canonically there: one bridge-local current structure on the same
bridge already recovers one microscopic closure law, one exact constructive
current realization of that law, and then the full constructive microscopic
law itself because the grammar and bundle-intrinsicity clauses are already
fixed on that bridge. From that fixed-bridge constructive microscopic law one reads the
origin-closure witness and the local-event object directly, so the
selected-bundle forcing statement also follows on that same bridge. Hence,
once the selected bridge data themselves are fixed, neither the current-side
microscopic seam nor the origin-side seam remains independent; the first
remaining independent seam begins only above this constructive microscopic
layer.
\end{proof}

\begin{theorem}[On a fixed selected bridge, the temporal law determines the selected bundle itself]
\label{thm:temporal-law-determines-the-selected-bundle-itself-on-a-fixed-bridge}\lean{ClosureCurrent.TemporalRealizationLaw.selectedBundleForcingOnBridge, ClosureCurrent.TemporalRealizationLaw.selectedBundleOnBridge, ClosureCurrent.TemporalRealizationLaw.selectedBundleSurfaceOnBridge}
Assume the temporal realization law, and fix a selected bridge datum on that
same realized cut. Then the law does not merely force existence of an
intrinsic selected bundle on that bridge; it already determines the active
selected-bundle object itself on that bridge. In particular, the selected
bundle is intrinsic on the least-motion cut, carries no carrier-wise
visibility hypotheses, inherits the selected cut and closure class of the
canonical Schur bridge, and already packages the one observed bundle shared by
all carrier realizations.
\end{theorem}

\begin{proof}
On a fixed selected bridge, the temporal law already determines the
fixed-bridge constructive microscopic law and hence the fixed-bridge
origin-closure witness. That witness already determines the exact
selected-bundle forcing object on the same bridge, and the active
selected-bundle object is read directly from that forcing datum. The listed
selected-bundle properties are then exactly the active selected-bundle theorem
already proved for that object.
\end{proof}

\begin{theorem}[On a fixed selected bridge, the temporal law already forces the realized bedrock recurrence profile]
\label{thm:temporal-law-forces-the-realized-bedrock-recurrence-profile-on-a-fixed-bridge}\lean{ClosureCurrent.TemporalRealizationLaw.bedrockRecurrenceSurfaceOnBridge}
Assume the temporal realization law, and fix a selected bridge datum on that
same realized cut. Then the same fixed bridge already carries the realized
bedrock recurrence profile: the matched selected generator carries the bedrock
law, the unique nontrivial residual interface occurs at \(D=3\), the balanced
carrier has six slots, and the intrinsic \([3,2,1]\) channel profile is
canonical there. Equivalently, the current fixed-bridge theorem
already certifies the bedrock side of the recursive picture: the selected
bundle is realized on a bridge whose local bookkeeping matches the canonical
bedrock profile before any independent Step~3 carrier-generation hypothesis is
supplied.
\end{theorem}

\begin{proof}
By the previous theorem, the temporal realization law already forces on that
same bridge the selected-bundle forcing theorem together with the facts that
the matched selected generator carries the bedrock law and is autonomous on
the selected horizon. The remaining profile statements are already forced on
the active Part~I spine: the unique nontrivial residual interface occurs at
\(D=3\), the balanced carrier has six slots, and the intrinsic
\([3,2,1]\) profile is canonical. Putting these together yields the stated
fixed-bridge recurrence statement.
\end{proof}

\begin{theorem}[On a fixed selected bridge, recursive realization forms a \(D=2 \to D=3 \to D=4\) ladder]
\label{thm:temporal-law-and-d2-seed-form-the-recursive-realization-ladder-on-a-fixed-bridge}\lean{ClosureCurrent.TemporalRealizationLaw.recursiveRealizationLadderOnBridge}
Assume the temporal realization law, fix a selected bridge datum on that same
realized cut, and supply the canonical \(D=2\) spectral seed datum. Then the
active certified theorem already exhibits one recursive realization ladder on
that same bridge:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item the \(D=2\) seed remains one-fiber, contributes no new carrier under
      repeat cycles, and carries the forced continuum spectral-defect form;
\item the unique nontrivial residual interface occurs at \(D=3\);
\item the selected \(D=4\) bridge already carries the six-slot balanced
      carrier and the canonical logical profile \([3,2,1]\).
\end{enumerate}
This is the strongest current certified recursive-realization statement. It does
not yet identify the full Step~3 carrier-generation data, but it isolates
the exact seed/interface/bulk ladder that any such data must realize on the
same selected bridge.
\end{theorem}

\begin{proof}
The \(D=2\) seed datum already gives the one-channel seed, one-fiber visible
law, repeat-no-new-carrier clause, prime-index primitive-support refinement,
and the forced continuum spectral-defect form. The preceding theorem supplies
on the same fixed selected bridge the selected-bundle existence, bedrock law on
the matched generator, the unique \(D=3\) residual interface, the six-slot
balanced carrier, and the canonical \([3,2,1]\) profile. Combining these two
results yields the stated recursive ladder.
\end{proof}

\begin{theorem}[On a fixed selected bridge, the temporal law already realizes the diophantine pair carrier]
\label{thm:temporal-law-realizes-the-diophantine-pair-carrier-on-a-fixed-bridge}\lean{ClosureCurrent.TemporalRealizationLaw.diophantinePairCarrierSurfaceOnBridge}
Assume the temporal realization law, and fix a selected bridge datum on that
same realized cut. Then the fixed-bridge local event already carries the finite
pair carrier counted by \(\binom{D}{2}\): the first stable bulk event is
four-legged, the hidden current is oriented on those legs by pair reversal,
and the carrier count is exactly
\[
\binom{4}{2}=6.
\]
So the pair count is not an extra microscopic choice principle. It is the
counting formula for the local pair carrier already determined by the law on
that bridge.
\end{theorem}

\begin{proof}
On a fixed selected bridge, the temporal realization law already determines the
fixed-bridge local-event object. That object carries, by construction, the first
stable bulk event with four legs, six pair slots, and the oriented pair-current
rule that reversing the leg order reverses the current value. Independently,
the active Part~I counting spine forces the nontrivial stable dimension
\(D=4\) and the corresponding six-slot pair count
\(\binom{4}{2}=6\). Therefore the local pair carrier determined on that bridge
is exactly the diophantine pair carrier.
\end{proof}

\begin{theorem}[On a fixed selected bridge, the diophantine pair carrier already carries the intrinsic overlap law]
\label{thm:diophantine-pair-carrier-carries-the-intrinsic-overlap-law-on-a-fixed-bridge}\lean{ClosureCurrent.TemporalRealizationLaw.diophantinePairCarrierIntrinsicChannelSurfaceOnBridge}
Assume the temporal realization law, and fix a selected bridge datum on that
same realized cut. Then the fixed-bridge six-slot pair carrier already carries
the canonical intrinsic overlap law: equal slot pairs contribute weight \(2\),
adjacent slot pairs contribute weight \(1\), and disjoint slot pairs
contribute weight \(0\). Consequently the active Part~I six-slot calculus acts
directly on that bridge-local carrier: this intrinsic law is already
adjacency-invariant, already has a unique three-parameter normal form, and
already carries the corresponding three channel eigenvalue decomposition.
\end{theorem}

\begin{proof}
The previous theorem gives on the fixed selected bridge the fixed-bridge
six-slot pair carrier itself. On any six-slot carrier, the canonical overlap
law is determined purely by slot incidence: two equal slots share two legs,
adjacent slots share one leg, and disjoint slots share none. Therefore the law
depends only on the intrinsic adjacency class of the slot pair. The active
Part~I six-slot channel calculus then applies directly, yielding the unique
three-parameter normal form and the associated three channel eigenvalue
decomposition.
\end{proof}

\begin{theorem}[On a fixed selected bridge, Step~3 is already fully determined]
\label{thm:temporal-law-reduces-step-3-to-canonical-carrier-generation-on-a-fixed-bridge}\lean{ClosureCurrent.TemporalRealizationLaw.intrinsicGenerationClauseOnBridge_valid, ClosureCurrent.TemporalRealizationLaw.minimalCompatibilityClauseOnBridge_valid, ClosureCurrent.TemporalRealizationLaw.lawNativeIntrinsicSectorSurfaceOnBridge}
Assume the temporal realization law, and fix a selected bridge datum on that
same realized cut. Then the temporal realization law already determines the selected-bundle
forcing object on that bridge, and that same bridge already carries the full
Step~3 structure: the selected bundle is intrinsic on the
least-motion cut, all visible sectors share that one selected bundle and
selected visible law, the carrier-level identification is the only non-common step,
the bridge-local pair carrier is governed by the intrinsic overlap law, the
canonical \([3,2,1]\) profile is already forced, and the finite-carrier,
canonical-signature, and three-parameter control data are already present.
Consequently the full active intrinsic sector-generation theorem already
follows on that same bridge. No independent Step~3 supplement remains.
\end{theorem}

\begin{proof}
On a fixed selected bridge, the temporal realization law already determines
the exact selected-bundle forcing object on that same bridge. The selected
bundle already carries the canonical visible carrier-generation data there.
The bridge-local diophantine six-slot pair carrier already carries the
intrinsic overlap law, and the fixed-bridge bedrock recurrence theorem already
forces the canonical \([3,2,1]\) profile. The active finite-carrier theorem
already gives the canonical-signature and three-parameter control data.
These together are exactly the Step~3 clauses, so the active
intrinsic sector-generation theorem applies with no additional independent
Step~3 data.
\end{proof}

\begin{theorem}[Temporal realization plus terminal exactification determines the constructive sector law on a fixed bridge]
\label{thm:temporal-plus-terminal-law-determines-the-constructive-sector-law-on-a-fixed-bridge}\lean{ClosureCurrent.TerminalExactificationLaw.lawNativeConstructiveSectorSurface}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the law already determines the full
constructive sector-law structure on that bridge. In particular, the same bridge
already carries one bridge-local pair current with direct-return compatibility,
autonomous visible realization, and minimal visible quotients; the selected cut
already carries the exact visible law and forced continuum law on that same
bundle; the bundle is already intrinsic on the least-motion cut with no
carrier-wise visibility hypotheses; and the canonical \([3,2,1]\) profile is
already fixed there. Thus no Step~3 supplement, and no current-side,
origin-side, exactifier, or carrier-generation supplement, remains below
Step~4 on that bridge.
\end{theorem}

\begin{proof}
The temporal realization law already determines the fixed-bridge local-event
object on the fixed bridge, and the terminal exactification law adds the
local sign/frame and exactifier/generator intertwining data on that same
event. By the previous theorem, the underlying temporal law already forces the
full Step~3 structure on that bridge. Therefore the constructive sector law on
that bridge is now completely fixed by the two-law hypothesis. Its active theorem is
exactly the listed constructive sector-law structure, so below Step~4 no further
Step~3, current-side, origin-side, exactifier-side, or carrier-generation
supplement remains.
\end{proof}

\begin{theorem}[On a fixed selected bridge, the two-law hypothesis already forces Step~3]
\label{thm:on-a-fixed-selected-bridge-only-canonical-carrier-generation-remains-genuinely-independent-in-step-3}\lean{ClosureCurrent.TerminalExactificationLaw.lawNativeIntrinsicSectorGenerationSurface}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then every Step~3 control datum is already forced
there: the finite carrier is already available, the canonical signature is
already fixed, the three-parameter control data are already present, the
canonical \([3,2,1]\) profile is already forced, and the visible phase, wave,
kinetic, gauge, and geometric generation outputs already follow. Thus no
independent Step~3 input remains on that fixed bridge.
\end{theorem}

\begin{proof}
The previous theorem gives the bridge-local constructive sector law on the fixed
bridge with no extra Step~3 datum. The active intrinsic sector-generation
theorem therefore applies directly to that same fixed-bridge object. It
contributes, without any further bridge-side, current-side, or Step~3
supplement, the finite-carrier theorem, the canonical-signature theorem, the
three-parameter control data, the canonical \([3,2,1]\) profile, and the
five visible generation outputs. Hence Step~3 is already fully forced on that
fixed bridge by the public two-law hypothesis itself.
\end{proof}

\begin{theorem}[Terminal exactification removes the four-state exactifier seam]
\label{thm:terminal-exactification-removes-the-four-state-exactifier-seam}\lean{ClosureCurrent.TerminalExactificationLaw.lawNativeFourStateReadout, ClosureCurrent.TerminalExactificationLaw.lawNativeExactifierRealizationTarget, ClosureCurrent.TerminalExactificationLaw.completionClassificationTargetOfRepresentatives, ClosureCurrent.TerminalExactificationLaw.completionSplitTargetOfRigidityAndRepresentatives, ClosureCurrent.TerminalExactificationLaw.completionBridgeTargetOfRigidityAndRepresentatives, ClosureCurrent.TerminalExactificationLaw.completionTargetOfRigidityAndRepresentatives}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. If, on that same fixed-bridge local event, the
Step~4 rigidity target and the canonical representative target are
supplied, then no separate exactifier/generator realization supplement
remains, and no separate carrier-classification target remains either. The law
itself already supplies the fixed-bridge four-state readout and the
exactifier/generator intertwining target on the same constructive sector law.
The reduced representative data already carries the four endpoint-sensitive
canonical representatives together with the already classified kinetic face, so
the split completion target, the split completion-bridge target, and the
no-stage completion target already follow on the same microscopic law from just
those two remaining Step~4 inputs.
\end{theorem}

\begin{proof}
The terminal exactification law already provides the signed readout/frame pair
and the exactifier/generator intertwining identity on the fixed-bridge local
event determined by the temporal law on that bridge. Hence the four-state
assembly data on that same fixed-bridge event are no longer detached. Moreover,
once the reduced representative data are supplied on the generated carriers,
the weaker carrier-classification target is already forced: the kinetic face is
already present at the stock/classification level, and the four remaining faces
are carried as canonical endpoint-sensitive representatives. So the only
genuinely independent Step~4 input left below no-stage completion is the
fixed-bridge rigidity target together with that reduced representative target.
Those two targets, together with the fixed-bridge four-state data, complete the
split completion bridge and therefore yield the split completion target, the
split completion-bridge target, and the no-stage completion target.
\end{proof}

\begin{theorem}[A completion bridge plus endpoint rigidity yields the direct normal forms]
\label{thm:law-native-completion-bridge-plus-lane-rigidity-yields-the-direct-flagship-normal-forms}\lean{ClosureCurrent.TerminalExactificationLaw.normalFormTargetOfBridgeRigidityTargets, ClosureCurrent.TerminalExactificationLaw.fullNormalFormSurfaceOfBridgeRigidityTargets, ClosureCurrent.NoStageCompletionBridge.normalFormTargetOfRigidityTargets, ClosureCurrent.NoStageCompletionBridge.fullSurfaceOfRigidityTargets}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Let one no-stage completion bridge be fixed on the
same fixed microscopic law, and assume that on that same completion
bridge the phase, wave, gauge, and geometric endpoint-rigidity targets are all
realized. Then the direct normal-form target already follows on that
same microscopic law. In fact the full completion-side normal-form theorem follows
there: one common no-stage completion witness on that microscopic law already
carries the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
Einstein forms in the standard external languages
\cite{Schrodinger1926,Klein1926,Maxwell1865,Einstein1915,Wald1984}.
\end{theorem}

\begin{proof}
The fixed completion bridge already carries the same microscopic law, and the
four endpoint-rigidity targets live on that same aligned completion data. The
split normal-form bridge theorem therefore applies directly on that bridge and
forces the direct normal-form target there. Since the bridge is fixed on the
same fixed microscopic law, the same conclusion rewrites immediately to
that bridge-local object. The stronger full normal-form theorem is the
corresponding full theorem on the same bridge, transported along the
same law identity.
\end{proof}

\begin{theorem}[One canonical witness target already recovers the unique strong microscopic structure]
\label{thm:law-native-flagship-witness-target-recovers-the-strong-microscopic-package}\lean{ClosureCurrent.TerminalExactificationLaw.flagshipWitnessTargetOfCanonicalFlagshipWitnessTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfCanonicalFlagshipWitnessTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalFlagshipWitnessTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume the fixed-bridge microscopic law itself already
carries one unique endpoint-complete witness structure: one no-stage completion
witness on the same bridge and physical principle together with one aggregate
endpoint-witness bundle on that witness's own selected bundle, and
every other such witness structure on that same bridge and physical principle is equal to it. Then one unique
endpoint-complete strong microscopic law already exists on that same bridge and
physical principle. Hence the analytic normal forms and the exact physical
equation field already follow there.
\end{theorem}

\begin{proof}
This is the canonical witness target on the fixed bridge. Unpacking it gives one unique
pair consisting of a no-stage completion witness on the same microscopic law
and one endpoint witness bundle on that witness's own selected bundle. That
pair already defines the endpoint-complete strong microscopic structure on the
same completion law. Any other strong microscopic structure on the same bridge
and physical principle yields the same witness pair, so uniqueness is forced
at that level rather than added by hand. The analytic normal forms and
exact physical equation field are then immediate consequences of the
strong microscopic theorem.
\end{proof}

\begin{theorem}[A unique completion witness together with a unique endpoint bundle already gives the canonical witness target]
\label{thm:canonical-completion-witness-bundle-target-implies-canonical-flagship-witness-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalFlagshipWitnessTargetOfCanonicalCompletionWitnessBundleTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfCanonicalCompletionWitnessBundleTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalCompletionWitnessBundleTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume, first, that the fixed-bridge microscopic law
admits one unique no-stage completion witness. Assume, second, that on this
same witness there is one unique aggregate endpoint-witness bundle.
Then the canonical witness target is realized. Hence one
unique endpoint-complete strong microscopic law already exists on that same
bridge and physical principle, and the analytic normal forms and exact
physical equation field already follow there.
\end{theorem}

\begin{proof}
This is the sequential form of the canonical witness bottleneck. A unique
completion witness and a unique endpoint witness bundle on that witness
determine one unique witness structure on the fixed bridge. That is exactly the canonical
witness target in unpacked form. The preceding theorem then applies
immediately and yields the unique strong microscopic structure together with the
analytic normal forms and exact physical equation field.
\end{proof}

\begin{theorem}[A unique completion witness together with unique carrier-wise endpoint representatives already gives the canonical witness target]
\label{thm:canonical-completion-witness-lane-target-implies-canonical-flagship-witness-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTargetOfCanonicalCompletionWitnessLaneTarget, ClosureCurrent.TerminalExactificationLaw.canonicalFlagshipWitnessTargetOfCanonicalCompletionWitnessLaneTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfCanonicalCompletionWitnessLaneTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalCompletionWitnessLaneTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume the fixed-bridge microscopic law admits one
unique no-stage completion witness. Assume moreover that on this same witness
each of the four intrinsic carrier laws carries one unique endpoint witness. Then the
canonical witness target is realized. Hence one unique
endpoint-complete strong microscopic law already exists on that same bridge and
physical principle, and the analytic normal forms and exact physical
equation field already follow there.
\end{theorem}

\begin{proof}
This is the carrier-wise unpacking of the same canonical endpoint representative. The
four unique carrier witnesses assemble into one unique aggregate endpoint witness
bundle on the unique completion witness. That yields the previous theorem's
unique witness-plus-bundle target, and therefore the same unique strong
microscopic structure together with the analytic normal forms and exact
physical equation field.
\end{proof}

\begin{theorem}[A unique completion witness together with unique carrier-wise frontier representatives already gives the canonical witness target]
\label{thm:canonical-completion-witness-frontier-target-implies-canonical-flagship-witness-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessLaneTargetOfCanonicalCompletionWitnessFrontierTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTargetOfCanonicalCompletionWitnessFrontierTarget, ClosureCurrent.TerminalExactificationLaw.canonicalFlagshipWitnessTargetOfCanonicalCompletionWitnessFrontierTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfCanonicalCompletionWitnessFrontierTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalCompletionWitnessFrontierTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume the fixed-bridge microscopic law admits one
unique no-stage completion witness. Assume moreover that on this same witness
each of the four intrinsic carrier laws carries one unique frontier representative on the
selected bundle. Then the canonical witness target is
realized. Hence one unique endpoint-complete strong microscopic law already
exists on that same bridge and physical principle, and the analytic normal forms
and exact physical equation field already follow there.
\end{theorem}

\begin{proof}
This is the smaller frontier-side form of the same canonical completion
mechanism. The four unique frontiers determine the four endpoint witnesses on
the same completion witness, so the preceding carrier-wise endpoint theorem
applies immediately. The unique strong microscopic structure and its analytic and
equation surfaces then follow as before.
\end{proof}

\begin{theorem}[A unique completion witness together with a unique frontier bundle already gives the canonical witness target]
\label{thm:canonical-completion-witness-frontier-bundle-target-implies-canonical-flagship-witness-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierTargetOfCanonicalCompletionWitnessFrontierBundleTarget, ClosureCurrent.TerminalExactificationLaw.canonicalFlagshipWitnessTargetOfCanonicalCompletionWitnessFrontierBundleTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfCanonicalCompletionWitnessFrontierBundleTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalCompletionWitnessFrontierBundleTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume the fixed-bridge microscopic law admits one
unique no-stage completion witness. Assume moreover that on this same witness
there is one unique aggregate frontier bundle on the selected bundle.
Then the canonical witness target is realized. Hence one
unique endpoint-complete strong microscopic law already exists on that same
bridge and physical principle, and the analytic normal forms and exact
physical equation field already follow there.
\end{theorem}

\begin{proof}
This is the aggregate form of the same frontier-side mechanism. A unique
frontier bundle on the unique completion witness already determines the unique
phase, wave, gauge, and geometric frontiers individually. The preceding
frontier theorem therefore applies immediately, and yields the same
unique strong microscopic structure together with the analytic normal forms
and exact physical equation field.
\end{proof}

\begin{theorem}[Unique witness structure plus universal frontier fill upgrades to the exact canonical completion bottleneck]
\label{thm:canonical-flagship-witness-target-plus-universal-frontier-fill-implies-canonical-completion-bundle-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTargetOfCanonicalFlagshipWitnessTargetAndUniversalFrontierFill, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTargetOfCanonicalFlagshipWitnessTargetAndUniversalFrontierFill, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalFlagshipWitnessTargetAndUniversalFrontierFill}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume the fixed-bridge microscopic law already
carries one unique witness structure. Assume further that every
no-stage completion witness on that same microscopic law already
carries some frontier bundle on its own selected bundle. Then the
exact canonical completion bottleneck is met: there is one unique no-stage
completion witness together with one unique aggregate frontier bundle,
equivalently one unique aggregate endpoint-witness bundle. Hence one
unique endpoint-complete strong microscopic law already exists on that same
bridge and physical principle, together with the analytic normal forms and
the exact physical equation field.
\end{theorem}

\begin{proof}
The only obstruction to upgrading the distinguished witness
target to the sequential canonical completion target is that an arbitrary
no-stage completion witness might not yet carry any frontier data, so
it cannot even be compared to the distinguished structure. The universal
frontier-fill hypothesis removes exactly that obstruction. Every witness then
admits a frontier structure, which repackages into an endpoint structure; the
unique witness structure therefore forces the witness itself to be
unique. On that same witness, uniqueness of the frontier structure follows by the
same comparison argument, and the endpoint-bundle version follows by the
frontier/endpoint round-trip identities. The previously proved canonical
completion theorems then recover the unique strong microscopic structure and its
analytic and equation surfaces.
\end{proof}

\begin{theorem}[The exact canonical completion bottleneck is equivalent to a unique witness structure plus universal frontier fill]
\label{thm:canonical-completion-frontier-bundle-target-iff-canonical-flagship-witness-plus-universal-frontier-fill}\lean{ClosureCurrent.TerminalExactificationLaw.universalFlagshipFrontierFillTargetOfCanonicalCompletionWitnessFrontierBundleTarget, ClosureCurrent.TerminalExactificationLaw.canonicalFlagshipWitnessFrontierFillTargetOfCanonicalCompletionWitnessFrontierBundleTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTargetOfCanonicalFlagshipWitnessFrontierFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTarget_iff_canonicalFlagshipWitnessFrontierFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalFlagshipWitnessFrontierFillTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalFlagshipWitnessFrontierFillTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the following are equivalent on the same
microscopic law:
\begin{enumerate}
\item there is one unique no-stage completion witness, and on that witness one
unique aggregate frontier bundle;
\item there is one unique witness structure, and every
      no-stage completion witness already carries some frontier bundle on
      its own selected bundle.
\end{enumerate}
Equivalently, the endpoint-bundle form of the canonical completion bottleneck
is also exactly this same conjunction. Hence this two-part bottleneck already
recovers one unique endpoint-complete strong microscopic law together with the
analytic normal forms and the exact physical equation field.
\end{theorem}

\begin{proof}
If the exact canonical completion bottleneck holds, then the unique witness and
its unique frontier bundle already give one unique witness structure,
and witness uniqueness transports the same frontier bundle to every other
completion witness. Conversely, the previous theorem showed that a unique
witness structure plus universal frontier fill upgrades back to the
exact canonical completion target. The endpoint-bundle form is equivalent by
the frontier/endpoint round-trip identities, and the previously proved
completion theorem then yields the unique strong microscopic structure
and its analytic and equation surfaces.
\end{proof}

\begin{theorem}[Universal frontier fill is exactly universal boundary fill]
\label{thm:canonical-completion-bottleneck-iff-canonical-flagship-witness-plus-universal-boundary-fill}\lean{ClosureCurrent.NoStageCompletionWitness.flagshipBoundaryTarget_iff_nonempty_frontiers, ClosureCurrent.TerminalExactificationLaw.universalFlagshipBoundaryFillTarget_iff_universalFlagshipFrontierFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalFlagshipWitnessBoundaryFillTarget_iff_canonicalFlagshipWitnessFrontierFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTarget_iff_canonicalFlagshipWitnessBoundaryFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalFlagshipWitnessBoundaryFillTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalFlagshipWitnessBoundaryFillTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then universal frontier fill on the
completion class is exactly the same as universal aggregate boundary closure:
for every no-stage completion witness, carrying some aggregate
frontier bundle on its selected bundle is equivalent to satisfying the
aggregate boundary target there. Consequently, the exact canonical
completion bottleneck is equivalently the conjunction of:
\begin{enumerate}
\item one unique witness structure on the microscopic law;
\item universal aggregate boundary closure on every
      no-stage completion witness.
\end{enumerate}
Hence this boundary-form bottleneck already recovers one unique
endpoint-complete strong microscopic law together with the analytic normal forms
and the exact physical equation field.
\end{theorem}

\begin{proof}
On one fixed no-stage completion witness, the four frontier targets package
into one aggregate frontier bundle, and conversely any such bundle unpacks into
the four frontier targets; this is exactly the aggregate boundary target. The
frontier-fill and boundary-fill formulations are therefore equivalent witness
by witness, hence also universally over the completion class. The
preceding equivalence theorem then identifies the canonical completion
bottleneck with the unique witness structure plus universal boundary
fill, and the already proved strong-law recovery theorem supplies the unique
strong microscopic structure together with the analytic and equation surfaces.
\end{proof}

\begin{theorem}[The exact boundary-form bottleneck is equivalently one unique strong microscopic law plus universal boundary fill]
\label{thm:canonical-completion-bottleneck-iff-canonical-strong-microscopic-law-plus-universal-boundary-fill}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalStrongMicroscopicLawTargetOfCanonicalFlagshipWitnessTarget, ClosureCurrent.TerminalExactificationLaw.canonicalFlagshipWitnessTargetOfCanonicalStrongMicroscopicLawTarget, ClosureCurrent.TerminalExactificationLaw.canonicalFlagshipWitnessTarget_iff_canonicalStrongMicroscopicLawTarget, ClosureCurrent.TerminalExactificationLaw.canonicalStrongMicroscopicLawBoundaryFillTarget_iff_canonicalFlagshipWitnessBoundaryFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTarget_iff_canonicalStrongMicroscopicLawBoundaryFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalStrongMicroscopicLawBoundaryFillTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalStrongMicroscopicLawBoundaryFillTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the exact canonical completion bottleneck is
equivalently the conjunction of:
\begin{enumerate}
\item one unique endpoint-complete strong microscopic law on the same bridge
and physical principle;
\item universal aggregate boundary closure on every
      no-stage completion witness.
\end{enumerate}
Hence this strong-law form of the bottleneck already recovers one unique
endpoint-complete strong microscopic law together with the analytic field
surface and the exact physical equation field.
\end{theorem}

\begin{proof}
The unique witness package and the unique strong microscopic law are
the same data read at two nearby levels. The witness package determines the
completion law and endpoint data of the unique strong microscopic law, while a
unique strong microscopic law determines the same canonical witness package on
its own completion law. Therefore replacing the unique witness package by the
equivalent unique strong microscopic law does not change the exact boundary-form
bottleneck. The previously proved boundary-fill theorem then yields the same
unique strong microscopic package together with the analytic and equation
surfaces.
\end{proof}

\begin{theorem}[The exact boundary-form bottleneck is equivalently one unique strong microscopic law plus universal endpoint-witness fill]
\label{thm:canonical-completion-bottleneck-iff-canonical-strong-microscopic-law-plus-universal-endpoint-fill}\lean{ClosureCurrent.NoStageCompletionWitness.flagshipBoundaryTargetOfEndpointWitnessTarget, ClosureCurrent.NoStageCompletionWitness.endpointWitnessTarget_iff_flagshipBoundaryTarget, ClosureCurrent.TerminalExactificationLaw.universalFlagshipBoundaryFillTarget_iff_universalEndpointWitnessFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalStrongMicroscopicLawEndpointFillTarget_iff_canonicalStrongMicroscopicLawBoundaryFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTarget_iff_canonicalStrongMicroscopicLawEndpointFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalStrongMicroscopicLawEndpointFillTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalStrongMicroscopicLawEndpointFillTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the exact canonical completion bottleneck is
equivalently the conjunction of:
\begin{enumerate}
\item one unique endpoint-complete strong microscopic law on the same bridge
and physical principle;
\item universal aggregate endpoint-witness fill on every no-stage
      completion witness.
\end{enumerate}
Hence this endpoint-witness form of the bottleneck already recovers one unique
endpoint-complete strong microscopic law together with the analytic field
surface and the exact physical equation field.
\end{theorem}

\begin{proof}
On one fixed no-stage completion witness, carrying an aggregate endpoint
witness package is equivalent to satisfying the aggregate boundary target:
endpoint witnesses determine the frontier bundle, and the frontier-side
boundary target already reassembles the aggregate endpoint witness package.
Therefore universal boundary fill and universal endpoint-witness fill are
exactly the same condition on the completion class. Replacing the boundary-fill clause by
the equivalent endpoint-fill clause therefore does not change the exact
strong-law bottleneck, and the previously proved strong-law recovery theorem
yields the same unique strong microscopic package together with the analytic
and equation surfaces.
\end{proof}

\begin{theorem}[The exact boundary-form bottleneck is equivalently one unique strong microscopic law plus universal strong extension]
\label{thm:canonical-completion-bottleneck-iff-canonical-strong-microscopic-law-plus-universal-extension}\lean{ClosureCurrent.NoStageCompletionWitness.strongMicroscopicExtensionTargetOfEndpointWitnessTarget, ClosureCurrent.NoStageCompletionWitness.endpointWitnessTargetOfStrongMicroscopicExtensionTarget, ClosureCurrent.NoStageCompletionWitness.endpointWitnessTarget_iff_strongMicroscopicExtensionTarget, ClosureCurrent.TerminalExactificationLaw.universalEndpointWitnessFillTarget_iff_universalStrongMicroscopicExtensionTarget, ClosureCurrent.TerminalExactificationLaw.canonicalStrongMicroscopicLawExtensionTarget_iff_canonicalStrongMicroscopicLawEndpointFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTarget_iff_canonicalStrongMicroscopicLawExtensionTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalStrongMicroscopicLawExtensionTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalStrongMicroscopicLawExtensionTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the exact canonical completion bottleneck is
equivalently the conjunction of:
\begin{enumerate}
\item one unique endpoint-complete strong microscopic law on the same bridge
and physical principle;
\item universal strong microscopic extension on every no-stage
      completion witness.
\end{enumerate}
Hence this extension form of the bottleneck already recovers one unique
endpoint-complete strong microscopic law together with the analytic field
surface and the exact physical equation field.
\end{theorem}

\begin{proof}
On one fixed no-stage completion witness, carrying an aggregate endpoint
witness package is equivalent to extending that same completion law to an
endpoint-complete strong microscopic law. Therefore universal endpoint fill and
universal strong microscopic extension are exactly the same
condition. Replacing the endpoint-fill clause by the equivalent extension
clause therefore does not change the exact strong-law bottleneck, and the
previously proved strong-law recovery theorem yields the same unique strong
microscopic package together with the analytic and equation surfaces.
\end{proof}

\begin{theorem}[The exact boundary-form bottleneck is equivalently one unique strong microscopic law plus universal completion-law collapse]
\label{thm:canonical-completion-bottleneck-iff-canonical-strong-microscopic-law-plus-universal-completion-collapse}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalStrongMicroscopicLawCompletionCollapseTarget_iff_canonicalStrongMicroscopicLawExtensionTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTarget_iff_canonicalStrongMicroscopicLawCompletionCollapseTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalStrongMicroscopicLawCompletionCollapseTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalStrongMicroscopicLawCompletionCollapseTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the exact canonical completion bottleneck is
equivalently the conjunction of:
\begin{enumerate}
\item one unique endpoint-complete strong microscopic law on the same bridge
and physical principle;
\item every no-stage completion witness already carries exactly the
      same completion law as that unique strong microscopic law.
\end{enumerate}
Hence this completion-collapse form of the bottleneck already recovers one
unique endpoint-complete strong microscopic law together with the analytic
field surface and the exact physical equation field.
\end{theorem}

\begin{proof}
Universal strong microscopic extension means that every no-stage
completion witness extends to some endpoint-complete strong microscopic law.
But once the strong microscopic law is unique on the fixed bridge and physical
principle, every such extension must be that same unique strong law.
Therefore universal strong extension is equivalent to collapse of the entire
completion class onto the completion law carried by the unique
strong microscopic law. Replacing the extension clause by this equivalent
completion-collapse clause therefore does not change the exact bottleneck, and
the previously proved recovery theorem yields the same unique strong
microscopic package together with the analytic and equation surfaces.
\end{proof}

\begin{theorem}[The exact boundary-form bottleneck is equivalently one unique strong microscopic law plus one unique no-stage completion witness]
\label{thm:canonical-completion-bottleneck-iff-canonical-strong-microscopic-law-plus-unique-completion-witness}\lean{ClosureCurrent.NoStageCompletionWitness.eq_of_completionLaw_eq, ClosureCurrent.TerminalExactificationLaw.canonicalStrongMicroscopicLawCompletionWitnessTarget_iff_canonicalStrongMicroscopicLawCompletionCollapseTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTarget_iff_canonicalStrongMicroscopicLawCompletionWitnessTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalStrongMicroscopicLawCompletionWitnessTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalStrongMicroscopicLawCompletionWitnessTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the exact canonical completion bottleneck is
equivalently the conjunction of:
\begin{enumerate}
\item one unique endpoint-complete strong microscopic law on the same bridge
and physical principle;
\item one unique no-stage completion witness on that same
microscopic law.
\end{enumerate}
Hence this unique-witness form of the bottleneck already recovers one unique
endpoint-complete strong microscopic law together with the analytic field
surface and the exact physical equation field.
\end{theorem}

\begin{proof}
Universal completion-law collapse says that every
no-stage
completion witness has the same completion law as the unique strong
microscopic law. But a no-stage completion witness is determined by its
completion law: the bridge and physical-principle components are only
propositional alignment data. Hence collapse of the entire completion class
onto one completion law is equivalent to uniqueness of the
no-stage completion witness itself. Replacing the collapse clause by this
equivalent unique-witness clause therefore does not change the exact
bottleneck, and the previously proved recovery theorem yields the same unique
strong microscopic package together with the analytic and equation surfaces.
\end{proof}

\begin{theorem}[The exact boundary-form bottleneck is equivalently one unique strong microscopic law plus one unique no-stage completion law]
\label{thm:canonical-completion-bottleneck-iff-canonical-strong-microscopic-law-plus-unique-completion-law}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalStrongMicroscopicLawCompletionLawTarget_iff_canonicalStrongMicroscopicLawCompletionWitnessTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTarget_iff_canonicalStrongMicroscopicLawCompletionLawTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalStrongMicroscopicLawCompletionLawTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalStrongMicroscopicLawCompletionLawTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the exact canonical completion bottleneck is
equivalently the conjunction of:
\begin{enumerate}
\item one unique endpoint-complete strong microscopic law on the same bridge
and physical principle;
\item one unique no-stage completion law on that same selected bridge and
physical principle.
\end{enumerate}
Hence this unique-completion-law form of the bottleneck already recovers one
unique endpoint-complete strong microscopic law together with the analytic
field surface and the exact physical equation field.
\end{theorem}

\begin{proof}
The no-stage completion witness is only the completion law together with the
two alignment equalities asserting that it lives on the same selected bridge
and physical principle as the fixed-bridge microscopic law. Thus uniqueness of
the witness is equivalent to uniqueness of the underlying no-stage completion
law with those same alignment properties. Replacing the witness clause by this
equivalent public completion-law clause therefore does not change the exact
bottleneck, and the previously proved recovery theorem yields the same unique
strong microscopic package together with the analytic and equation surfaces.
\end{proof}

\begin{theorem}[The exact boundary-form bottleneck is equivalently one unique no-stage completion law plus one unique endpoint bundle on that law]
\label{thm:canonical-completion-bottleneck-iff-unique-completion-law-plus-unique-endpoint-bundle}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalCompletionLawEndpointBundleTarget_iff_canonicalStrongMicroscopicLawCompletionLawTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalCompletionLawEndpointBundleTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the exact canonical completion bottleneck is
equivalently the conjunction of:
\begin{enumerate}
\item one unique no-stage completion law on the same selected bridge and
physical principle;
\item one unique aggregate endpoint-witness bundle on that same
completion law.
\end{enumerate}
Hence this unique-completion-law / unique-endpoint-bundle form already
recovers one unique endpoint-complete strong microscopic law together with the
analytic field surface and the exact physical equation field.
\end{theorem}

\begin{proof}
An endpoint-complete strong microscopic law is exactly a no-stage completion
law together with an aggregate endpoint-witness bundle on that same
completion law. Thus, once the completion law itself is unique on the fixed
bridge and physical principle, uniqueness of the strong microscopic package is
equivalent to uniqueness of the aggregate endpoint bundle carried by that
completion law. Replacing the strong-law clause by this equivalent endpoint-bundle
clause therefore does not change the exact bottleneck, and the same recovery
theorem yields the unique strong microscopic package together with the analytic
and equation surfaces.
\end{proof}

\begin{theorem}[The stronger endpoint-bundle bottleneck already yields the honest boundary-form candidate law]
\label{thm:canonical-boundary-microscopic-law-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalBoundaryMicroscopicLawTargetOfCanonicalStrongMicroscopicLawCompletionLawTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalBoundaryMicroscopicLawTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. If the exact canonical completion bottleneck holds,
then there is one unique no-stage completion law on the same selected bridge
and physical principle, and that same law
already carries the aggregate boundary target on its canonical
completion witness.

Hence the stronger endpoint-bundle bottleneck implies a cleaner candidate law:
one unique no-stage completion law together with boundary closure on that same
law. This boundary-form candidate law already yields one endpoint-complete
strong microscopic package on the same bridge and physical principle, and
therefore the analytic field surface and the exact physical equation field.
\end{theorem}

\begin{proof}
The stronger bottleneck already gives one unique no-stage completion law on the
selected bridge and physical principle. Its endpoint bundle determines the
aggregate boundary target on the canonical no-stage completion witness of that
same law. Thus the stronger bottleneck immediately yields the boundary-form
candidate law. Since the boundary target is itself a proposition on that fixed
witness, no second uniqueness clause is needed for the boundary datum. Once
this boundary-form candidate law is fixed, the established boundary-to-field
reconstruction theorem yields one endpoint-complete strong microscopic package,
hence the analytic and equation surfaces.
\end{proof}

\begin{theorem}[The boundary-form candidate law is exactly the unique completion law with automatic boundary closure]
\label{thm:canonical-completion-law-boundary-fill-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalCompletionLawBoundaryFillTarget_iff_canonicalBoundaryMicroscopicLawTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalCompletionLawBoundaryFillTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the following are equivalent:
\begin{enumerate}
\item there is one unique no-stage completion law on the selected bridge and
physical principle, and that same law carries the aggregate boundary
target on its canonical completion witness;
\item there is one unique no-stage completion law on the selected bridge and
physical principle, and every no-stage completion law on that same bridge and
physical principle automatically satisfies the aggregate boundary
target on its canonical completion witness.
\end{enumerate}
Hence the honest candidate law can be read in the sharper form:
one unique no-stage completion law, with boundary closure automatic across its
entire aligned completion class. This sharper form already yields one
endpoint-complete strong microscopic package, and therefore the analytic
field surface and the exact physical equation field.
\end{theorem}

\begin{proof}
If boundary closure is automatic for every aligned completion law, then it
holds in particular for the unique aligned completion law. Conversely, if the
unique aligned completion law already carries the boundary target, then every
other aligned completion law is equal to it by uniqueness, so the same
boundary target holds there as well. Thus the two formulations are exactly
equivalent. The established boundary-to-field reconstruction theorem then
supplies one endpoint-complete strong microscopic package and therefore the
analytic and equation surfaces.
\end{proof}

\begin{theorem}[The boundary-form candidate law is literally unique as a law object]
\label{thm:canonical-boundary-microscopic-law-object-target}\lean{ClosureCurrent.BoundaryMicroscopicLaw.eq_of_completionLaw_eq, ClosureCurrent.TerminalExactificationLaw.canonicalBoundaryMicroscopicLawObjectTargetOfCanonicalCompletionLawBoundaryFillTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalBoundaryMicroscopicLawObjectTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. If the exact candidate-law bottleneck holds in the
completion-law / boundary-fill form, then there is one unique boundary-form
microscopic law object on the selected bridge and physical principle.

In particular, the candidate law is now unique not only through its underlying
completion law but also as a literal law object. This unique boundary-form law
already yields one endpoint-complete strong microscopic package, and therefore
the analytic field surface and the exact physical equation field.
\end{theorem}

\begin{proof}
Once the aligned completion law is unique, any two boundary-form laws on that
same bridge and physical principle have the same completion law. Their
remaining boundary field is only a proposition on the canonical witness of that
law, so the two boundary-form laws are equal. Thus the candidate law itself is
literally unique. The established boundary-to-field reconstruction theorem
then yields one endpoint-complete strong microscopic package and hence the
analytic and equation surfaces.
\end{proof}

\begin{theorem}[The exact bottleneck is the unique candidate-law object with automatic aligned-class boundary closure]
\label{thm:canonical-boundary-microscopic-law-object-fill-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalBoundaryMicroscopicLawObjectFillTarget_iff_canonicalCompletionLawBoundaryFillTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalBoundaryMicroscopicLawObjectFillTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the following are equivalent:
\begin{enumerate}
\item there is one unique no-stage completion law on the selected bridge and
physical principle, and every aligned completion law automatically satisfies
the aggregate boundary target on its canonical witness;
\item there is one unique boundary-form microscopic law object on the
selected bridge and physical principle, and every aligned completion law
automatically satisfies the aggregate boundary target on its canonical
witness.
\end{enumerate}
Thus the exact remaining bottleneck can now be read directly as:
one unique candidate law object, together with automatic boundary closure
across the whole aligned completion-law class. This exact object-level form
already yields one endpoint-complete strong microscopic package, and therefore
the analytic field surface and the exact physical equation field.
\end{theorem}

\begin{proof}
If the exact bottleneck is given in completion-law form, the corresponding
boundary-form law object is unique because a boundary-form law is already
determined by its completion law. Conversely, if the unique boundary-form law
object is given together with automatic boundary closure on every aligned
completion law, then applying that automatic closure to an arbitrary aligned
completion law produces a boundary-form law object, and uniqueness of the law
object forces uniqueness of the underlying completion law. Hence the two
formulations are exactly equivalent. The established boundary-to-field
reconstruction theorem then yields one endpoint-complete strong microscopic
package and therefore the analytic and equation surfaces.
\end{proof}

\begin{theorem}[The stricter fixed-assembly route already forces one unique boundary law on the fixed assembly]
\label{thm:canonical-completion-boundary-law-target}\lean{ClosureCurrent.CompletionBoundaryLaw.eq_of_alignment_eq, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionBoundaryLawTargetOfCanonicalLawNativeAlignmentBoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalCompletionBoundaryLawTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume further the stricter fixed-assembly route
target: every aligned no-stage completion law collapses to the same
constructive sector law and the same fixed four-state assembly, and the
remaining Step~4 completion alignment on that fixed sector law is unique while
its reconstructed canonical witness already satisfies the aggregate boundary
target.

Then there is one unique smaller candidate law on that fixed four-state
assembly: one Step~4 alignment together with aggregate boundary closure on the
reconstructed canonical witness. Hence this unique fixed-assembly boundary law
already yields one endpoint-complete strong microscopic law on the same bridge
and physical principle, and therefore the analytic field surface and the exact
physical equation field.
\end{theorem}

\begin{proof}
Once the four-state assembly is fixed, the only remaining datum in
the smaller split completion law is the Step~4 alignment. By hypothesis that
alignment is unique. The remaining boundary field is a proposition on the
canonical witness reconstructed from the fixed assembly and that alignment, so
it carries no further independent choice. Thus the smaller fixed-assembly
boundary law is literally unique. The established boundary-to-field
reconstruction theorem then yields the strong microscopic law and hence the
analytic field surface and the exact physical equation field.
\end{proof}

\begin{theorem}[The stricter fixed-assembly route is exactly the same as uniqueness of the smaller Step~4 data]
\label{thm:canonical-law-native-parts-boundary-route-target}\lean{ClosureCurrent.CompletionAlignment.ofParts_eq, ClosureCurrent.CompletionAlignment.ofParts_toCompletionRigidity, ClosureCurrent.CompletionAlignment.ofParts_toCanonicalRepresentatives, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeAlignmentBoundaryRouteTargetOfCanonicalLawNativePartsBoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativePartsBoundaryRouteTargetOfCanonicalLawNativeAlignmentBoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativePartsBoundaryRouteTarget_iff_canonicalLawNativeAlignmentBoundaryRouteTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the stricter fixed-assembly route target is
equivalent to the following smaller statement:
\begin{enumerate}
\item every aligned no-stage completion law collapses to the same constructive
sector law and the same fixed four-state assembly;
\item the Step~4 rigidity datum is unique;
\item the canonical representative datum is unique;
\item the no-stage completion law reconstructed from those two smaller Step~4
data is already boundary-complete.
\end{enumerate}
Thus the only remaining Step~4 freedom in the stricter route is exactly the
pair consisting of the rigidity datum and the representative datum.
\end{theorem}

\begin{proof}
An aligned completion datum is rebuilt from exactly two smaller pieces: the
rigidity datum and the canonical representative datum. Reading those two
pieces from the rebuilt datum recovers them exactly, and rebuilding an aligned
completion datum from its own two pieces recovers the original alignment.
Therefore uniqueness of the alignment is equivalent to uniqueness of those two
smaller data. The boundary condition is imposed on the same
reconstructed completion law in either formulation, so no information is lost.
\end{proof}

\begin{theorem}[The stricter fixed-assembly route is also exactly the same as uniqueness of the rigidity principle, endpoint reduction, and representative datum]
\label{thm:canonical-law-native-rigidity-boundary-route-target}\lean{ClosureCurrent.CompletionRigidity.ofParts_eq, ClosureCurrent.CompletionRigidity.ofParts_toRigidityPrinciple, ClosureCurrent.CompletionRigidity.ofParts_toEndpointRigidity, ClosureCurrent.CompletionRigidity.eq_of_parts_eq, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativePartsBoundaryRouteTargetOfCanonicalLawNativeRigidityBoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeRigidityBoundaryRouteTargetOfCanonicalLawNativePartsBoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeRigidityBoundaryRouteTarget_iff_canonicalLawNativePartsBoundaryRouteTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the stricter fixed-assembly route target is also
equivalent to the following still smaller statement:
\begin{enumerate}
\item every aligned no-stage completion law collapses to the same constructive
sector law and the same fixed four-state assembly;
\item the endpoint-rigidity principle on the fixed intrinsic sector generation
is unique;
\item the reduced endpoint-rigidity datum is unique;
\item the canonical representative datum is unique;
\item the completion law reconstructed from those data is boundary-complete.
\end{enumerate}
Thus the only remaining Step~4 freedom in the stricter route is exactly the
endpoint-rigidity principle, the reduced endpoint-rigidity datum, and the
representative datum.
\end{theorem}

\begin{proof}
The intermediate rigidity datum is rebuilt from exactly two pieces: the
endpoint-rigidity principle on the fixed intrinsic sector generation and the
reduced endpoint-rigidity datum. Reading those two pieces from the rebuilt
rigidity datum recovers them exactly, and rebuilding the rigidity datum from
its own two pieces recovers the original datum. Therefore uniqueness of the
rigidity datum is equivalent to uniqueness of those two smaller pieces.
Combining this with the previous theorem shows that the stricter route is
equivalently expressed by the collapse clause together with uniqueness of the
endpoint-rigidity principle, the reduced endpoint-rigidity datum, and the
representative datum. The boundary condition is imposed on the same
reconstructed completion law in either formulation.
\end{proof}

\begin{theorem}[The remaining strict route splits into current-side collapse and a fixed-assembly Step~4 remainder]
\label{thm:canonical-law-native-rigidity-boundary-route-split}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeCompletionCollapseTarget_and_canonicalLawNativeStep4BoundaryRouteTarget_of_canonicalLawNativeRigidityBoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeRigidityBoundaryRouteTarget_of_canonicalLawNativeCompletionCollapseTarget_and_canonicalLawNativeStep4BoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeRigidityBoundaryRouteTarget_iff_canonicalLawNativeCompletionCollapseTarget_and_canonicalLawNativeStep4BoundaryRouteTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the remaining strict route target is exactly the
conjunction of two independent statements:
\begin{enumerate}
\item every aligned no-stage completion law on the selected bridge and
physical principle collapses to the same constructive sector law and the same
fixed four-state assembly;
\item on that fixed assembly, the endpoint-rigidity principle, the reduced
endpoint-rigidity datum, and the canonical representative datum are unique,
and the reconstructed completion law is boundary-complete.
\end{enumerate}
Thus the unresolved theorem no longer mixes the current-side collapse problem
with the Step~4 uniqueness problem.
\end{theorem}

\begin{proof}
This is only a regrouping of the already isolated strict route target. The
first conjunct is the current-side collapse clause from the smaller
rigidity-split route. The second conjunct is the remaining Step~4 datum on the
fixed sector law together with boundary closure on the reconstructed
completion law. Recombining those two pieces recovers the original strict
route verbatim.
\end{proof}

\begin{theorem}[The fixed-assembly Step~4 remainder is exactly one unique completion alignment]
\label{thm:canonical-law-native-step4-boundary-route-target-iff-canonical-law-native-alignment-boundary-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeAlignmentBoundaryTargetOfCanonicalLawNativeStep4BoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeStep4BoundaryRouteTargetOfCanonicalLawNativeAlignmentBoundaryTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeStep4BoundaryRouteTarget_iff_canonicalLawNativeAlignmentBoundaryTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the fixed-assembly Step~4 remainder is
equivalent to the statement that there is one unique completion alignment on
the fixed constructive sector law and that the reconstructed completion law is
already boundary-complete.
\end{theorem}

\begin{proof}
The forward direction compresses the low-level Step~4 data. The unique
endpoint-rigidity principle, the unique reduced endpoint-rigidity datum, and
the unique canonical representative datum rebuild one unique alignment, and
the boundary condition is imposed on the completion law reconstructed from
that alignment. Conversely, one unique alignment remembers exactly one
rigidity principle on the fixed intrinsic sector generation, exactly one
reduced endpoint-rigidity datum, and exactly one representative datum, so the
low-level Step~4 remainder is recovered verbatim.
\end{proof}

\begin{theorem}[The fixed-assembly endpoint-terminality remainder alone already forces the unique candidate law]
\label{thm:canonical-completion-boundary-law-target-of-canonical-law-native-step4-boundary-route-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalCompletionBoundaryLawTargetOfCanonicalLawNativeStep4BoundaryRouteTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. If the fixed-assembly endpoint-terminality remainder
holds, then there is one unique completion-boundary law on the constructive
sector law and the fixed four-state assembly.
\end{theorem}

\begin{proof}
The current-side collapse clause is not used here. The fixed-assembly Step~4
remainder is exactly one unique completion alignment together with boundary
closure on the completion law reconstructed from that alignment. That unique
alignment is exactly one completion-boundary law on the fixed assembly, and
uniqueness follows because such a law is determined by its alignment.
\end{proof}

\begin{theorem}[Selected-cut endpoint terminality is exactly one unique candidate law with automatic boundary closure]
\label{thm:canonical-completion-boundary-law-fill-target-iff-canonical-law-native-alignment-boundary-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalCompletionBoundaryLawFillTargetOfCanonicalLawNativeAlignmentBoundaryTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeAlignmentBoundaryTargetOfCanonicalCompletionBoundaryLawFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionBoundaryLawFillTarget_iff_canonicalLawNativeAlignmentBoundaryTarget, ClosureCurrent.TerminalExactificationLaw.selectedCutEndpointTerminalityTarget_iff_canonicalLawNativeAlignmentBoundaryTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionBoundaryLawFillTargetOfCanonicalLawNativeStep4BoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.selectedCutEndpointTerminalityTargetOfCanonicalLawNativeStep4BoundaryRouteTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the fixed-assembly alignment theorem is
equivalent to the following selected-cut endpoint-terminality statement:
\begin{enumerate}
\item there is one unique completion-boundary law on the constructive sector
law and the fixed four-state assembly;
\item every alignment on that same fixed sector law is already
boundary-complete on its reconstructed canonical witness.
\end{enumerate}
In particular, the fixed-assembly endpoint-terminality remainder alone already
forces this sharper unique candidate-law form.
\end{theorem}

\begin{proof}
If there is one unique alignment and the completion law reconstructed from it
is boundary-complete, then that alignment is already one completion-boundary
law on the fixed assembly. Any other alignment equals it, so the corresponding
reconstructed completion law is boundary-complete as well. Conversely, if
there is one unique completion-boundary law and every alignment is already
boundary-complete, then applying the unique law to the law built from any
other alignment forces that alignment to equal the distinguished one. Hence
the fixed-assembly remainder is exactly the same as one unique candidate law
together with automatic boundary closure across the whole alignment class on
that fixed assembly.
\end{proof}

\begin{theorem}[The remaining strict route is exactly current-side collapse plus selected-cut endpoint terminality]
\label{thm:canonical-law-native-alignment-boundary-route-target-iff-canonical-law-native-completion-collapse-target-and-canonical-completion-boundary-law-fill-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeCompletionCollapseTarget_and_canonicalCompletionBoundaryLawFillTarget_of_canonicalLawNativeAlignmentBoundaryRouteTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeAlignmentBoundaryRouteTarget_of_canonicalLawNativeCompletionCollapseTarget_and_canonicalCompletionBoundaryLawFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeAlignmentBoundaryRouteTarget_iff_canonicalLawNativeCompletionCollapseTarget_and_canonicalCompletionBoundaryLawFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeAlignmentBoundaryRouteTarget_iff_canonicalLawNativeCompletionCollapseTarget_and_selectedCutEndpointTerminalityTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the remaining strict route is equivalent to the
conjunction of:
\begin{enumerate}
\item current-side collapse of every aligned completion law to the same
constructive sector law and the same fixed four-state assembly;
\item selected-cut endpoint terminality on that fixed assembly: one unique
completion-boundary law there, together with automatic boundary closure across
its whole alignment class.
\end{enumerate}
Thus the strict remaining gap can now be read directly as current-side collapse
plus the selected-cut endpoint-terminality theorem.
\end{theorem}

\begin{proof}
The strict route is the conjunction of current-side collapse and the
fixed-assembly alignment theorem. The previous theorem identifies that
fixed-assembly theorem exactly with selected-cut endpoint terminality.
Substituting that equivalence yields the present form immediately.
\end{proof}

\begin{theorem}[Canonical selected completion]
\label{thm:canonical-selected-completion-target}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalSelectedCompletionTarget, ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeCompletionCollapseTarget_iff_canonicalLawNativeSectorCollapseTarget_and_canonicalLawNativeAssemblyFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalSelectedCompletionTarget_iff_canonicalLawNativeSectorCollapseTarget_and_canonicalLawNativeAssemblyFillTarget_and_canonicalCompletionBoundaryLawFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalSelectedCompletionTarget_iff_canonicalLawNativeCompletionCollapseTarget_and_selectedCutEndpointTerminalityTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfCanonicalSelectedCompletionTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the exact remaining upstream theorem can be
stated as a single canonical selected completion target:
\begin{enumerate}
\item every aligned completion law on the selected bridge and physical
principle collapses to the same constructive sector law;
\item once that smaller constructive sector law is fixed, the same aligned
completion laws all carry the same fixed four-state assembly;
\item on that fixed assembly there is one unique completion-boundary law, and
every alignment is already boundary-complete on its reconstructed
canonical witness.
\end{enumerate}
This single target is exactly equivalent to the remaining strict route, and
once it holds, the strong microscopic law, analytic field surface, and exact
physical equation field all follow.
\end{theorem}

\begin{proof}
The previous theorem already identified the strict route with the conjunction
of current-side collapse and selected-cut endpoint terminality. The current-side
clause itself now splits exactly into smaller sector-law collapse and
fixed-sector assembly fill, so the present statement is the sharpened
three-clause form of that same route. The downstream strong microscopic law
and analytic/equation surface then follow from the
candidate-law component alone.
\end{proof}

\begin{theorem}[A smaller strict route removes the full visible state-bridge object]
\label{thm:canonical-selected-completion-from-microscopic-current-boundary-route}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalSelectedCompletionTargetOfCanonicalLawNativeMicroscopicCurrentBoundaryRouteTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume:
\begin{enumerate}
\item every aligned completion law on the selected bridge and physical
principle already carries the same smaller constructive microscopic law as the
distinguished datum;
\item every aligned completion law already carries the same extracted
current-side data as the distinguished datum:
the same extracted four-state-assembly state bridge and the same three
explicit Step~3 fields;
\item on the fixed constructive sector law there is one unique completion
alignment, and its reconstructed completion law is boundary-complete.
\end{enumerate}
Then the canonical selected completion target follows.

In particular, the strict route no longer needs literal equality of the larger
local-event state-bridge datum; the smaller constructive microscopic law plus
the extracted current-side data already suffice.
\end{theorem}

\begin{proof}
The first two clauses force current-side completion collapse: the smaller
constructive microscopic law together with the explicit Step~3 fields force the
distinguished constructive sector law, and the extracted assembly state-bridge
clause then forces the distinguished four-state assembly. The third clause gives
the fixed-assembly completion-boundary law target. Combining these yields the
canonical selected completion target.
\end{proof}

\begin{theorem}[The extracted current-side data alone already force current-side collapse]
\label{thm:canonical-selected-completion-from-current-boundary-route}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeCompletionCollapseTargetOfCanonicalLawNativeCurrentSurfaceTarget, ClosureCurrent.TerminalExactificationLaw.canonicalSelectedCompletionTargetOfCanonicalLawNativeCurrentBoundaryRouteTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume:
\begin{enumerate}
\item every aligned completion law already carries the same extracted
four-state-assembly state bridge as the distinguished datum;
\item every aligned completion law already carries the same three explicit
Step~3 fields;
\item on the fixed constructive sector law there is one unique completion
alignment, and its reconstructed completion law is boundary-complete.
\end{enumerate}
Then the canonical selected completion target follows.

Equivalently, the extracted current-side data alone already force the whole
current-side collapse statement; no separate microscopic-collapse clause is
needed.
\end{theorem}

\begin{proof}
The extracted assembly state bridge already remembers the smaller constructive
microscopic law through its local-event object. Therefore the extracted
current-side data force the distinguished constructive sector law directly, and
then force the distinguished four-state assembly. The unique alignment clause again
gives the fixed-assembly completion-boundary law target, so the canonical
selected completion target follows.
\end{proof}

\begin{theorem}[A closed unique completion law already forces current-side collapse]
\label{thm:canonical-selected-completion-from-unique-completion-law-and-boundary-fill}\lean{ClosureCurrent.TerminalExactificationLaw.canonicalLawNativeCompletionCollapseTargetOfCanonicalCompletionLawTarget_and_canonicalCompletionBoundaryLawFillTarget, ClosureCurrent.TerminalExactificationLaw.canonicalSelectedCompletionTargetOfCanonicalCompletionLawTarget_and_canonicalCompletionBoundaryLawFillTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume:
\begin{enumerate}
\item there is one unique no-stage completion law on the selected bridge and
physical principle;
\item on the fixed constructive sector law and the fixed four-state
four-state assembly there is one unique completion-boundary law, and every
alignment is boundary-complete on its reconstructed canonical
witness.
\end{enumerate}
Then every aligned completion law already collapses to the same constructive
sector law, and once that smaller law is fixed the same aligned completion laws
all carry the same fixed four-state assembly.
Consequently the canonical selected completion target follows.
\end{theorem}

\begin{proof}
Choose the unique fixed-assembly completion-boundary law supplied by the second
clause, and let its alignment reconstruct the corresponding no-stage
completion law. This reconstructed law lies on the same bridge and physical
principle as the fixed microscopic law, so uniqueness in the first clause
identifies every aligned completion law with it. Because the reconstructed law
is built directly from the fixed constructive sector law and fixed four-state
assembly, both current-side objects are forced on every aligned completion
law. This is exactly current-side collapse. Combined with the fixed-assembly
boundary-law fill theorem, it yields the canonical selected completion target.
\end{proof}

\begin{theorem}[The fixed-assembly candidate-law target already gives one unique candidate law]
\label{thm:fixed-assembly-candidate-law-surface}\lean{ClosureCurrent.TerminalExactificationLaw.selectedCutEndpointTerminalitySurface, ClosureCurrent.TerminalExactificationLaw.candidateLawSurfaceOfCanonicalCompletionBoundaryLawFillTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume the fixed-assembly candidate-law target:
there is one unique completion-boundary law on the constructive sector law and
fixed four-state assembly, and every alignment is already boundary-complete on
its reconstructed canonical witness.

Then there is one literally unique candidate law on that fixed assembly. Its
reconstructed completion law already satisfies the full Part~IV completion
statement, and its canonical witness is already boundary-complete.
Consequently this same unique law determines an endpoint-complete strong
microscopic law on the same bridge and physical principle. Hence the analytic
field surface and the exact physical equation field already follow from that
unique candidate law.
\end{theorem}

\begin{proof}
The fixed-assembly target already contains the unique completion-boundary law.
Boundary-completeness is part of that law by construction. The boundary-to-
field theorem on its reconstructed completion law therefore yields the Part~IV
completion statement and, from the same completion law, an endpoint-complete
strong microscopic law. Because this reconstructed completion law lies on the
same selected bridge and physical principle, the analytic field surface and
exact physical equation field follow immediately.
\end{proof}

\begin{theorem}[The aggregate endpoint-bundle and frontier-bundle uniqueness targets are equivalent]
\label{thm:canonical-completion-witness-bundle-target-iff-canonical-completion-witness-frontier-bundle-target}\lean{ClosureCurrent.FlagshipEndpointWitnesses.toFrontiers_toEndpointWitnesses, ClosureCurrent.FlagshipFrontiers.toEndpointWitnesses_toFrontiers, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessFrontierBundleTargetOfCanonicalCompletionWitnessBundleTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTargetOfCanonicalCompletionWitnessFrontierBundleTarget, ClosureCurrent.TerminalExactificationLaw.canonicalCompletionWitnessBundleTarget_iff_canonicalCompletionWitnessFrontierBundleTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Then the following two uniqueness formulations on
the fixed microscopic law are equivalent:
\begin{enumerate}
\item there is one unique no-stage completion witness, and on that same witness
there is one unique aggregate endpoint-witness bundle;
\item there is one unique no-stage completion witness, and on that same witness
there is one unique aggregate frontier bundle.
\end{enumerate}
Thus the frontier-bundle bottleneck is not merely a sufficient reformulation of
the exact witness-level target; it is an equivalent one.
\end{theorem}

\begin{proof}
The exact endpoint bundle and the coarser frontier bundle are mutually
repackaged on one fixed completion witness, and each round-trip is the
identity. Therefore uniqueness of one bundle type on a unique witness forces
uniqueness of the other, and conversely. This identifies the two aggregate
uniqueness targets exactly.
\end{proof}

\begin{theorem}[One completion bridge with aggregate endpoint-witness data already recovers the strong microscopic law]
\label{thm:law-native-flagship-witness-bridge-recovers-the-strong-microscopic-package}\lean{ClosureCurrent.TerminalExactificationLaw.flagshipFrontierBridgeTargetOfWitnessBridgeTarget, ClosureCurrent.TerminalExactificationLaw.flagshipCompletionBridgeTargetOfWitnessBridgeTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfFlagshipWitnessBridgeTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfFlagshipWitnessBridgeTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume there exists one no-stage completion bridge on
the same microscopic law, and that the bridge's own no-stage completion
witness already carries one aggregate endpoint-witness bundle. Then this same
bridge already determines the aggregate frontier bundle and the aggregate
boundary target on that same witness. Hence one endpoint-complete strong
microscopic law already exists on that same microscopic law, and therefore the
analytic field surface and the exact physical equation field already follow
there.
\end{theorem}

\begin{proof}
The aggregate endpoint witness bundle on the bridge's own no-stage witness
repackages directly into the four frontier fields on that same selected
bundle. Those frontier fields in turn package into the aggregate boundary
target on the same witness. But the endpoint witness bundle itself already
defines the endpoint-complete strong microscopic law on the same completion
law. Since the bridge is fixed on the same microscopic law, the strong
microscopic law, the analytic field surface, and the exact physical equation
field follow immediately there.
\end{proof}

\begin{theorem}[One completion bridge carrying the four carrier frontiers already recovers the strong microscopic law]
\label{thm:law-native-flagship-frontier-bridge-recovers-the-strong-microscopic-package}\lean{ClosureCurrent.TerminalExactificationLaw.flagshipCompletionBridgeTargetOfFrontierBridgeTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfFlagshipFrontierBridgeTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfFlagshipFrontierBridgeTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume there exists one no-stage completion bridge on
the same microscopic law, and that this bridge carries the four textbook
carrier frontiers on its own intrinsically selected bundle. Then one
endpoint-complete strong microscopic law already exists on that same
microscopic law. Hence the analytic field surface and the exact physical
equation field already follow there.
\end{theorem}

\begin{proof}
The four actual carrier frontiers on the bridge's own no-stage completion
witness package into the aggregate boundary target on that same witness. So
the stronger frontier-bridge datum immediately implies the single
completion-bridge target with aggregate boundary closure. The preceding theorem
then applies directly and yields the strong microscopic law together with the
analytic field surface and exact physical equation field.
\end{proof}

\begin{theorem}[One completion bridge with aggregate boundary closure recovers the strong microscopic law]
\label{thm:law-native-flagship-completion-bridge-target-recovers-the-strong-microscopic-package}\lean{ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfFlagshipCompletionBridgeTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfFlagshipCompletionBridgeTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawOfBridgeBoundaryTarget, ClosureCurrent.TerminalExactificationLaw.strongMicroscopicLawSurfaceOfBridgeBoundaryTarget}
Assume the terminal exactification law on one fixed selected bridge of the
temporal realization law. Assume the single completion-bridge target with
aggregate boundary closure is realized: there exists one no-stage completion
bridge on the same fixed microscopic law, and on the corresponding no-stage
completion witness the aggregate boundary target is realized. Then one
endpoint-complete strong microscopic law already exists on that same
microscopic law. Hence the analytic field surface and the exact physical
equation field already follow there.
\end{theorem}

\begin{proof}
Unpack the single completion-bridge target into its fixed completion bridge and
the aggregate boundary target on that bridge's own no-stage completion
witness. The fixed bridge already determines that witness on the same
microscopic law. The boundary target on that
witness reassembles the exact endpoint witness package on the same no-stage
completion law, hence determines one endpoint-complete strong microscopic law
there. Therefore the analytic field surface and the exact physical equation
field follow there as well.
\end{proof}

\begin{theorem}[Endpoint completion law recovers the strong microscopic law]
\label{thm:endpoint-completion-law-recovers-the-strong-microscopic-package}\lean{ClosureCurrent.EndpointCompletionLaw.completionBridgeTarget, ClosureCurrent.EndpointCompletionLaw.strongMicroscopicLawSurface, ClosureCurrent.EndpointCompletionLaw.strongMicroscopicLawSurfaceOnLawNativeMicroscopicLaw}
Assume the endpoint completion law. Then on the same fixed microscopic law
there exists one endpoint-complete strong microscopic law whose completion law
lives on the same fixed selected bridge and physical principle. Hence the
analytic field surface and the exact physical equation field already follow
there.
\end{theorem}

\begin{proof}
Read the endpoint completion law on the fixed four-state assembly
determined by terminal exactification. In that fixed-assembly language, the
law is exactly one completion-boundary law on the same bridge and physical
principle. That completion-boundary law reconstructs one no-stage completion
law, and its boundary clause is precisely the aggregate boundary target on the
corresponding completion witness. Therefore one endpoint-complete
strong microscopic law exists on that same completion law. Terminal
exactification identifies the same bridge and physical principle with the
fixed microscopic law, so the analytic field surface and exact
physical equation field follow there.
\end{proof}

\paragraph{Open problem.}
The present Part~II formulation takes endpoint completion as an explicit third
law. It remains open whether this law is genuinely independent, or whether it
is already forced by temporal realization and terminal exactification through
a sharper intrinsic completion theorem on the fixed four-state assembly.

\begin{definition}[Detached completion datum]
\label{def:temporal-flagship-package}\lean{ClosureCurrent.DetachedFlagshipPackage}
A \emph{detached completion datum} consists of a temporal realization law
together with a detached no-stage local-event four-state completion law on the
same realized datum and the canonical phase, wave, gauge, and geometric carrier
realizations of that detached completion law.
\end{definition}

\begin{theorem}[Completion-side normal form of the detached completion datum]
\label{thm:completion-side-normal-form-of-the-temporal-realization-law}\lean{ClosureCurrent.DetachedFlagshipPackage.toCoherentRealizationNormalForm, ClosureCurrent.CoherentRealizationNormalForm.surface, ClosureCurrent.DetachedFlagshipPackage.completionNormalFormSurface}
Assume a detached completion datum. Then on that same selected datum it already
fixes one no-stage local-event four-state completion law together with the
exact phase, wave, gauge, and geometric endpoint-witness data. This is a
completion-side normal form used later as an alternative formulation, and it is
not part of the stated Part~II law.
\end{theorem}

\begin{proof}
By definition the detached completion datum carries one temporal realization
law together with a detached no-stage completion law on the same realized
datum and the canonical carrier-realization data of that detached completion
law.
Read in the detached completion language, those data are exactly the
completion-side normal form.
\end{proof}

The temporal realization and terminal exactification laws form the
two-law base formulation of Part~II. Their content is already explicit on
one common datum: the observed bundle on the realized class, the exact
visible law on that realized bundle, the exchange/return source structure,
exact internal elimination, least-motion selection on the realized class, self-sufficient
selected-cut closure, and terminal exactification on fixed selected bridges.
The base formulation therefore closes the selected-cut realization statement
and the exactified generator-fixed seam on the same bridge. Even before
endpoint completion is added, the fixed-bridge law formulation already
certifies the realized bedrock recurrence profile: bedrock law on the matched
selected generator, the unique \(D=3\) residual interface, the
six-slot balanced carrier, and the canonical \([3,2,1]\) intrinsic profile.

The endpoint completion law closes the remaining microscopic endpoint seam on
that same bridge. Read on the fixed assembly, it is exactly one
completion-boundary law on the same bridge and physical principle. The
preceding theorem therefore yields one endpoint-complete strong microscopic
law and hence the analytic formulation and the exact physical equation field.

A detached completion datum is a different completion-side presentation on the
same realized datum: it specifies a detached no-stage completion law together
with the canonical carrier realizations of that detached completion law. It is
useful later as a completion-side normal form, but it is stronger than the
first two laws alone and is not presently derived from them. The recognizable
Schr\"odinger, wave/Klein--Gordon, Maxwell, and Einstein equations may then
also be read as canonical carrier realizations of that completion law.

On the realized cut the observable dynamics are exactly the selected visible
effective law. Admissible visible forcing is only returned residual from the
same coherent bundle, observable irreversibility is unrecovered residual, and
no exogenous constitutive completion is admitted. The carrier laws developed
later depend only on inherited compatibility identities, admissibility,
minimal-order forcing, characteristic reduction, exact return elimination, and
continuum identification. Geometry enters later as one intrinsic carrier
realization of this common physical-law structure, not as the foundational
language on which the rest of Part~II is built.

\subsection{Current Objects on the Selected Cut}
\label{sec:detached-current-build}

The detached current formulation begins with a local closure-stable bulk event
\(e\), its leg set \(L_e\), and one pair-exchange carrier \(A_e\) with reversal
involution \(\rho_e\) and observable \(s_e\). The hidden local current is then
the oriented pair-current
\[
j_e : L_e \times L_e \to A_e,
\qquad
j_e(a,a)=0,
\qquad
j_e(b,a)=\rho_e(j_e(a,b)).
\]
The event exactifier acts on that current and returns the unresolved remainder;
schematically,
\[
E_e(j_e)=\text{exactified current},
\qquad
R_e(j_e)=\text{returned defect}.
\]
Carrier-specific dynamics are read not directly from \(j_e\), but from
role-indexed autonomous minimal quotients
\[
q_r(j_e),
\qquad
r \in \{\mathrm{phase},\mathrm{wave},\mathrm{gauge},\mathrm{geometric}\}.
\]
Finally one chooses the selected observer as anchor, reads the quotient values
there, and transports the selected closure identity from that anchor to
the full selected cut. This is the full detached construction:
\[
\begin{aligned}
\text{pair current}
&\;\Longrightarrow\;
\text{local exactifier and returned defect}
\;\Longrightarrow\;
\text{visible quotients},
\\
&\;\Longrightarrow\;
\text{selected-observer anchor}
\;\Longrightarrow\;
\text{selected-cut transport}.
\end{aligned}
\]

\begin{theorem}[Detached current construction ladder]
\label{thm:detached-current-build-ladder}\lean{ClosureCurrent.LocalEventObject.surface, ClosureCurrent.CurrentAnchor.surface, ClosureCurrent.AnchoredCurrentTransport.surface, ClosureCurrent.AnchoredCurrentObject.surface}
The detached closure-current formulation proceeds in four mathematically
distinct steps.
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item The pair-exchange current object already determines a genuine local event
      current together with exactification, returned defect, and autonomous
      carrier quotients.
\item Evaluating those quotients at the selected observer yields a
      current anchor carrying exact visibility and the forced continuum
      singleton at that anchor.
\item Adding anchored transport extends that anchored closure identity from the
      selected observer to every observer reading the same selected cut,
      without changing any current-side fact.
\item Supplementing the transported anchor by the remaining
      structural/intrinsicity
      clauses recovers the full observer-realized detached current object, and
      therefore the reduced selected-bundle conclusion used later in the
      chapter.
\end{enumerate}
\end{theorem}

\begin{proof}
Item (i) is exactly the local current datum: one has a nonempty pair
current, direct/return compatibility, local exactification with returned
defect, and autonomous carrier quotients. Item (ii) then specializes that
local datum to the selected observer. At that anchor the selected
visible law and the selected closure class are already identified, so exact
visibility and the forced continuum singleton are read there directly.

Item (iii) adds only the common closure transport from that anchor to every
observer reading the same selected cut. No new current-side fact is introduced
at this step. Item (iv) then adds the remaining structural/intrinsicity clauses
and reads the visible quotients on the transported selected cut, recovering the
observer-realized detached current object and hence the reduced selected-bundle
conclusion used later in the chapter.

Thus the detached formulation is a genuine construction sequence: first the
local current, then its selected anchor, then transport across the selected
cut, and finally the observer-realized law read from that transported anchor.
\end{proof}

\begin{remark}[Appendix factorization of the construction ladder]
After Theorem~\ref{thm:detached-current-build-ladder}, the remaining detached
definitions factor this construction ladder into smaller interfaces. The
appendix verifies that each smaller datum recovers the next conclusion in the
chain and that the same selected-cut closure statements survive each
compression.
\end{remark}

\subsection{Compact Law Form}
\label{sec:detached-current-law-form}

The detached current formulation now admits a first compact equation form.
Write
\[
\Gamma := E_e,
\qquad
C_r := q_r,
\qquad
T_r := \tau_r,
\qquad
\Delta_r := C_r \circ R_e,
\]
where \(E_e\) is the local exactifier on the pair current \(j_e\), \(q_r\) is
the visible channel observable for the role \(r\), \(\tau_r\) is the
autonomous transport on that visible channel, and \(R_e\) is the
returned-defect current. Then the microscopic current law takes the
generator/transport/channel form
\[
C_r(\Gamma j_e)=T_r(C_r(j_e)),
\qquad
\Delta_r(j_e)=C_r(R_e(j_e)).
\]
This is the first compact law equation in the detached formulation. It is
still abstract, not yet a PDE or explicit carrier realization. But it is
already a genuine law equation rather than only a list of auxiliary
structures.

\begin{definition}[Detached local law form]
\label{def:detached-local-law-form}\lean{ClosureCurrent.LocalEventLawForm}
A \emph{detached local law form} is a detached pair-exchange current object
together with the rolewise transport-compatibility statement
\[
C_r(\Gamma j)=T_r(C_r(j))
\]
for every visible role \(r\) and every local pair current \(j\). The returned
defect on the same role is then read as \(\Delta_r(j)=C_r(R_e(j))\).
\end{definition}

\begin{theorem}[Detached local law form yields the compact equation]
\label{thm:detached-flagship-law-form}\lean{ClosureCurrent.LocalEventLawForm.surface}
On any detached local law form, the hidden pair current carries
direct/return compatibility, every visible role is an autonomous minimal
quotient, and the rolewise generator/transport/channel equation
\[
C_r(\Gamma j)=T_r(C_r(j)),
\qquad
\Delta_r(j)=C_r(R_e(j))
\]
holds for every visible role \(r\) and every local pair current \(j\).
\end{theorem}

\begin{proof}
The underlying object is still the local pair current with its direct/return
compatibility and its autonomous minimal visible quotients. The new ingredient
is the rolewise commutation law between the generator and the visible channel
transport. Its first equation is precisely
\[
C_r(\Gamma j)=T_r(C_r(j)),
\]
while its second equation is the definitional identity saying that the visible
residual \(\Delta_r\) is the same role quotient map applied to the returned-defect
current \(R_e(j)\).
\end{proof}

\begin{theorem}[Selected-cut law equation from the detached current object]
\label{thm:selected-cut-detached-flagship-law}\lean{ClosureCurrent.AnchoredLawForm.surface}
If the detached local law form is carried by an anchored detached current
object, then the same equation already defines a selected-cut law equation. More
precisely, on the selected bridge observer one has exact visibility and the
forced continuum singleton for the selected closure law; that closure identity
then transports to every observer reading the same selected cut; and
\[
C_r(\Gamma j)=T_r(C_r(j)),
\qquad
\Delta_r(j)=C_r(R_e(j))
\]
still holds for every visible role \(r\) and every local pair current \(j\).
\end{theorem}

\begin{proof}
This combines two facts already established. First, the anchored object yields
exact visibility on the selected bridge observer, forced continuum closure
there, and transport of that same closure class to every observer reading the
selected cut. Second, forgetting the transport data leaves the local detached
law form, so the rolewise generator/transport equation and the visible
residual identity still hold. Putting the two together gives exactly the
selected-cut law equation claimed here.
\end{proof}

\begin{definition}[Channel-compatible detached current object]
\label{def:channel-compatible-detached-current-object}\lean{ClosureCurrent.ChannelLocalEventObject, ClosureCurrent.ChannelAnchoredObject}
A \emph{channel-compatible detached current object} is a detached current
object on which the quotient objects themselves already satisfy the rolewise
exactifier-compatibility law
\[
C_r(\Gamma j)=T_r(C_r(j)).
\]
At the local level this upgrades the detached pair-exchange current object; at
the anchored selected-cut level it upgrades the anchored detached current
object.
\end{definition}

\begin{theorem}[Channel-compatible current object forces the compact law]
\label{thm:channel-compatible-current-object-forces-the-flagship-law}\lean{ClosureCurrent.ChannelLocalEventObject.surface, ClosureCurrent.ChannelAnchoredObject.surface}
On a channel-compatible detached current object, the compact law equation is
forced.
Locally this yields the compact law form
\[
C_r(\Gamma j)=T_r(C_r(j)),
\qquad
\Delta_r(j)=C_r(R_e(j)),
\]
and on the anchored selected cut it yields the same equation together with
exact visibility on the selected bridge observer and transported continuum
closure on the full selected cut.
\end{theorem}

\begin{proof}
Once the exactifier/quotient compatibility is carried by the current object
itself, the compact law equation follows directly from the object rather than
from an additional law datum. Passing from the local object to the
anchored selected-cut object preserves the same equation and adds the already
known selected-cut facts: exact visibility at the selected bridge observer and
closure transport along the full selected cut.
\end{proof}

\begin{definition}[Autonomous realized detached current object]
\label{def:autonomous-realized-detached-current-object}\lean{ClosureCurrent.AutonomousStateField, ClosureCurrent.AutonomousAnchoredCurrentObject}
Fix an anchored detached current object with matched selected generator \(X\)
and selected projection \(\pi\). An \emph{autonomous realized detached current
object} consists of a realization \(\rho\) of the hidden pair current as a
selected-cut state, together with for each visible role \(r\):
\begin{enumerate}
\item an injective realization \(s_r\) of visible quotient values as
projection-fixed states;
\item the observation factorization
\[
s_r(C_r(j))=\pi(\rho(j));
\]
\item an autonomous state law \(L_r\) on the same selected cut for the matched
generator \(X\);
\item the realized visible transport law
\[
s_r(T_r(v))=L_r(s_r(v)).
\]
\end{enumerate}
The current realization is required to intertwine the local exactifier with the
matched selected generator:
\[
\rho(\Gamma j)=X(\rho(j)).
\]
\end{definition}

\begin{theorem}[Autonomy forces the detached law equation]
\label{thm:autonomy-forces-the-detached-flagship-equation}\lean{ClosureCurrent.VisibleStateLaw.transportCompatible, ClosureCurrent.AutonomousAnchoredCurrentObject.surface}
On an autonomous realized detached current object, the compact law equation is
forced rather than postulated:
\[
C_r(\Gamma j)=T_r(C_r(j)),
\qquad
\Delta_r(j)=C_r(R_e(j)).
\]
On the anchored selected cut, the same object still carries exact visibility on
the selected bridge observer and transported continuum closure on the full
selected cut. Moreover the realized visible law agrees pointwise with the
matched selected generator on realized visible states:
\[
L_r(s_r(v))=X(s_r(v)).
\]
\end{theorem}

\begin{proof}
The visible transport equation is now derived from a realized autonomous law
on the selected cut. For a fixed visible role \(r\), let \(s_r\) be the
realized visible state, let \(\rho\) be the realized current state, and let
\(L_r\) be the autonomous state law. Then
\[
\begin{aligned}
s_r(C_r(\Gamma j))
  &= \pi(\rho(\Gamma j)) \\
  &= \pi(X(\rho(j))) \\
  &= L_r(\pi(\rho(j))) \\
  &= L_r(s_r(C_r(j))) \\
  &= s_r(T_r(C_r(j))).
\end{aligned}
\]
The first and fourth identities are the observation factorization
\(s_r(C_r(j))=\pi(\rho(j))\). The second is the current realization of the
exactifier, \(\rho(\Gamma j)=X(\rho(j))\). The third is exactly the autonomy
factorization on the selected cut. The fifth is the realized visible transport
law \(s_r(T_r(v))=L_r(s_r(v))\). Since \(s_r\) is injective, this yields
\(C_r(\Gamma j)=T_r(C_r(j))\). The residual identity
\(\Delta_r(j)=C_r(R_e(j))\) remains the same definitional quotient map of the
returned-defect current. The pointwise agreement
\[
L_r(s_r(v))=X(s_r(v))
\]
is the selected-cut autonomy uniqueness statement on projection-fixed visible
states. Together with exact visibility and transported continuum closure, this
gives the asserted selected-cut law statement.
\end{proof}

\begin{theorem}[Autonomy yields a unified state field]
\label{thm:autonomy-collapses-to-a-unified-state-field}\lean{ClosureCurrent.AutonomousAnchoredCurrentObject.unifiedSurface}
Any autonomous realized detached current object already determines a unified
detached state field. In particular, the role-indexed visible laws are not
independent extra dynamics: on realized visible states they all collapse to the
same matched selected generator \(X\).
\end{theorem}

\begin{proof}
Autonomy uniqueness on projection-fixed visible states replaces each
role-indexed law \(L_r\) by the same matched selected generator \(X\). The
result is exactly the unified state-field datum of
Definition~\ref{def:unified-detached-state-field}.
\end{proof}

\begin{definition}[Unified detached state field]
\label{def:unified-detached-state-field}\lean{ClosureCurrent.UnifiedStateField, ClosureCurrent.UnifiedAnchoredCurrentObject}
A \emph{unified detached state field} is an anchored detached current object
equipped with one common selected-cut state realization \(\rho\) of the hidden
pair current and one common ambient state realization \(s_r\) of each visible
role, such that every visible role is transported by the same matched selected
generator \(X\):
\[
\rho(\Gamma j)=X(\rho(j)),
\qquad
s_r(T_r(v))=X(s_r(v)).
\]
The role-indexed visible laws are therefore no longer primitive data; they are
all read through one common ambient state evolution.
\end{definition}

\begin{theorem}[Unified state field forces the detached law equation]
\label{thm:unified-state-field-forces-the-detached-flagship-equation}\lean{ClosureCurrent.UnifiedStateField.transportCompatible, ClosureCurrent.UnifiedAnchoredCurrentObject.surface}
On a unified detached state field, the detached law equation is forced by
one common selected-cut generator, not by separate role-indexed laws:
\[
C_r(\Gamma j)=T_r(C_r(j)),
\qquad
\Delta_r(j)=C_r(R_e(j)).
\]
Moreover every visible role is transported by that same matched selected
generator on its realized visible states:
\[
X(s_r(v))=s_r(T_r(v)).
\]
\end{theorem}

\begin{proof}
The proof is the same selected-cut autonomy argument as before, but now the
role-indexed visible law \(L_r\) has disappeared: the matched selected
generator \(X\) itself transports all realized visible roles. For a fixed role
\(r\),
\[
\begin{aligned}
s_r(C_r(\Gamma j))
  &= \pi(\rho(\Gamma j)) \\
  &= \pi(X(\rho(j))) \\
  &= X(\pi(\rho(j))) \\
  &= X(s_r(C_r(j))) \\
  &= s_r(T_r(C_r(j))).
\end{aligned}
\]
The third identity is now the selected-cut autonomy law for the matched
generator itself, rather than a separate visible law. Injectivity of \(s_r\)
again yields \(C_r(\Gamma j)=T_r(C_r(j))\), while the residual identity remains
the same returned-defect observation. Together with exact visibility on the
selected bridge observer and transported continuum closure on the full
selected cut, this gives the claimed unified state-field conclusion.
\end{proof}

\subsection{Explicit State Assembly of the Hidden Current}
\label{sec:detached-current-state-assembly}

The unified detached state field already says that there is one common hidden
state \(\rho(j)\) on the selected cut. The next reduction is to make
that state explicit. Fix a signed observable \(\chi_e\) of the pair-current
carrier into signed counts, satisfying
\[
\chi_e(0)=0,
\qquad
\chi_e(\rho_e x)=-\chi_e(x),
\]
and fix a genuine four-leg frame
\((\lambda_0,\lambda_1,\lambda_2,\lambda_3)\)
for the first closure-stable bulk event. Then the signed leg-flux observable of a
pair current \(j_e\) at a leg \(\lambda\) is
\[
\Phi_\lambda(j_e)
:=
\chi_e(j_e(\lambda,\lambda_0))
\;+\;
\chi_e(j_e(\lambda,\lambda_1))
\;+\;
\chi_e(j_e(\lambda,\lambda_2))
\;+\;
\chi_e(j_e(\lambda,\lambda_3)).
\]
This gives a concrete hidden state on the selected cut:
\[
\rho_{\mathrm{asm}}(j_e)
:=
\bigl(
\Phi_{\lambda_0}(j_e),
\Phi_{\lambda_1}(j_e),
\Phi_{\lambda_2}(j_e),
\Phi_{\lambda_3}(j_e)
\bigr)\in \operatorname{State}.
\]
So the hidden current is no longer represented by an arbitrary map
\(\rho : j \mapsto \operatorname{State}\); it is read by legwise signed pair flux on the
framed local event.

\begin{definition}[Explicit detached current-state assembly]
\label{def:explicit-detached-current-state-assembly}\lean{ClosureCurrent.SignedExchangeReadout, ClosureCurrent.FourLegFrame, ClosureCurrent.CurrentStateAssembly, ClosureCurrent.AssembledUnifiedStateField, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject}
An \emph{explicit detached current-state assembly} consists of:
\begin{enumerate}
\item a signed observable \(\chi_e\) of pair-current values into
      \(\operatorname{SignedCount}\), compatible with zero and reversal;
\item a four-leg frame
      \((\lambda_0,\lambda_1,\lambda_2,\lambda_3)\) for the local
      closure-stable bulk event;
\item the assembled hidden state \(\rho_{\mathrm{asm}}(j_e)\in\operatorname{State}\) defined
      by the four leg-flux sums above;
\item the intertwining law
\[
\rho_{\mathrm{asm}}(\Gamma j)=X(\rho_{\mathrm{asm}}(j))
\]
      between the local exactifier and the matched selected generator;
\item realized visible states \(s_r\) for the quotient roles, with the same
      selected-cut factorization and visible transport identities as in the
      unified state-field datum.
\end{enumerate}
\end{definition}

\begin{theorem}[Explicit current-state assembly yields the unified law equation]
\label{thm:explicit-current-state-assembly-forces-the-unified-flagship-surface}\lean{ClosureCurrent.CurrentStateAssembly.surface, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.surface}
On an explicit detached current-state assembly, the hidden current-state map is
literally the assembled legwise signed flux
\[
\rho_{\mathrm{asm}}(j_e)
=
\bigl(
\Phi_{\lambda_0}(j_e),
\Phi_{\lambda_1}(j_e),
\Phi_{\lambda_2}(j_e),
\Phi_{\lambda_3}(j_e)
\bigr),
\]
and the same unified selected-cut law statement follows:
\[
C_r(\Gamma j)=T_r(C_r(j)),
\qquad
\Delta_r(j)=C_r(R_e(j)).
\]
In particular, the detached hidden state is now carried by an explicit
four-coordinate current assembly rather than an opaque map
\(\operatorname{PairExchangeCurrent}\to\operatorname{State}\).
\end{theorem}

\begin{proof}
The displayed formula for \(\rho_{\mathrm{asm}}(j_e)\) simply evaluates the
signed observable of the pair current against each framed leg and collects the
four resulting signed counts into one state in \(\operatorname{State}\). The
current assembly therefore gives an explicit hidden-state realization together
with the exactifier/generator intertwining law
\[
\rho_{\mathrm{asm}}(\Gamma j)=X(\rho_{\mathrm{asm}}(j)).
\]
Reading the unified state field through this explicit assembly then yields the
same selected-cut consequences as
Theorem~\ref{thm:unified-state-field-forces-the-detached-flagship-equation}.
\end{proof}

\begin{theorem}[Explicit current assembly is balanced]
\label{thm:explicit-current-assembly-is-balanced}\lean{ClosureCurrent.assembledState_total_zero, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentBalance}
The explicit assembled hidden current state is automatically balanced:
\[
\Phi_{\lambda_0}(j_e)+
\Phi_{\lambda_1}(j_e)+
\Phi_{\lambda_2}(j_e)+
\Phi_{\lambda_3}(j_e)=0.
\]
Equivalently, the explicit hidden current-state map already lands in a
zero-sum sector of \(\operatorname{State}\). The detached closure current
therefore does not produce an arbitrary four-coordinate state; it produces a
balanced one.
\end{theorem}

\begin{corollary}[Explicit current assembly factors through the balanced sector]
\label{thm:explicit-current-assembly-factors-through-balanced-sector}\lean{ClosureCurrent.CurrentStateAssembly.balancedSurface, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentBalancedState, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentBalancedSurface}
Under an explicit detached current-state assembly, the hidden current-state map
factors through the balanced zero-sum sector
\[
\operatorname{BalancedState}
:=
\{x\in\operatorname{State} : x_0+x_1+x_2+x_3=0\}.
\]
Equivalently, there is a balanced hidden current state
\[
\rho_{\mathrm{bal}}(j_e)\in\operatorname{BalancedState}
\]
whose forgetful image is exactly the explicit assembled state
\(\rho_{\mathrm{asm}}(j_e)\in\operatorname{State}\). Moreover the same
exactifier/generator law survives after forgetting back to
\(\operatorname{State}\):
\[
\rho_{\mathrm{bal}}(\Gamma j_e)_{\mathrm{forget}}
=
X(\rho_{\mathrm{bal}}(j_e)_{\mathrm{forget}}).
\]
\end{corollary}

\begin{proof}
The pointwise balance identity shows that the explicit current assembly already
lands in the zero-sum sector. So the state map factors through
\(\operatorname{BalancedState}\), and the exactifier/generator identity
survives after forgetting back to \(\operatorname{State}\). That is exactly the
balanced-sector factorization claimed here.
\end{proof}

\begin{corollary}[Explicit hidden current law closes on the balanced sector]
\label{thm:explicit-hidden-current-law-closes-on-the-balanced-sector}\lean{ClosureCurrent.CurrentStateAssembly.generator_preserves_balance, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentBalancedClosure}
Under an explicit detached current-state assembly, the matched selected
generator preserves the balanced hidden current sector on realized current
states:
\[
\operatorname{stateTotal}
\bigl(
X(\rho_{\mathrm{bal}}(j_e)_{\mathrm{forget}})
\bigr)
=
0.
\]
Equivalently, the detached hidden current law closes internally on the
balanced zero-sum sector traced by the explicit current assembly.
\end{corollary}

\begin{proof}
The balanced current state \(\rho_{\mathrm{bal}}(j_e)\) is already known to
factor through \(\operatorname{BalancedState}\), so
\(\rho_{\mathrm{bal}}(\Gamma j_e)\) is balanced as well. But
Corollary~\ref{thm:explicit-current-assembly-factors-through-balanced-sector}
identifies its forgetful image with
\(X(\rho_{\mathrm{bal}}(j_e)_{\mathrm{forget}})\). Therefore the matched
selected generator sends every realized balanced hidden current state to
another balanced state. This is formalized at the assembly level by
\lean{ClosureCurrent.CurrentStateAssembly.generator_preserves_balance} and in
the packaged anchored form by
\lean{ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentBalancedClosure}.
\end{proof}

\begin{definition}[Reduced balanced hidden-state carrier]
\label{def:reduced-balanced-hidden-state-carrier}\lean{ClosureCurrent.BalancedCoordinates}
The \emph{reduced balanced hidden-state carrier} is the three-coordinate signed
carrier
\[
\operatorname{BalancedCoordinates}
=
\{(x_0,x_1,x_2)\},
\]
equipped with the forced fourth coordinate
\[
x_3
:=
-(x_0+x_1+x_2).
\]
It therefore reconstructs a balanced four-state by
\[
(x_0,x_1,x_2)
\longmapsto
(x_0,x_1,x_2,-(x_0+x_1+x_2)).
\]
\end{definition}

\begin{corollary}[Explicit hidden current reduces to three coordinates]
\label{thm:explicit-hidden-current-reduces-to-three-coordinates}\lean{ClosureCurrent.BalancedCoordinates.toBalancedState, ClosureCurrent.CurrentStateAssembly.coordinateSurface, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentCoordinates, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentCoordinateSurface}
Under an explicit detached current-state assembly, the hidden current factors
through the reduced three-coordinate carrier
\[
\rho_3(j_e)
:=
\bigl(
\Phi_{\lambda_0}(j_e),
\Phi_{\lambda_1}(j_e),
\Phi_{\lambda_2}(j_e)
\bigr)\in\operatorname{BalancedCoordinates},
\]
and the fourth coordinate is forced by
\[
\Phi_{\lambda_3}(j_e)
=
-
\bigl(
\Phi_{\lambda_0}(j_e)+
\Phi_{\lambda_1}(j_e)+
\Phi_{\lambda_2}(j_e)
\bigr).
\]
Equivalently, the balanced hidden current state is exactly the reconstruction
of this three-coordinate carrier, and the exactifier/generator identity survives
after that reconstruction.
\end{corollary}

\begin{proof}
The first three signed coordinates determine the fourth by the balance
condition, so they already form a complete carrier for the hidden current.
Reconstruction to the balanced four-state is therefore exact, and the current
assembly factors through this reduced carrier without loss. The selected-cut
transport law survives under that reconstruction, so the reduced coordinates
carry exactly the same hidden-current evolution as the full balanced state.
\end{proof}

\begin{corollary}[Reduced hidden current transport law]
\label{thm:reduced-hidden-current-transport-law}\lean{ClosureCurrent.BalancedCoordinates.transport, ClosureCurrent.CurrentStateAssembly.coordinateTransport, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentCoordinateTransport}
The reduced hidden current carrier carries its own three-coordinate transport
law:
\[
\rho_3(\Gamma j_e)
=
\Pi_3\!\bigl(X(\iota(\rho_3(j_e)))\bigr),
\]
where \(\iota\) reconstructs the balanced four-state from the reduced carrier
and \(\Pi_3\) reads back the first three coordinates. Equivalently, the reduced
hidden current evolves by reconstructing to the balanced four-state, applying
the matched selected generator, and projecting back to three coordinates.
\end{corollary}

\begin{proof}
Exactification transports the full balanced hidden state by the matched
selected generator. Passing to the reduced carrier therefore amounts to three
steps only: reconstruct the balanced four-state, transport it by the matched
generator, and project back to the first three coordinates. That is exactly the
formula displayed in the statement.
\end{proof}

\begin{definition}[Reduced hidden-current discrete trajectory]
\label{def:reduced-hidden-current-discrete-trajectory}\lean{ClosureCurrent.AnchoredCurrentObject.exactifyIterate, ClosureCurrent.CurrentStateAssembly.coordinateIterate, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentCoordinateIterate}
The \emph{reduced hidden-current discrete trajectory} consists of two parallel
iterates:
\[
j_e^{(n)} := \Gamma^{[n]} j_e,
\qquad
\rho_3^{(n)} := T_3^{[n]} \rho_3(j_e),
\]
where \(\Gamma^{[n]}\) denotes \(n\) repeated local exactification steps and
\(T_3\) is the reduced three-coordinate transport map
\[
T_3(\rho) := \Pi_3\!\bigl(X(\iota(\rho))\bigr).
\]
Thus the detached reduced law already carries a discrete update rule on the
three-coordinate hidden carrier.
\end{definition}

\begin{corollary}[Reduced hidden current carries an exact discrete trajectory law]
\label{thm:reduced-hidden-current-discrete-trajectory-law}\lean{ClosureCurrent.CurrentStateAssembly.coordinateTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentCoordinateTrajectory}
Under an explicit detached current-state assembly, the reduced hidden current
satisfies the exact \(n\)-step law
\[
\rho_3(\Gamma^{[n]} j_e)
=
T_3^{[n]}(\rho_3(j_e)).
\]
Equivalently, iterating the microscopic exactifier on the hidden current agrees
exactly with iterating the reduced three-coordinate transport map. This is the
first detached law surface that is already structurally ready for a finite-step
simulation once concrete coordinate representatives are chosen.
\end{corollary}

\begin{proof}
The one-step reduced transport law from
Corollary~\ref{thm:reduced-hidden-current-transport-law} is
\[
\rho_3(\Gamma j_e)=T_3(\rho_3(j_e)).
\]
The \(n\)-step formula follows by induction on \(n\). The case \(n=0\) is
immediate. If
\(\rho_3(\Gamma^{[n]}j_e)=T_3^{[n]}(\rho_3(j_e))\),
then
\[
\rho_3(\Gamma^{[n+1]}j_e)
=
\rho_3(\Gamma(\Gamma^{[n]}j_e))
=
T_3(\rho_3(\Gamma^{[n]}j_e))
=
T_3\bigl(T_3^{[n]}(\rho_3(j_e))\bigr)
=
T_3^{[n+1]}(\rho_3(j_e)).
\]
So iterating the microscopic exactifier and iterating the reduced transport
agree exactly.
\end{proof}

\begin{corollary}[Selected observed state carries an exact discrete trajectory law]
\label{thm:selected-observed-state-discrete-trajectory-law}\lean{ClosureCurrent.CurrentStateAssembly.observedState, ClosureCurrent.CurrentStateAssembly.observedTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentObservedState, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentObservedTrajectory}
The explicit detached current assembly also induces a canonical selected
observed state
\[
\rho_{\mathrm{sel}}(j_e)
:=
\Pi_{\mathrm{sel}}(\rho(j_e)),
\]
and that selected observed state satisfies the exact \(n\)-step law
\[
\rho_{\mathrm{sel}}(\Gamma^{[n]} j_e)
=
X^{[n]}(\rho_{\mathrm{sel}}(j_e)).
\]
Equivalently, once the hidden current is assembled into a state, projection to
the selected cut already gives an exact discrete observed trajectory driven by
the same matched selected generator. This is the cleanest detached setting on
which later numerical simulation can act directly on selected observed states.
\end{corollary}

\begin{proof}
By definition,
\[
\rho_{\mathrm{sel}}(j_e)=\Pi_{\mathrm{sel}}(\rho(j_e)).
\]
Using the exactifier identity for the assembled hidden state and the autonomy
of the matched selected generator on the selected cut, one obtains the one-step
relation
\[
\rho_{\mathrm{sel}}(\Gamma j_e)=X(\rho_{\mathrm{sel}}(j_e)).
\]
Iterating this identity gives the stated \(n\)-step law. Thus the selected
observed trajectory is already the exact discrete trajectory generated by the
same ambient selected dynamics.
\end{proof}

\begin{corollary}[Detached law terms already have concrete coordinate expressions]
\label{thm:detached-law-terms-already-have-concrete-coordinate-expressions}\lean{ClosureCurrent.CurrentStateAssembly.coordinateFormula, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentCoordinateFormula, ClosureCurrent.CurrentStateAssembly.observedFormula, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentObservedFormula}
Once the detached current-state assembly datum is fixed, the principal law
terms are already concrete.

The reduced hidden current is exactly
\[
\rho_3(j_e)
=
\bigl(
\Phi_{\lambda_0}(j_e),
\Phi_{\lambda_1}(j_e),
\Phi_{\lambda_2}(j_e)
\bigr),
\]
where each coordinate is the explicit leg-flux sum
\[
\Phi_{\lambda_i}(j_e)
:=
\sum_{k=0}^{3}\chi\!\bigl(j_e(\lambda_i,\lambda_k)\bigr).
\]
The selected observed state is exactly
\[
\rho_{\mathrm{sel}}(j_e)
=
\Pi_{\mathrm{sel}}
\bigl(
\Phi_{\lambda_0}(j_e),
\Phi_{\lambda_1}(j_e),
\Phi_{\lambda_2}(j_e),
\Phi_{\lambda_3}(j_e)
\bigr).
\]
So the remaining abstraction is no longer in the law terms themselves, but only
in the still-detached choice of carrier observable, framed local event, and
matched selected generator.
\end{corollary}

\begin{proof}
These identities are exactly the defining formulas of the detached
current-state assembly. Once the signed observable, four-leg frame, and assembled
hidden state are fixed, the reduced hidden coordinates are the three displayed
leg-flux sums, while the selected observed state is obtained by projecting the
assembled four-state to the selected cut. Nothing further is being inferred
here: the principal law terms are already explicit by construction.
\end{proof}

\begin{corollary}[Selected observed trajectory is read directly from reduced hidden coordinates]
\label{thm:selected-observed-trajectory-is-read-directly-from-reduced-hidden-coordinates}\lean{ClosureCurrent.CurrentStateAssembly.observedFromCoordinates, ClosureCurrent.CurrentStateAssembly.observedCoordinateTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentObservedFromCoordinates, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.currentObservedCoordinateTrajectory}
Along any realized detached current trajectory, the selected observed state is
already determined by the reduced hidden coordinates:
\[
\rho_{\mathrm{sel}}(j_e)
=
\Pi_{\mathrm{sel}}(\iota(\rho_3(j_e))),
\]
and therefore the entire observed discrete trajectory is read directly from the
reduced hidden trajectory by
\[
\rho_{\mathrm{sel}}(\Gamma^{[n]} j_e)
=
\Pi_{\mathrm{sel}}
\Bigl(
\iota\bigl(T_3^{[n]}(\rho_3(j_e))\bigr)
\Bigr).
\]
So within the detached formulation, once the assembly datum is fixed, the selected
observed evolution is not extra structure on top of the reduced hidden system;
it is already its exact observation along realized trajectories.
\end{corollary}

\begin{proof}
On realized current states, the assembled four-state is balanced. Hence it is
recovered uniquely from its first three coordinates by the balanced
reconstruction map \(\iota\). Applying the selected projection therefore gives
\[
\rho_{\mathrm{sel}}(j_e)=\Pi_{\mathrm{sel}}(\iota(\rho_3(j_e))).
\]
The finite-step formula follows by substituting the reduced hidden trajectory
law
\[
\rho_3(\Gamma^{[n]}j_e)=T_3^{[n]}(\rho_3(j_e))
\]
into the same observation identity. Thus the observed trajectory is obtained by
reading the reduced hidden trajectory through one fixed reconstruction and one
fixed selected projection.
\end{proof}

\begin{definition}[Detached reduced observed system]
\label{def:detached-reduced-observed-system}\lean{ClosureCurrent.ReducedObservedSystem, ClosureCurrent.AnchoredCurrentObject.reducedObservedSystem}
The \emph{detached reduced observed system} is the concrete discrete system on
the reduced hidden carrier \(\operatorname{BalancedCoordinates}\) consisting of
two maps:
\[
T_3 : \operatorname{BalancedCoordinates}\to\operatorname{BalancedCoordinates},
\qquad
O_{\mathrm{sel}} : \operatorname{BalancedCoordinates}\to\operatorname{State},
\]
where
\[
T_3(\rho):=\Pi_3\!\bigl(X(\iota(\rho))\bigr),
\qquad
O_{\mathrm{sel}}(\rho):=\Pi_{\mathrm{sel}}(\iota(\rho)).
\]
Thus the detached formulation now carries one hidden update rule together with
one canonical selected observation map from the same reduced hidden carrier.
\end{definition}

\begin{corollary}[Detached current trajectories factor through the reduced observed system]
\label{thm:detached-current-trajectories-factor-through-the-reduced-observed-system}\lean{ClosureCurrent.CurrentStateAssembly.systemHiddenTrajectory, ClosureCurrent.CurrentStateAssembly.systemObservedTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.reducedObservedSystem, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.systemHiddenTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.systemObservedTrajectory}
Once the detached assembly datum is fixed, the hidden and observed trajectories
of the current are exactly trajectories of one canonical reduced observed
system:
\[
\rho_3(\Gamma^{[n]} j_e)=T_3^{[n]}(\rho_3(j_e)),
\qquad
\rho_{\mathrm{sel}}(\Gamma^{[n]} j_e)=
O_{\mathrm{sel}}\!\bigl(T_3^{[n]}(\rho_3(j_e))\bigr).
\]
Thus within the detached formulation, the current no longer carries separate
hidden and observed dynamics. It factors through one concrete reduced
dynamical system together with one canonical observation map.
\end{corollary}

\begin{proof}
The reduced hidden current already evolves autonomously on the balanced
three-coordinate carrier, and the selected observed state is read from that
same hidden trajectory by the canonical observation map. So there is one
single reduced dynamical system whose hidden trajectory is the reduced current
itself and whose observed trajectory is the visible selected-cut observation of
that same hidden evolution.
\end{proof}

\begin{corollary}[Reduced hidden coordinates are already the autonomous detached state variable]
\label{thm:reduced-hidden-coordinates-are-already-the-autonomous-detached-state-variable}\lean{ClosureCurrent.CurrentStateAssembly.sameCoordinates_sameHiddenTrajectory, ClosureCurrent.CurrentStateAssembly.sameCoordinates_sameObservedTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.sameCoordinates_sameHiddenTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.sameCoordinates_sameObservedTrajectory}
If two detached hidden currents have the same initial reduced hidden
coordinates,
\[
\rho_3(j_e)=\rho_3(j'_e),
\]
then for every discrete step \(n\) they have the same hidden and observed
states:
\[
\rho_3(\Gamma^{[n]} j_e)=\rho_3(\Gamma^{[n]} j'_e),
\qquad
\rho_{\mathrm{sel}}(\Gamma^{[n]} j_e)=
\rho_{\mathrm{sel}}(\Gamma^{[n]} j'_e).
\]
Thus within the detached formulation, once the assembly datum is fixed, the reduced
hidden coordinates are not merely one convenient compression of the current.
They already form an autonomous state variable for both the hidden and the
selected observed discrete dynamics.
\end{corollary}

\begin{proof}
If two currents have the same initial reduced coordinates, then applying the
same iterate of the same reduced update map \(T_3\) yields the same reduced
hidden state at every step:
\[
T_3^{[n]}(\rho_3(j_e))=T_3^{[n]}(\rho_3(j'_e)).
\]
By the factorization through the reduced observed system, this is exactly the
hidden statement. Applying the same canonical observation map
\(O_{\mathrm{sel}}\) to equal hidden states gives the observed statement. So
both the hidden and selected observed dynamics depend only on the reduced
initial coordinates.
\end{proof}

\begin{corollary}[Explicit detached assemblies matter dynamically only through the reduced initial state]
\label{thm:explicit-detached-assemblies-matter-dynamically-only-through-the-reduced-initial-state}\lean{ClosureCurrent.CurrentStateAssembly.sameCoordinates_acrossAssemblies_sameHiddenTrajectory, ClosureCurrent.CurrentStateAssembly.sameCoordinates_acrossAssemblies_sameObservedTrajectory}
Fix one anchored detached current object and consider two explicit detached
assemblies of it. If they assign the same reduced hidden coordinates to two
initial currents,
\[
\rho_3^{(1)}(j_e)=\rho_3^{(2)}(j'_e),
\]
then for every discrete step \(n\) they induce the same hidden and observed
states:
\[
\rho_3^{(1)}(\Gamma^{[n]} j_e)=\rho_3^{(2)}(\Gamma^{[n]} j'_e),
\qquad
\rho_{\mathrm{sel}}^{(1)}(\Gamma^{[n]} j_e)=
\rho_{\mathrm{sel}}^{(2)}(\Gamma^{[n]} j'_e).
\]
Thus within the detached formulation, the observable/frame assembly data do not contribute
additional dynamical memory beyond the reduced hidden initial state. Their
only surviving dynamical role is to determine that initial reduced state.
\end{corollary}

\begin{proof}
Both assemblies factor through the same canonical reduced observed system of
the anchored detached current object. Therefore equal initial reduced hidden
coordinates force the same iterated hidden coordinates by the same iterate of
the same reduced hidden update map, and they force the same observed states by
the same canonical observation map on that same reduced system. Hence the
assembly data carry no further dynamical memory once the reduced initial state
has been fixed.
\end{proof}

\begin{definition}[Reduced detached hidden-state assembly]
\label{def:reduced-detached-hidden-state-assembly}\lean{ClosureCurrent.ReducedCurrentAssembly, ClosureCurrent.CurrentStateAssembly.toReducedCurrentAssembly}
A \emph{reduced detached hidden-state assembly} keeps only the data that still
matter dynamically after the previous reductions:
\[
\rho_3 :
\text{pair current}\to \operatorname{BalancedCoordinates},
\qquad
\rho_3(\Gamma j_e)=T_3(\rho_3(j_e)).
\]
So it forgets the full signed observable and four-leg frame realization and
remembers only the reduced hidden coordinates together with their exact
transport law under the microscopic exactifier.
\end{definition}

\begin{corollary}[The reduced detached hidden-state assembly already carries the detached dynamics]
\label{thm:the-reduced-detached-hidden-state-assembly-already-carries-the-detached-dynamics}\lean{ClosureCurrent.ReducedCurrentAssembly.coordinateTrajectory, ClosureCurrent.ReducedCurrentAssembly.systemHiddenTrajectory, ClosureCurrent.ReducedCurrentAssembly.systemObservedTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.toReducedCurrentAssembly, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.reducedAssemblyHiddenTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.reducedAssemblyObservedTrajectory}
Every explicit detached current assembly factors through a reduced detached
hidden-state assembly, and that smaller datum already carries the exact
hidden and observed trajectory laws:
\[
\rho_3(\Gamma^{[n]} j_e)=T_3^{[n]}(\rho_3(j_e)),
\qquad
\rho_{\mathrm{sel}}(\Gamma^{[n]} j_e)=
O_{\mathrm{sel}}\!\bigl(T_3^{[n]}(\rho_3(j_e))\bigr).
\]
So from this point onward, the full observable/frame assembly is no longer needed
to express the detached dynamics themselves. It is only one upstream route for
producing the reduced hidden-state realization.
\end{corollary}

\begin{proof}
Every explicit current assembly determines a reduced hidden-state assembly.
Once one passes to that reduced assembly, the exact reduced hidden trajectory
is already closed, and both the hidden and observed current trajectories are
read as trajectories of the canonical reduced observed system. So the larger
observable/frame assembly is unnecessary for the detached dynamics themselves; it
serves only as one route to the reduced hidden-state realization.
\end{proof}

\begin{definition}[Reduced anchored detached current object]
\label{def:reduced-anchored-detached-current-object}\lean{ClosureCurrent.ReducedAnchoredCurrentObject, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.toReducedAnchoredCurrentObject}
A \emph{reduced anchored detached current object} consists of one anchored
detached current bridge together with one reduced detached hidden-state
assembly on that same bridge. So it keeps exactly the anchored microscopic
current/exactifier datum plus the reduced hidden-state realization
\[
\rho_3 : \text{pair current}\to \operatorname{BalancedCoordinates}
\]
and its exact transport law, while discarding the larger explicit
observable/frame realization datum.
\end{definition}

\begin{corollary}[The reduced anchored detached current object already carries the canonical reduced observed system]
\label{thm:the-reduced-anchored-detached-current-object-already-carries-the-canonical-reduced-observed-system}\lean{ClosureCurrent.ReducedAnchoredCurrentObject.reducedObservedSystem, ClosureCurrent.ReducedAnchoredCurrentObject.currentCoordinateIterate, ClosureCurrent.ReducedAnchoredCurrentObject.currentObservedState, ClosureCurrent.ReducedAnchoredCurrentObject.currentCoordinateTrajectory, ClosureCurrent.ReducedAnchoredCurrentObject.systemHiddenTrajectory, ClosureCurrent.ReducedAnchoredCurrentObject.systemObservedTrajectory, ClosureCurrent.AssembledUnifiedAnchoredCurrentObject.toReducedAnchoredCurrentObject}
Every explicit assembled detached current object factors through a reduced
anchored detached current object, and that smaller object already carries the
canonical reduced observed system together with the exact hidden and observed
trajectory laws:
\[
\rho_3(\Gamma^{[n]} j_e)=T_3^{[n]}(\rho_3(j_e)),
\qquad
\rho_{\mathrm{sel}}(\Gamma^{[n]} j_e)=
O_{\mathrm{sel}}\!\bigl(T_3^{[n]}(\rho_3(j_e))\bigr).
\]
So the detached discrete dynamics now live on one anchored current bridge plus
one reduced hidden-state realization; the larger explicit assembled state-field
datum is no longer needed to state the dynamics themselves.
\end{corollary}

\begin{proof}
Every explicit assembled detached current object factors through a reduced
anchored current object. On that smaller object, the canonical reduced
observed system, the iterated reduced hidden transport, and the selected
observed projection are already determined, and the corresponding finite-step
hidden and observed trajectory laws follow immediately. Thus the detached
discrete dynamics are already carried by this reduced anchored object.
\end{proof}

\begin{corollary}[At the reduced hidden-state level, the initial reduced coordinate is the full detached state]
\label{thm:at-the-reduced-hidden-state-level-the-initial-reduced-coordinate-is-the-full-detached-state}\lean{ClosureCurrent.ReducedCurrentAssembly.sameCoordinates_sameHiddenTrajectory, ClosureCurrent.ReducedCurrentAssembly.sameCoordinates_sameObservedTrajectory, ClosureCurrent.ReducedCurrentAssembly.sameCoordinates_acrossAssemblies_sameHiddenTrajectory, ClosureCurrent.ReducedCurrentAssembly.sameCoordinates_acrossAssemblies_sameObservedTrajectory}
Fix one anchored detached current bridge and one reduced detached hidden-state
assembly on it. If two initial pair currents have the same reduced hidden
coordinate \(\rho_3\), then they have the same full future hidden trajectory
and the same full future selected observed trajectory. More generally, if two
reduced hidden-state assemblies on the same anchored bridge agree on the
initial reduced coordinate, then they induce the same hidden and observed
future on those initial currents.

So on the reduced detached setting, the reduced initial hidden coordinate
\(\rho_3(j_e)\) is already the entire dynamical state variable.
\end{corollary}

\begin{proof}
Both the one-assembly and the cross-assembly statements are proved in the same
way: factor the detached evolution through the canonical reduced observed
system of the anchored bridge and use equality of the initial reduced hidden
coordinates. Once the initial reduced coordinate agrees, both the hidden and
observed futures agree. Thus the reduced coordinate alone carries all detached
dynamical memory on this surface.
\end{proof}

\begin{corollary}[Current-free state-space form of the detached dynamics]
\label{thm:current-free-state-space-form-of-the-detached-dynamics}\lean{ClosureCurrent.AnchoredCurrentObject.hiddenTrajectoryFrom, ClosureCurrent.AnchoredCurrentObject.observedTrajectoryFrom, ClosureCurrent.ReducedCurrentAssembly.hiddenTrajectory_from_initialCoordinate, ClosureCurrent.ReducedCurrentAssembly.observedTrajectory_from_initialCoordinate, ClosureCurrent.ReducedAnchoredCurrentObject.hiddenTrajectoryFrom, ClosureCurrent.ReducedAnchoredCurrentObject.observedTrajectoryFrom, ClosureCurrent.ReducedAnchoredCurrentObject.hiddenTrajectory_from_initialCoordinate, ClosureCurrent.ReducedAnchoredCurrentObject.observedTrajectory_from_initialCoordinate}
Fix one anchored detached current bridge. Then every reduced hidden coordinate
\(x \in \operatorname{BalancedCoordinates}\) determines a current-free hidden
orbit
\[
n \longmapsto H_x(n)
\]
and a current-free selected observed orbit
\[
n \longmapsto O_x(n),
\]
obtained by iterating the canonical reduced hidden update map and then the
canonical selected observed projection. For every detached current realization,
the exact hidden and observed trajectories are precisely
\[
\rho_3(\Gamma^{[n]} j_e)=H_{\rho_3(j_e)}(n),
\qquad
\rho_{\mathrm{sel}}(\Gamma^{[n]} j_e)=O_{\rho_3(j_e)}(n).
\]
So after passage to the reduced hidden coordinate, the detached law is already
a genuine discrete state-space system; the hidden current appears only through
its initial reduced state.
\end{corollary}

\begin{proof}
The current-free hidden and observed state-space orbits are obtained by
iterating the reduced hidden update map and then applying the canonical
selected observed projection. Every detached current trajectory factors exactly
through those current-free orbits by taking its initial reduced hidden
coordinate. On the smaller reduced anchored current object, the same
factorization is preserved, so the detached law is already a genuine discrete
state-space system on the reduced hidden carrier.
\end{proof}

\begin{corollary}[Current-free recurrence form on the reduced hidden carrier]
\label{thm:current-free-recurrence-form-on-the-reduced-hidden-carrier}\lean{ClosureCurrent.AnchoredCurrentObject.hiddenTrajectoryFrom_step, ClosureCurrent.AnchoredCurrentObject.observedTrajectoryFrom_readout, ClosureCurrent.ReducedAnchoredCurrentObject.hiddenTrajectoryFrom_step, ClosureCurrent.ReducedAnchoredCurrentObject.observedTrajectoryFrom_readout}
On the reduced hidden carrier, the detached state-space law is already given by
one current-free recurrence and one current-free observation law:
\[
H_x(n+1)=T_3(H_x(n)),
\qquad
O_x(n)=P_{\mathrm{sel}}\!\bigl(H_x(n)\bigr),
\]
where \(H_x(0)=x\). So once the reduced initial hidden coordinate is fixed, the
entire detached future is generated by iterating the canonical reduced hidden
update map and then applying the canonical selected projection.
\end{corollary}

\begin{proof}
The anchored bridge already determines the current-free recurrence law for the
hidden trajectory together with the selected observed projection law. Passing to
the smaller reduced anchored current object preserves exactly the same
recurrence and projection. Hence once the reduced initial coordinate is fixed,
the detached future is generated entirely by repeated application of the
selected bridge dynamics and the selected projection.
\end{proof}

\begin{definition}[Reduced detached initial state]
\label{def:reduced-detached-initial-state}\lean{ClosureCurrent.ReducedInitialState, ClosureCurrent.ReducedAnchoredCurrentObject.initialStateOf}
A \emph{reduced detached initial state} consists of one reduced anchored
detached current object together with one initial reduced hidden coordinate
\[
x_0 \in \operatorname{BalancedCoordinates}.
\]
Equivalently, every detached current on a reduced anchored system determines
one such initial state by taking
\[
x_0=\rho_3(j_e).
\]
\end{definition}

\begin{corollary}[The detached law is a reduced initial-value problem]
\label{thm:the-detached-law-is-a-reduced-initial-value-problem}\lean{ClosureCurrent.ReducedInitialState.hiddenTrajectory, ClosureCurrent.ReducedInitialState.observedTrajectory, ClosureCurrent.ReducedInitialState.hiddenTrajectory_zero, ClosureCurrent.ReducedInitialState.hiddenTrajectory_step, ClosureCurrent.ReducedInitialState.observedTrajectory_readout, ClosureCurrent.ReducedAnchoredCurrentObject.hiddenTrajectory_initialStateOf, ClosureCurrent.ReducedAnchoredCurrentObject.observedTrajectory_initialStateOf}
On the reduced hidden carrier, the detached law is already an initial-value
problem:
\[
x_{n+1}=T_3(x_n),
\qquad
y_n=P_{\mathrm{sel}}(x_n),
\qquad
x_0=\rho_3(j_e).
\]
The hidden and observed detached futures are exactly the hidden and observed
orbits of that reduced initial state. So after passage to \(\rho_3\), the
microscopic detached law has the same formal status as an ordinary discrete
dynamical system with initial data.
\end{corollary}

\begin{proof}
Given a reduced anchored current object and an initial reduced coordinate
\(x_0\), one obtains hidden and observed orbits by the recurrence
\(x_{n+1}=T_3(x_n)\) and the observation law \(y_n=P_{\mathrm{sel}}(x_n)\). Choosing
\(x_0=\rho_3(j_e)\) for a detached current \(j_e\) identifies those orbits
exactly with the hidden and observed detached futures. So the detached law is
already an ordinary reduced initial-value problem.
\end{proof}

\begin{definition}[Current-free reduced system state]
\label{def:current-free-reduced-system-state}\lean{ClosureCurrent.ReducedObservedDynamicsState, ClosureCurrent.ReducedAnchoredCurrentObject.dynamicsStateOf}
A \emph{current-free reduced system state} consists only of the canonical
reduced observed system on the selected cut together with one initial reduced
hidden coordinate \(x_0\). Equivalently, every detached current on a reduced
anchored system determines one such smaller state by forgetting everything
except the canonical reduced observed system and the initial reduced coordinate
\(\rho_3(j_e)\).
\end{definition}

\begin{corollary}[The detached law already factors through the canonical reduced observed system plus initial coordinate]
\label{thm:the-detached-law-already-factors-through-the-canonical-reduced-observed-system-plus-initial-coordinate}\lean{ClosureCurrent.ReducedObservedDynamics.hiddenTrajectoryFrom_step, ClosureCurrent.ReducedObservedDynamics.observedTrajectoryFrom_readout, ClosureCurrent.ReducedObservedDynamicsState.hiddenTrajectory, ClosureCurrent.ReducedObservedDynamicsState.observedTrajectory, ClosureCurrent.ReducedObservedDynamicsState.hiddenTrajectory_zero, ClosureCurrent.ReducedObservedDynamicsState.hiddenTrajectory_step, ClosureCurrent.ReducedObservedDynamicsState.observedTrajectory_readout, ClosureCurrent.ReducedAnchoredCurrentObject.dynamicsStateOf, ClosureCurrent.ReducedAnchoredCurrentObject.hiddenTrajectory_dynamicsStateOf, ClosureCurrent.ReducedAnchoredCurrentObject.observedTrajectory_dynamicsStateOf}
Even the reduced anchored detached current object is more than is needed to
state the detached evolution. The law already factors through:
\[
\text{canonical reduced observed system}
\;+\;
\text{initial reduced coordinate }x_0.
\]
On that smaller datum the hidden and observed futures are still exactly the
hidden and observed detached futures. So the detached formulation has now collapsed to
its canonical current-free dynamics together with initial data.
\end{corollary}

\begin{proof}
The canonical reduced observed system together with an initial reduced
coordinate already determines hidden and observed orbits by recurrence and
observation alone. For a detached current on a reduced anchored system, taking the
initial coordinate to be \(\rho_3(j_e)\) produces exactly the same hidden and
observed futures. Thus the detached law factors through this smaller
current-free initial-data datum.
\end{proof}

\begin{definition}[Selected-bridge reduced state]
\label{def:selected-bridge-reduced-state}\lean{ClosureCurrent.SelectedReducedState, ClosureCurrent.ReducedAnchoredCurrentObject.selectedReducedStateOf}
A \emph{selected-bridge reduced state} consists only of:
\[
\text{selected bridge generator}
\;+\;
\text{selected projection}
\;+\;
\text{initial reduced coordinate }x_0.
\]
Equivalently, every detached current on a reduced anchored system determines
one such state by retaining only the selected bridge generator, the selected
projection, and the initial reduced hidden coordinate \(\rho_3(j_e)\).
\end{definition}

\begin{corollary}[Once \texorpdfstring{$\rho_3(j_e)$}{rho3(je)} is fixed, the detached future is generated by the selected bridge]
\label{thm:once-rho3-is-fixed-the-detached-future-is-generated-by-the-selected-bridge}\lean{ClosureCurrent.SelectedReducedState.hiddenTrajectory_zero, ClosureCurrent.SelectedReducedState.hiddenTrajectory_step, ClosureCurrent.SelectedReducedState.observedTrajectory_readout, ClosureCurrent.ReducedAnchoredCurrentObject.selectedReducedStateOf, ClosureCurrent.ReducedAnchoredCurrentObject.hiddenTrajectory_selectedReducedStateOf, ClosureCurrent.ReducedAnchoredCurrentObject.observedTrajectory_selectedReducedStateOf}
The pure reduced-dynamics datum is still not the smallest public
formulation. For detached currents on a reduced anchored system, the hidden and
observed futures are already exactly the orbits of the selected-bridge reduced
state determined by that current. So once the reduced initial coordinate
\(\rho_3(j_e)\) is fixed, the detached future is generated canonically by the
selected bridge generator and the selected projection.
\end{corollary}

\begin{proof}
Once the selected bridge generator, the selected projection, and the initial
reduced coordinate are fixed, both hidden and observed orbits are generated
canonically. For a detached current on a reduced anchored system, those
bridge-driven orbits agree exactly with the hidden and observed detached
futures. So no further datum is needed beyond the selected bridge and the
initial reduced coordinate.
\end{proof}

\begin{definition}[Current-coordinate assembly]
\label{def:current-coordinate-assembly}\lean{ClosureCurrent.CurrentCoordinateAssembly, ClosureCurrent.CoordinateAnchoredCurrentObject}
A \emph{current-coordinate assembly} consists only of:
\begin{enumerate}
\item a signed readout \(\chi_e\) of pair-current values;
\item a genuine four-leg frame
      \((\lambda_0,\lambda_1,\lambda_2,\lambda_3)\);
\item the explicit reduced-coordinate law
\[
\rho_3(j_e)
=
\bigl(
\Phi_{\lambda_0}(j_e),
\Phi_{\lambda_1}(j_e),
\Phi_{\lambda_2}(j_e)
\bigr);
\]
\item the reduced transport identity
\[
\rho_3(\Gamma j_e)=\Pi_3(X(\iota(\rho_3(j_e)))).
\]
\end{enumerate}
So this package retains exactly the explicit data that determine the reduced
hidden coordinate \(\rho_3\), and nothing from the larger four-state visible
realization.
\end{definition}

\begin{corollary}[The detached future already depends only on the coordinate assembly and the selected bridge]
\label{thm:the-detached-future-already-depends-only-on-the-coordinate-assembly-and-the-selected-bridge}\lean{ClosureCurrent.CurrentCoordinateAssembly, ClosureCurrent.CoordinateAnchoredCurrentObject.selectedReducedStateOf, ClosureCurrent.CoordinateAnchoredCurrentObject.hiddenTrajectory_selectedReducedStateOf, ClosureCurrent.CoordinateAnchoredCurrentObject.observedTrajectory_selectedReducedStateOf}
The full explicit current-state assembly is no longer needed to determine the
detached future. Once the signed readout, the four-leg frame, and the reduced
transport law for \(\rho_3\) are fixed, the detached hidden and observed
futures are already exactly the hidden and observed orbits generated by the
selected bridge from the initial reduced coordinate.
\end{corollary}

\begin{proof}
Once the signed readout, the four-leg frame, and the reduced transport law are
fixed, every detached current determines its selected-bridge reduced state
through the initial reduced coordinate. The resulting hidden and observed
futures are exactly the bridge-generated orbits of that state. So the only
remaining live detached datum is the concrete reduced-coordinate assembly that
determines \(\rho_3\).
\end{proof}

\begin{definition}[Local-event state bridge]
\label{def:local-event-state-bridge}\lean{ClosureCurrent.LocalEventStateBridge}
A \emph{local-event state bridge} consists of a detached local-event current
object together with:
\begin{enumerate}
\item a signed readout \(\chi_e\) of pair-current values;
\item a genuine four-leg frame
      \((\lambda_0,\lambda_1,\lambda_2,\lambda_3)\);
\item the explicit four-state transport identity
\[
\rho_4(\Gamma j_e)=X(\rho_4(j_e)).
\]
\end{enumerate}
So this is stronger than the coordinate bridge: it fixes the same microscopic
readout data, but requires the exactifier/generator intertwining law already on
the full assembled four-state.
\end{definition}

\begin{definition}[Local-event coordinate bridge]
\label{def:local-event-coordinate-bridge}\lean{ClosureCurrent.LocalEventCoordinateObject}
A \emph{local-event coordinate bridge} consists of a detached local-event
current object together with only:
\begin{enumerate}
\item a signed readout \(\chi_e\) of pair-current values;
\item a genuine four-leg frame
      \((\lambda_0,\lambda_1,\lambda_2,\lambda_3)\);
\item the reduced transport identity for the resulting concrete coordinate
      \(\rho_3\).
\end{enumerate}
So this is the smallest present upstream microscopic package that already
recovers the explicit coordinate assembly and hence the selected-bridge
reduced state.
\end{definition}

\begin{theorem}[The coordinate bridge is derived from the local-event state bridge]
\label{thm:the-coordinate-bridge-is-derived-from-the-local-event-state-bridge}\lean{ClosureCurrent.LocalEventStateBridge.coordinateTransport, ClosureCurrent.LocalEventStateBridge.toLocalEventCoordinateObject, ClosureCurrent.LocalEventStateBridge.surface}
On the stronger local-event state bridge, the reduced transport identity for
\(\rho_3\) is no longer postulated. It is forced from the four-state
intertwining law. Consequently the local-event coordinate bridge, and the same
reduced selected-bridge future it determines, are recovered as a corollary.
\end{theorem}

\begin{proof}
The four-state intertwining law already implies the reduced transport identity
for \(\rho_3\): reconstruct the balanced four-state from the reduced
coordinate, transport it by the selected generator, and project back. Hence
the coordinate bridge is recovered from the stronger state bridge, and with it
the same reduced hidden and observed initial-value dynamics as before.
\end{proof}

\begin{corollary}[The local-event current object needs only the coordinate bridge to generate the detached future]
\label{cor:the-local-event-current-object-needs-only-the-coordinate-bridge-to-generate-the-detached-future}\lean{ClosureCurrent.LocalEventCoordinateObject, ClosureCurrent.LocalEventCoordinateObject.toCoordinateAnchoredCurrentObject, ClosureCurrent.LocalEventCoordinateObject.selectedReducedStateOf, ClosureCurrent.LocalEventCoordinateObject.hiddenTrajectory_selectedReducedStateOf, ClosureCurrent.LocalEventCoordinateObject.observedTrajectory_selectedReducedStateOf}
Once the detached local-event current object is fixed, no further visible-state
or observer-realization package is needed to generate the detached future. The
only remaining upstream microscopic datum is the coordinate bridge for
\(\rho_3\); with that in hand, the hidden and observed futures factor exactly
through the selected-bridge reduced state determined by the current.
\end{corollary}

\begin{proof}
Once the detached local-event current object is fixed, the coordinate bridge
determines the corresponding selected-bridge reduced state from the initial
reduced coordinate. The hidden and observed futures then factor exactly
through that selected-bridge state. So the only remaining upstream microscopic
datum needed to generate the detached future is the coordinate bridge for
\(\rho_3\).
\end{proof}

\begin{corollary}[The sharpened detached microscopic law is already a pure reduced initial-value system]
\label{cor:the-sharpened-detached-microscopic-law-is-already-a-pure-reduced-initial-value-system}\lean{ClosureCurrent.LocalEventStateBridge.reducedDynamics, ClosureCurrent.LocalEventStateBridge.initialStateOf, ClosureCurrent.LocalEventStateBridge.hiddenTrajectory_initialStateOf, ClosureCurrent.LocalEventStateBridge.observedTrajectory_initialStateOf, ClosureCurrent.LocalEventStateBridge.surface}
If the local-event state bridge is taken as part of the assumed detached
microscopic law, then no further microscopic datum remains inside that lane.
The law
already determines one pure reduced observed dynamics and, for each detached
current \(j_e\), one corresponding initial reduced coordinate. The hidden and
observed futures are exactly the hidden and observed orbits of that pure
initial-value system.
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:the-coordinate-bridge-is-derived-from-the-local-event-state-bridge},
the local-event state bridge already yields the coordinate bridge. It therefore
also yields the pure reduced observed dynamics and its initial-value problem.
For each detached current, the hidden and observed futures are exactly the
hidden and observed orbits of that reduced initial-value system.
So once the local-event state bridge is included in the assumed detached
microscopic law, the detached lane is already a fully defined pure reduced
initial-value system.
\end{proof}

\begin{definition}[Pure four-state detached initial-value law]
\label{def:pure-four-state-detached-initial-value-law}\lean{ClosureCurrent.StateDynamics, ClosureCurrent.StateDynamicsState, ClosureCurrent.LocalEventStateBridge.stateDynamics, ClosureCurrent.LocalEventStateBridge.stateInitialStateOf}
On the stronger local-event state bridge, there is also a pure
\emph{four-state} detached initial-value law. It keeps only:
\[
\text{one four-state update map }X : \mathrm{State}\to\mathrm{State},
\qquad
\text{one initial four-state } \rho_4(j_e).
\]
Its trajectory is the explicit recurrence
\[
x_{n+1}=X(x_n),
\qquad
x_0=\rho_4(j_e).
\]
So the detached microscopic law is no longer only a reduced
\(\rho_3\)-system. It already carries a current-free four-state dynamics.
\end{definition}

\begin{theorem}[The local-event state bridge already determines a pure four-state law]
\label{thm:the-local-event-state-bridge-already-determines-a-pure-four-state-law}\lean{ClosureCurrent.LocalEventStateBridge.stateTrajectory_initialStateOf, ClosureCurrent.LocalEventStateBridge.stateTrajectory_balanced, ClosureCurrent.LocalEventStateBridge.stateSurface}
If the local-event state bridge is taken as part of the assumed detached
microscopic law, then for each detached current \(j_e\) the explicit
four-state future is already the trajectory of one pure current-free
initial-value system
\[
x_{n+1}=X(x_n),
\qquad
x_0=\rho_4(j_e).
\]
Moreover every such four-state trajectory stays in the balanced zero-sum
sector.
\end{theorem}

\begin{proof}
The local-event state bridge already supplies the four-state transport identity
\[
\rho_4(\Gamma j_e)=X(\rho_4(j_e)).
\]
Taking \(x_0=\rho_4(j_e)\) and defining \(x_{n+1}=X(x_n)\), an induction on
\(n\) shows that
\[
x_n=\rho_4(j_e^{(n)}).
\]
Thus the explicit four-state future is the trajectory of the current-free
system \(x_{n+1}=X(x_n)\) with initial state \(x_0\). Since every realized
four-state lies in the balanced zero-sum sector and the transport identity is
compatible with the same selected dynamics, each iterate remains balanced.
\end{proof}

\begin{corollary}[The reduced \texorpdfstring{$\rho_3$}{rho3} law is the balanced quotient of the four-state law]
\label{cor:the-reduced-rho3-law-is-the-balanced-quotient-of-the-four-state-law}\lean{ClosureCurrent.LocalEventStateBridge.reducedTrajectory_projectState, ClosureCurrent.LocalEventStateBridge.observedTrajectory_stateProjection}
On the stronger local-event state bridge, the reduced hidden law is not a
second independent stage. The reduced trajectory is exactly the balanced
three-coordinate quotient of the four-state trajectory:
\[
\rho_3(j_e^{(n)})=\Pi_3(x_n).
\]
Likewise the reduced observed trajectory is exactly the selected projection of
that same four-state orbit:
\[
y_n=P_{\mathrm{sel}}(x_n).
\]
So the detached microscopic law already has one explicit four-state dynamics,
and the sharpened \(\rho_3\)-law is simply its balanced quotient.
\end{corollary}

\begin{proof}
By construction, the reduced hidden state is the first-three-coordinate
projection of the balanced four-state, so
\[
\rho_3(j_e^{(n)})=\Pi_3(x_n).
\]
The selected observed state is obtained from the same four-state orbit by the
selected projection:
\[
y_n=P_{\mathrm{sel}}(x_n).
\]
Therefore both reduced laws are read from a single four-state trajectory, and
the sharpened \(\rho_3\)-law is simply the balanced quotient of the current-free
four-state dynamics.
\end{proof}

\begin{definition}[No-stage local-event four-state law]
\label{def:no-stage-local-event-four-state-law}\lean{ClosureCurrent.FramedLocalEventObject, ClosureCurrent.LocalEventFourStateLaw}
If one does not wish to leave a further hidden microscopic interface before the
continuum limit, the detached lane can be stated directly in its smallest
no-stage form.

A \emph{framed local-event object} is a detached local-event current object
together with:
\begin{enumerate}
\item a signed readout \(\chi_e\) of pair-current values;
\item a genuine four-leg frame
      \((\lambda_0,\lambda_1,\lambda_2,\lambda_3)\).
\end{enumerate}

A \emph{local-event four-state law} is a framed local-event object together
with the explicit four-state transport identity
\[
\rho_4(\Gamma j_e)=X(\rho_4(j_e)).
\]
This is the smallest current-side package that already determines the
pure four-state law and the reduced \(\rho_3\)-law as its balanced quotient.
\end{definition}

\begin{theorem}[The no-stage detached primitive is already a four-state law]
\label{thm:the-no-stage-detached-primitive-is-already-a-four-state-law}\lean{ClosureCurrent.LocalEventFourStateLaw.toLocalEventStateBridge, ClosureCurrent.LocalEventFourStateLaw.surface}
If the detached microscopic law is promoted to the no-stage local-event
four-state law, then the stronger local-event state bridge is no longer a
separate interface layer. It is recovered immediately, and with it:
\begin{enumerate}
\item the pure four-state initial-value law
      \(x_{n+1}=X(x_n)\), \(x_0=\rho_4(j_e)\);
\item the balance of every four-state trajectory;
\item the reduced hidden law as the balanced quotient
      \(\rho_3(j_e^{(n)})=\Pi_3(x_n)\);
\item the reduced observed law as the selected projection
      \(y_n=P_{\mathrm{sel}}(x_n)\).
\end{enumerate}
So if the theory is to assume no further microscopic stage before continuum,
this is now the clean primitive form to assume.
\end{theorem}

\begin{proof}
A framed local-event object already contains the detached local-event current,
the signed readout, and the genuine four-leg frame. Adding the explicit
four-state transport identity therefore gives exactly the data of the
local-event state bridge. Once that bridge is recovered, the conclusions follow
from the previous two theorems: the four-state future is a pure initial-value
trajectory, every iterate remains balanced, and the reduced hidden and observed
laws are obtained by projecting that same four-state orbit.
\end{proof}

\begin{theorem}[The no-stage four-state law already forces a four-state continuum law]
\label{thm:the-no-stage-four-state-law-already-forces-a-four-state-continuum-law}\lean{ClosureCurrent.StateDynamics.refinementCompatibleFamily, ClosureCurrent.StateDynamics.reconstructionDatum, ClosureCurrent.StateDynamics.continuumLaw_forced, ClosureCurrent.LocalEventFourStateLaw.stateContinuumLaw_forced}
If the detached microscopic law is taken in the no-stage local-event
four-state form, then its explicit four-state update map
\[
X:\mathrm{State}\to\mathrm{State}
\]
already defines a refinement-constant continuum-bridge family:
\[
F_n = X,\qquad
\sigma_{n\to m}=\mathrm{id},\qquad
\mathcal R_n=\mathrm{id}.
\]
Hence the continuum extension is not an extra endpoint design choice. The same
map \(X\) is already the unique forced continuum law in the corresponding
continuum-bridge limit class.
\end{theorem}

\begin{proof}
Take the constant continuum-bridge family with stage law \(F_n=X\),
comparison maps \(\sigma_{n\to m}=\mathrm{id}\), and reconstruction maps
\(\mathcal R_n=\mathrm{id}\). This family is refinement-compatible by
construction, and every stage reconstructs the same law \(X\). Hence the
continuum limit class contains no further freedom: the induced continuum law is
forced to be \(X\) itself. So the detached continuum law is already fixed
before any carrier-level endpoint representative is chosen.
\end{proof}

\begin{corollary}[The reduced hidden continuum law is the balanced quotient of the forced four-state continuum law]
\label{cor:the-reduced-hidden-continuum-law-is-the-balanced-quotient-of-the-forced-four-state-continuum-law}\lean{ClosureCurrent.ReducedObservedDynamics.hiddenContinuumLaw_forced, ClosureCurrent.LocalEventFourStateLaw.reducedContinuumLaw_forced, ClosureCurrent.LocalEventFourStateLaw.reducedContinuumLaw_quotient, ClosureCurrent.LocalEventFourStateLaw.observedContinuumReadout, ClosureCurrent.LocalEventFourStateLaw.continuumSurface}
Let \(X\) be the forced four-state continuum law from
Theorem~\ref{thm:the-no-stage-four-state-law-already-forces-a-four-state-continuum-law}.
Then the reduced hidden continuum law on the balanced three-coordinate carrier
is also forced, and it is exactly the balanced quotient
\[
L_3 = \Pi_3 \circ X \circ \iota_3,
\]
where \(\iota_3(x)=x^\sharp\) is the forced balanced four-state reconstruction
of a reduced hidden state and \(\Pi_3\) projects to the first three
coordinates. The selected observed readout is likewise
\[
Y = P_{\mathrm{sel}} \circ \iota_3.
\]
So the detached continuum extension already has one forced four-state law, one
forced reduced hidden quotient law, and the visible readout is simply the
selected projection of that same balanced carrier.
\end{corollary}

\begin{proof}
The four-state continuum law is already forced to be \(X\). Passing to the
balanced hidden carrier means reconstructing a balanced four-state from a
reduced hidden coordinate, applying \(X\), and projecting back to the first
three coordinates. That is exactly the quotient law
\[
L_3=\Pi_3\circ X\circ \iota_3.
\]
The selected observed readout is obtained from the same balanced hidden carrier
by the fixed projection
\[
Y=P_{\mathrm{sel}}\circ \iota_3.
\]
Hence the reduced hidden continuum law and the observed readout are both
derived from the same forced four-state continuum law.
\end{proof}

\begin{theorem}[The no-stage four-state law already has a canonical first-order continuum representative]
\label{thm:the-no-stage-four-state-law-already-has-a-canonical-first-order-continuum-representative}\lean{ClosureCurrent.ContinuumRepresentative, ClosureCurrent.ContinuumRepresentative.surface, ClosureCurrent.LocalEventFourStateLaw.toContinuumRepresentative, ClosureCurrent.LocalEventFourStateLaw.representativeSurface}
Let \(G_{\mathrm{sel}}\) denote the matched selected generator on the explicit
four-state carrier:
\[
G_{\mathrm{sel}}:\mathrm{State}\to\mathrm{State}.
\]
Then the no-stage four-state law already forces the following continuum
representative class:
\[
X = G_{\mathrm{sel}},\qquad
L_3 = \Pi_3 \circ G_{\mathrm{sel}} \circ \iota_3,\qquad
Y = P_{\mathrm{sel}} \circ \iota_3.
\]
Here \(X\) is the forced four-state continuum law, \(L_3\) is the forced
reduced hidden continuum law, and \(Y\) is the selected observed readout.
Therefore the first canonical continuum representative of the detached law is
already a first-order four-state state law together with its balanced hidden
quotient and selected projection, not a separately designed endpoint PDE.
\end{theorem}

\begin{proof}
The no-stage law already identifies the active four-state transport with the
matched selected generator on the explicit state carrier. Therefore the forced
four-state continuum law is
\[
X=G_{\mathrm{sel}}.
\]
Passing to the balanced hidden carrier yields the quotient law
\[
L_3=\Pi_3\circ G_{\mathrm{sel}}\circ \iota_3,
\]
and the observed readout remains
\[
Y=P_{\mathrm{sel}}\circ \iota_3.
\]
So the first canonical continuum representative is nothing more and nothing
less than the selected generator together with its balanced quotient and
selected projection.
\end{proof}

\begin{theorem}[The canonical continuum representative is already additive]
\label{thm:the-canonical-continuum-representative-is-already-additive}\lean{ClosureCurrent.CoordinateMap, ClosureCurrent.CoordinateMap.ofAddMap, ClosureCurrent.OperatorRepresentative, ClosureCurrent.OperatorRepresentative.surface, ClosureCurrent.LocalEventFourStateLaw.toOperatorRepresentative, ClosureCurrent.LocalEventFourStateLaw.operatorRepresentativeSurface}
Let \(A_{\mathrm{sel}}\) denote the same canonical four-state continuum
representative, now read as an operator on the explicit four-state carrier.
Then the no-stage four-state law already forces
\[
A_{\mathrm{sel}}(x+y)=A_{\mathrm{sel}}(x)+A_{\mathrm{sel}}(y),\qquad
A_{\mathrm{sel}}(0)=0.
\]
Its balanced hidden quotient
\[
\overline A_3 = \Pi_3 \circ A_{\mathrm{sel}} \circ \iota_3
\]
is likewise additive on the reduced hidden carrier:
\[
\overline A_3(u\oplus v)=\overline A_3(u)\oplus \overline A_3(v),\qquad
\overline A_3(0)=0.
\]
So the first canonical continuum representative is already an additive
four-state operator together with an additive balanced quotient, not merely an
arbitrary endomorphism of the hidden carrier.
\end{theorem}

\begin{proof}
The selected generator acts additively on the explicit four-state carrier, so
\[
A_{\mathrm{sel}}(x+y)=A_{\mathrm{sel}}(x)+A_{\mathrm{sel}}(y),
\qquad
A_{\mathrm{sel}}(0)=0.
\]
The balanced reconstruction \(\iota_3\) and projection \(\Pi_3\) are additive
as well. Hence their composite
\[
\overline A_3=\Pi_3\circ A_{\mathrm{sel}}\circ \iota_3
\]
is additive on the reduced hidden carrier. Thus the canonical representative is
already an additive operator both before and after passage to the balanced
quotient.
\end{proof}

\begin{theorem}[The canonical continuum representative is already quadratic-form driven]
\label{thm:the-canonical-continuum-representative-is-already-quadratic-form-driven}\lean{ClosureCurrent.QuadraticRepresentative, ClosureCurrent.QuadraticRepresentative.surface, ClosureCurrent.LocalEventFourStateLaw.toQuadraticRepresentative, ClosureCurrent.LocalEventFourStateLaw.quadraticRepresentativeSurface}
The same canonical four-state continuum representative is already the operator
of the selected admissible compiler quadratic form:
\[
Q_{\mathrm{sel}} = \text{selected observed law},\qquad
A_{\mathrm{sel}} = Q_{\mathrm{sel}}^{\mathrm{op}}.
\]
So the no-stage four-state law already forces:
\begin{enumerate}
\item an admissible quadratic form \(Q_{\mathrm{sel}}\) on the explicit
      four-state carrier;
\item the forced four-state continuum law as the operator of that quadratic
      form;
\item the balanced hidden continuum law as the quotient of that same
      quadratic-form operator.
\end{enumerate}
Thus the current formal surface already reaches a genuine quadratic
representative of the detached law, while still stopping short of a full
Lagrangian or Hamiltonian continuum theory.
\end{theorem}

\begin{proof}
The selected observed law already determines an admissible quadratic form
\(Q_{\mathrm{sel}}\) on the explicit four-state carrier. By construction, the
operator associated to that form is exactly the same selected generator
\(A_{\mathrm{sel}}\). The reduced hidden operator remains its balanced quotient
\(\Pi_3\circ A_{\mathrm{sel}}\circ \iota_3\), and the observed readout is still
the selected projection from the same carrier. So the canonical continuum
representative is already quadratic-form driven.
\end{proof}

\begin{theorem}[The canonical quadratic representative is already PSD, symmetry-compatible, and minimal]
\label{thm:the-canonical-quadratic-representative-is-already-psd-symmetry-compatible-and-minimal}\lean{ClosureCurrent.MinimalQuadraticRepresentative, ClosureCurrent.MinimalQuadraticRepresentative.surface, ClosureCurrent.LocalEventFourStateLaw.toMinimalQuadraticRepresentative, ClosureCurrent.LocalEventFourStateLaw.minimalQuadraticRepresentativeSurface}
The same canonical selected quadratic representative already carries the full
compiler-side canonicality surface:
\begin{enumerate}
\item it is positive semidefinite;
\item it is equivariant under the selected finite symmetry datum;
\item it is minimal among all positive semidefinite quadratic competitors;
\item hence it is minimal in particular among the positive semidefinite
      competitors respecting that same selected symmetry.
\end{enumerate}
So before any PDE or action-principle interpretation is attempted, the
detached lane has already forced one unique minimal selected quadratic law in
the compiler sense.
\end{theorem}

\begin{proof}
No extra analytic structure is introduced here. The selected quadratic form is
already admissible on the selected cut, so it is positive semidefinite. The
selected finite symmetry datum belongs to the same compiler-side selection
package, and the selected quadratic form is compatible with that symmetry.
Finally, the same admissibility package identifies this form as minimal among
all positive semidefinite competitors, hence in particular among those
respecting the same selected symmetry. Therefore the canonical selected
quadratic representative is already PSD, symmetry-compatible, and minimal.
\end{proof}

\begin{theorem}[The canonical quadratic representative already lives on the least-motion stationary cut]
\label{thm:the-canonical-quadratic-representative-already-lives-on-the-least-motion-stationary-cut}\lean{ClosureCurrent.StationaryQuadraticRepresentativeSurface, ClosureCurrent.LocalEventFourStateLaw.stationaryQuadraticRepresentativeSurface}
For the same selected datum, the detached lane already forces:
\begin{enumerate}
\item the selected projection is both the finite least-motion minimizer and
      the realized horizon cut;
\item the selected objective gradient is stationary on that projection, so its
      projection commutator and both off-diagonal gradient blocks vanish;
\item the selected quadratic law is exact-visible on that same cut, hence
      commutes with it and has zero \(PQ\) and \(QP\) blocks there.
\end{enumerate}
Thus the canonical selected quadratic representative is already tied to one
exact least-motion stationary cut before any stronger PDE or
action-principle realization is attempted.
\end{theorem}

\begin{proof}
The minimizer side comes directly from the explicit finite selection datum: the
selected projector is the certified least-motion minimizer of the finite design
objective, and on the selected bridge that same projector is already
identified with the realized horizon cut. The stationarity clause is then not
additional structure; it is part of the same selected datum. Stationarity on
that cut forces the projection commutator and the off-diagonal gradient blocks
to vanish.

On the law side, exact visibility of the selected quadratic law on the same
cut is already part of the selected Schur bridge. The target calculus then
forces commuting with that cut, and therefore vanishing \(PQ\) and \(QP\)
blocks. So the quadratic representative is already not just minimal, but
realized on one exact least-motion stationary cut.
\end{proof}

\begin{theorem}[The canonical quadratic representative is already the exact effective law on the least-motion cut]
\label{thm:the-canonical-quadratic-representative-is-already-the-exact-effective-law-on-the-least-motion-cut}\lean{ClosureCurrent.EffectiveQuadraticRepresentativeSurface, ClosureCurrent.LocalEventFourStateLaw.effectiveQuadraticRepresentativeSurface}
Fix the canonical selected shadow propagator on the same selected bridge.
Then on the least-motion stationary cut the detached lane already forces:
\begin{enumerate}
\item the selected quadratic law agrees exactly with its Schur/Feshbach
      effective observable law;
\item the corresponding Schur correction vanishes identically;
\item the returned residual field induced by that same cut and shadow
      propagator vanishes identically.
\end{enumerate}
So at the current exact-selected surface, the canonical quadratic
representative is already its own exact effective observable law on the
selected cut.
\end{theorem}

\begin{proof}
No new analytic input is added. The previous theorem already supplies exact
visibility of the selected quadratic law on the least-motion stationary cut.
The corresponding Schur/Feshbach effective observable law therefore agrees
exactly with the selected quadratic law on that cut. Since the same exact
visibility forces vanishing \(PQ\) transport, the Schur correction itself
vanishes there, and with it the returned residual induced by the chosen shadow
propagator. Thus exact selected visibility has already collapsed the
effective-law correction layer on the canonical cut.
\end{proof}

\begin{theorem}[The exact effective selected law already is the matched selected generator]
\label{thm:the-exact-effective-selected-law-already-is-the-matched-selected-generator}\lean{ClosureCurrent.governingScalarResidual, ClosureCurrent.SelectedGoverningSurface, ClosureCurrent.LocalEventFourStateLaw.selectedGoverningSurface}
Let \(A_{\mathrm{sel}}\) denote the canonical selected quadratic law,
\(A_{\mathrm{eff},\mathrm{sel}}\) its exact effective observable law on the
least-motion stationary cut, and \(G_{\mathrm{sel}}\) the matched selected
generator. Then the detached lane already forces:
\begin{enumerate}
\item \(A_{\mathrm{sel}}=A_{\mathrm{eff},\mathrm{sel}}=G_{\mathrm{sel}}\)
      pointwise on the four-state carrier;
\item the scalar residual
      \[
      r^{\mathrm{gov}}_{\mathrm{sel}}(x)=
      \operatorname{SignedCount.ofNat}\!\bigl(\langle x,G_{\mathrm{sel}}x\rangle\bigr)
      \]
      may be read equally from the selected quadratic law, from the exact
      effective selected law, and from the matched selected generator.
\end{enumerate}
So before any stronger PDE or action-principle realization is attempted, the
current detached analytic lane already has one common selected governing
operator.
\end{theorem}

\begin{proof}
The equality
\(A_{\mathrm{sel}}=A_{\mathrm{eff},\mathrm{sel}}\)
is exactly the previously established effective-law collapse on the
least-motion cut, while
\(A_{\mathrm{sel}}=G_{\mathrm{sel}}\)
is already part of the canonical quadratic-representative surface.

The new point is only that these two equalities are now fused into one
selected governing law. The residual
\[
r^{\mathrm{gov}}_{\mathrm{sel}}(x)
=
\operatorname{SignedCount.ofNat}\!\bigl(\langle x,G_{\mathrm{sel}}x\rangle\bigr)
\]
is therefore the same scalar readout whether it is computed from the selected
quadratic law, from the exact effective selected law, or directly from the
matched selected generator. Thus the detached lane now carries one common
selected governing operator before any later field-level realization is
attempted.
\end{proof}

\begin{theorem}[The selected governing operator already carries an exact continuous effective-flow package]
\label{thm:the-selected-governing-operator-already-carries-an-exact-continuous-effective-flow-package}\lean{ClosureCurrent.SelectedGoverningFlowSurface, ClosureCurrent.LocalEventFourStateLaw.selectedGoverningFlowSurface}
On the same least-motion stationary cut, the detached lane already forces:
\begin{enumerate}
\item a constant selected projection/shadow interpolation datum;
\item the actual \(PP/PQ/QP/QQ\) block decomposition of the selected quadratic
      law on that cut;
\item vanishing \(PQ\), \(QP\), and \(QQ\) blocks there, while the \(PP\)
      block is already the matched selected generator;
\item an exact continuum-bridge-type continuous effective-flow package whose flow is
      the exact effective selected law and which agrees exactly with the same
      matched selected generator.
\end{enumerate}
So before any stronger PDE realization is attempted, the selected governing
operator is already not just an equality of operators but an exact
field/flow package on the selected cut.
\end{theorem}

\begin{proof}
The selected projection and shadow are read as a constant interpolation datum
on the fixed least-motion cut. The block-derivative datum is then taken to be
the actual \(PP/PQ/QP/QQ\) decomposition of the selected quadratic law on that
same cut. The earlier exact-selected theorems already force the off-diagonal
blocks to vanish there, while the \(PP\) block is the matched selected
generator. Finally the exact effective selected law is packaged as a
continuous effective flow in the continuum-bridge sense, and the governing-operator
theorem identifies that same flow exactly with the matched selected generator.
So the detached lane now carries a genuine exact selected field/flow package
before any later PDE or action-principle interpretation is attempted.
\end{proof}

\begin{theorem}[The selected field/flow package admits no exogenous constitutive completion]
\label{thm:the-selected-field-flow-package-admits-no-exogenous-constitutive-completion}\lean{ClosureCurrent.SelectedPromotionSurface, ClosureCurrent.LocalEventFourStateLaw.selectedPromotionSurface}
On the same least-motion stationary cut, let the apparent constitutive term be
the returned residual of the exact effective selected law, read through the
generic continuum-bridge promotion interfaces. Then the detached lane already forces:
\begin{enumerate}
\item the promoted constitutive term vanishes identically;
\item the promoted observed law is exactly the same forced selected continuum
      law;
\item the characteristic-scale promotion package closes with no extra
      constitutive datum;
\item every finite admissible promotion chain collapses to that same law, so
      the minimum-energy branch is unique at every finite stage.
\end{enumerate}
So the selected field/flow package already carries the manuscript's strongest
current no-hidden-crime constitutive statement: no exogenous constitutive
completion remains on the selected cut.
\end{theorem}

\begin{proof}
The promotion context uses the selected projection as projector, the exact
effective selected law as carried transport, the identity readout on the
four-state carrier as reconstruction, and the returned residual field as the
only apparent constitutive term.

The decisive point is that the returned residual already vanishes identically
on the exact selected cut. So the promoted constitutive term is zero, the
promoted observed law collapses back to the same forced selected continuum
law, and the generic continuum-bridge promotion interfaces then add no new branch.
Every finite admissible promotion chain selects that same law at every stage,
and the minimum-energy interpretation is therefore unique. So the detached
lane now supports the cleanest current constitutive reading available:
apparent constitutive content is only returned residual from hidden-sector
elimination, and on the exact selected cut even that residual vanishes.
\end{proof}

\begin{theorem}[The scalarized variational residual is already the residual of the exact effective law]
\label{thm:the-scalarized-variational-residual-is-already-the-residual-of-the-exact-effective-law}\lean{ClosureCurrent.effectiveScalarResidual, ClosureCurrent.LocalEventFourStateLaw.effectiveVariationalRepresentativeSurface}
Let \(A_{\mathrm{eff},\mathrm{sel}}\) denote the exact effective observable law
on the least-motion stationary cut, and define
\[
r^{\mathrm{eff}}_{\mathrm{sel}}(x)=
\operatorname{SignedCount.ofNat}\!\bigl(\langle x,A_{\mathrm{eff},\mathrm{sel}}x\rangle\bigr).
\]
Then the detached lane already forces:
\begin{enumerate}
\item \(r^{\mathrm{eff}}_{\mathrm{sel}}=r_{\mathrm{sel}}\), where
      \(r_{\mathrm{sel}}\) is the scalar residual previously read from the
      canonical quadratic representative;
\item the same residual is equally the matched selected-generator residual;
\item therefore the same regular variational triad, observer-side transport
      triad, and Hamilton--Jacobi projection bridge already belong to that
      exact effective selected law on the same cut.
\end{enumerate}
So the current scalarized variational presentation is not a second layer added
after exact effective-law recovery. It is already the scalarized residual
presentation of that exact effective law itself.
\end{theorem}

\begin{proof}
The previous theorem already identified the selected quadratic law with that
exact effective law on the same cut. So the new residual and the old residual
agree pointwise. The earlier variational theorem then supplies the same
generator-side formula together with the already-proved dynamics triad,
observer triad, and Hamilton--Jacobi projection bridge. Hence the scalarized
variational presentation is already carried by the exact effective law itself,
not by a separate postulated variational structure.
\end{proof}

\begin{theorem}[The canonical continuum representative already carries an exact scalarized variational triad]
\label{thm:the-canonical-continuum-representative-already-carries-an-exact-scalarized-variational-triad}\lean{ClosureCurrent.scalarResidual, ClosureCurrent.regularSystem, ClosureCurrent.observerTransport, ClosureCurrent.projectionDatum, ClosureCurrent.LocalEventFourStateLaw.variationalRepresentativeSurface}
Let \(A_{\mathrm{sel}}\) denote the same canonical four-state continuum
operator, and define the signed-count scalar residual
\[
r_{\mathrm{sel}}(x)=
\operatorname{SignedCount.ofNat}\!\bigl(\langle x,A_{\mathrm{sel}}x\rangle\bigr).
\]
Then the no-stage four-state law already forces:
\begin{enumerate}
\item a regular variational system whose Lagrangian, Hamiltonian, and
      characteristic residuals are all \(r_{\mathrm{sel}}\);
\item an observer-side conservative transport datum whose Eulerian,
      Lagrangian, and characteristic residuals are all the same
      \(r_{\mathrm{sel}}\);
\item a Hamilton--Jacobi projection datum whose observer-side characteristic
      residual is exactly the projected dynamics-side characteristic
      residual.
\end{enumerate}
Thus the current formal surface already reaches an exact scalarized
variational/transport triad for the forced quadratic representative, while
still stopping short of a full analytic action principle.
\end{theorem}

\begin{proof}
The signed-count scalar residual is read directly from the selected quadratic
operator by the rebuilt state pairing. From that same residual one obtains the
regular variational datum, the observer-side transport datum, and the
projection bridge. Since the selected quadratic form remains admissible and the
same residual may be read equally from the quadratic operator and from the
matched selected generator, these three constructions belong to one exact
scalarized variational/transport triad for the same continuum representative.
\end{proof}

\begin{theorem}[The detached analytic lane already collapses to one selected operator-residual law]
\label{thm:the-detached-analytic-lane-already-collapses-to-one-selected-operator-residual-law}\lean{ClosureCurrent.SelectedFieldLaw, ClosureCurrent.SelectedFieldLawSurface, ClosureCurrent.LocalEventFourStateLaw.selectedFieldLaw, ClosureCurrent.LocalEventFourStateLaw.selectedFieldLawSurface}
On the same least-motion stationary cut, let
\[
\mathcal{L}_{\mathrm{sel}}=
\bigl(P_{\mathrm{sel}},G_{\mathrm{sel}},r^{\mathrm{gov}}_{\mathrm{sel}}\bigr)
\]
denote the selected projector, the matched selected generator, and the
governing scalar residual. Then the detached analytic lane already forces:
\begin{enumerate}
\item the four-state continuum law is exactly \(G_{\mathrm{sel}}\);
\item the scalar residual read from the canonical quadratic law and the scalar
      residual read from the exact effective selected law are both exactly
      \(r^{\mathrm{gov}}_{\mathrm{sel}}\);
\item the regular variational datum, the observer-side transport datum, and
      the Hamilton--Jacobi projection datum are generic wrappers of that same
      residual \(r^{\mathrm{gov}}_{\mathrm{sel}}\);
\item the zero-constitutive promoted observed law built from
      \(\mathcal{L}_{\mathrm{sel}}\) is again exactly \(G_{\mathrm{sel}}\).
\end{enumerate}
So the current detached analytic surface has already collapsed to one
selected operator-residual law: the variational, observer, projection, and
promotion layers are presentations of that same law, not independent analytic
ingredients.
\end{theorem}

\begin{proof}
The operator part of \(\mathcal{L}_{\mathrm{sel}}\) is the matched selected
generator \(G_{\mathrm{sel}}\), and the theorem first shows that the forced
four-state continuum law is already exactly that operator on the selected cut.
The residual part is
\[
r^{\mathrm{gov}}_{\mathrm{sel}}(x)=
\operatorname{SignedCount.ofNat}\!\bigl(\langle x,G_{\mathrm{sel}}x\rangle\bigr),
\]
and the same theorem identifies both earlier scalar readouts with this one
governing residual.

From there nothing genuinely new is added. The regular variational system, the
observer-side transport datum, and the Hamilton--Jacobi projection bridge are
the generic constructions obtained by feeding \(r^{\mathrm{gov}}_{\mathrm{sel}}\)
into the rebuilt continuum-bridge interfaces. Likewise the promotion law is the
generic zero-constitutive promotion built from the selected projector
\(P_{\mathrm{sel}}\) and the same operator \(G_{\mathrm{sel}}\), so its
promoted observed law is again exactly \(G_{\mathrm{sel}}\).

Thus the detached lane has already reached the cleanest current law-shaped
analytic statement available before any stronger PDE or action-principle
realization is attempted: one selected operator-residual law and several
equivalent presentations of it.
\end{proof}

\begin{theorem}[The selected operator-residual law is uniquely forced]
\label{thm:the-selected-operator-residual-law-is-uniquely-forced}\lean{ClosureCurrent.LocalEventFourStateLaw.selectedFieldLawClass, ClosureCurrent.SelectedFieldLawForcingSurface, ClosureCurrent.LocalEventFourStateLaw.selectedFieldLawForcingSurface}
Fix the detached no-stage law on its least-motion selected cut. Consider any
selected operator-residual law
\[
\widetilde{\mathcal{L}}_{\mathrm{sel}}=
\bigl(\widetilde P_{\mathrm{sel}},\widetilde G_{\mathrm{sel}},
\widetilde r_{\mathrm{sel}}\bigr)
\]
such that:
\begin{enumerate}
\item \(\widetilde P_{\mathrm{sel}}=P_{\mathrm{sel}}\) is the same selected
      projector;
\item \(\widetilde G_{\mathrm{sel}}\) is admissible for the same forced
      four-state continuum limit class;
\item \(\widetilde r_{\mathrm{sel}}=r^{\mathrm{gov}}_{\mathrm{sel}}\) is the
      same governing scalar residual.
\end{enumerate}
Then \(\widetilde{\mathcal{L}}_{\mathrm{sel}}=\mathcal{L}_{\mathrm{sel}}\).
Equivalently, the detached analytic lane already forces one unique selected
operator-residual law before any later PDE or action-principle realization is
attempted.
\end{theorem}

\begin{proof}
Once the projector is fixed to \(P_{\mathrm{sel}}\) and the residual is fixed
to \(r^{\mathrm{gov}}_{\mathrm{sel}}\), the only remaining variable datum in a
candidate selected field law is its operator. Continuum admissibility forces
that operator to agree pointwise with the same detached continuum law already
identified above. Hence the entire law object agrees with
\(\mathcal{L}_{\mathrm{sel}}\), so the selected operator-residual law is unique
on the detached selected cut.
\end{proof}

\begin{theorem}[All current selected-cut analytic presentations collapse to one common selected equation]
\label{thm:all-current-selected-cut-analytic-presentations-collapse-to-one-common-selected-equation}\lean{ClosureCurrent.LocalEventFourStateLaw.selectedFieldEquation, ClosureCurrent.SelectedFieldEquationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedFieldEquationSurface}
Let
\[
r_{\mathrm{sel}}(x)=
\operatorname{SignedCount.ofNat}\!\bigl(\langle x,G_{\mathrm{sel}}x\rangle\bigr)
\]
be the governing scalar residual of the uniquely forced selected
operator-residual law on the least-motion cut. Then the detached lane already
forces one common selected equation
\[
r_{\mathrm{sel}}(x)=0,
\]
and all current analytic presentations on that cut are already presentations
of that same equation. Concretely:
\begin{enumerate}
\item the four-state continuum law, the canonical quadratic law, the exact
      effective selected law, and the promoted observed law all carry the same
      operator \(G_{\mathrm{sel}}\);
\item the quadratic scalar residual and the effective scalar residual are both
      exactly \(r_{\mathrm{sel}}\);
\item vanishing of \(r_{\mathrm{sel}}\) is equivalent to vanishing of the
      regular variational residuals, the observer-side Eulerian/Lagrangian/
      characteristic residuals, and the Hamilton--Jacobi projected
      characteristic residuals.
\end{enumerate}
At the current strongest surface, the detached flagship law is not
yet a PDE, but it already is one uniquely forced selected equation with many
equivalent analytic presentations.
\end{theorem}

\begin{proof}
The first part of the theorem simply collects the previously separated
operator identities: the forced continuum law, the selected quadratic law, the
exact effective selected law, and the promoted observed law all agree with the
same matched selected generator \(G_{\mathrm{sel}}\) on the least-motion cut.
The second part collects the residual identities: both scalar residual
readouts already coincide with the governing residual
\(r_{\mathrm{sel}}\).

The final point is the genuine equation collapse. Once \(r_{\mathrm{sel}}\) is
fixed, the regular variational datum, the observer-side transport datum, and
the Hamilton--Jacobi projection datum are all built from that same residual.
So the zero sets of all of those presentations are already the same zero set
as \(r_{\mathrm{sel}}(x)=0\). Thus the detached analytic lane has already
forced one common selected equation before any later PDE or action-principle
realization is attempted.
\end{proof}

\begin{theorem}[Any later PDE or action-principle flagship form must realize the same selected equation]
\label{thm:any-later-pde-or-action-principle-flagship-form-must-realize-the-same-selected-equation}\lean{ClosureCurrent.PDERealization, ClosureCurrent.ActionRealization, ClosureCurrent.SelectedEquationRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedEquationRealizationSurface}
Fix the no-stage law on its least-motion selected cut, and let
\[
r_{\mathrm{sel}}(x)=0
\]
be the uniquely forced selected equation from
Theorem~\ref{thm:all-current-selected-cut-analytic-presentations-collapse-to-one-common-selected-equation}.
Then any later flagship-form realization must be a realization of that same
equation:
\begin{enumerate}
\item if a PDE presentation is given by a residual field
      \(\mathcal{E}(x)\) with equation \(\mathcal{E}(x)=0\), and this
      equation vanishes exactly when \(r_{\mathrm{sel}}(x)=0\), then its
      solution set is exactly the selected equation set;
\item if an action-style presentation is given by an Euler--Lagrange residual
      \(\delta S(x)\) with stationary equation \(\delta S(x)=0\), and this
      stationary equation vanishes exactly when \(r_{\mathrm{sel}}(x)=0\),
      then its stationary set is exactly the same selected equation set;
\item consequently any such PDE realization and any such action realization
      have the same solution set.
\end{enumerate}
So a future PDE or action-principle flagship form would not introduce a new
law. It would only realize the already uniquely forced selected equation in a
different analytic language.
\end{theorem}

\begin{proof}
The previous theorem already fixed the current analytic lane to one common
selected equation. So a later PDE form can count as a realization only if its
own zero set is exactly that same selected zero set; likewise for an
action-style Euler--Lagrange form.

Hence the theorem does not claim existence of a final PDE or action principle.
It proves the rigidity statement that any such later flagship form, if it is
admissible as a realization, must solve exactly the same selected equation and
therefore cannot add new law-level freedom.
\end{proof}

\begin{theorem}[Canonical scalar PDE-form and action-form realizations already exist]
\label{thm:canonical-scalar-pde-form-and-action-form-realizations-already-exist}\lean{ClosureCurrent.LocalEventFourStateLaw.scalarPDERealization, ClosureCurrent.LocalEventFourStateLaw.scalarActionRealization, ClosureCurrent.SelectedEquationExistenceSurface, ClosureCurrent.LocalEventFourStateLaw.selectedEquationExistenceSurface}
Fix the no-stage law on its least-motion selected cut, with uniquely
forced selected equation
\[
r_{\mathrm{sel}}(x)=0.
\]
Then the current surface already carries canonical scalar realizations of that
equation:
\begin{enumerate}
\item a PDE-form realization with residual field
      \(\mathcal{E}_{\mathrm{sel}}(x):=r_{\mathrm{sel}}(x)\), so the equation
      \(\mathcal{E}_{\mathrm{sel}}(x)=0\) is exactly the selected equation;
\item an action-form realization with Euler--Lagrange residual
      \(\delta S_{\mathrm{sel}}(x):=r_{\mathrm{sel}}(x)\), so the stationary
      equation \(\delta S_{\mathrm{sel}}(x)=0\) is exactly the same selected
      equation.
\end{enumerate}
Consequently the current surface already has a genuine PDE-form and
action-form existence statement, even though these realizations are still only
scalar residual realizations and not yet a spatial differential PDE or a full
action functional.
\end{theorem}

\begin{proof}
No extra analytic construction is needed to get an actual realization. The
already forced selected residual \(r_{\mathrm{sel}}\) itself serves as the PDE
residual field and also as the Euler--Lagrange residual field. Hence the
solution set of the PDE-form realization and the stationary set of the
action-form realization are both exactly the same selected equation set.

So this theorem supplies genuine realization existence, but only at the scalar
residual level. It still stops short of claiming a final spatial PDE or a full
action functional.
\end{proof}

\begin{theorem}[The current PDE-form and action-form realizations are the same scalar residual field]
\label{thm:the-current-pde-form-and-action-form-realizations-are-the-same-scalar-residual-field}\lean{ClosureCurrent.SelectedScalarRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedScalarRealizationSurface}
On the current selected-cut surface, the canonical PDE-form
realization and the canonical action-form realization are pointwise the same
scalar residual field:
\[
\mathcal{E}_{\mathrm{sel}}(x)=\delta S_{\mathrm{sel}}(x)=r_{\mathrm{sel}}(x).
\]
At the present level, the phrase ``PDE realization'' means only that
the theory already supplies a genuine residual equation object whose zero set
defines the selected law. It does \emph{not} yet mean that a spatial
differential operator or full field-theoretic action has already been forced.
\end{theorem}

\begin{proof}
The proof is immediate from the canonical constructions: both the PDE-form
equation field and the action-form Euler--Lagrange field are defined to be the
same forced selected residual \(r_{\mathrm{sel}}\). So the two realization
languages do not yet diverge mathematically; they are two presentations of one
scalar residual field on the selected state space.
\end{proof}

\begin{theorem}[The current scalar realizations come from one selected quadratic density]
\label{thm:the-current-scalar-realizations-come-from-one-selected-quadratic-density}\lean{ClosureCurrent.LocalEventFourStateLaw.selectedQuadraticDensity, ClosureCurrent.SelectedScalarDensitySurface, ClosureCurrent.LocalEventFourStateLaw.selectedScalarDensitySurface}
On the current detached selected-cut surface, define the selected quadratic
density
\[
q_{\mathrm{sel}}(x):=\langle x,G_{\mathrm{sel}}x\rangle.
\]
Then
\[
\begin{aligned}
r_{\mathrm{sel}}(x)
  &=\operatorname{SignedCount.ofNat}\!\bigl(q_{\mathrm{sel}}(x)\bigr),\\
\mathcal{E}_{\mathrm{sel}}(x)
  &=\operatorname{SignedCount.ofNat}\!\bigl(q_{\mathrm{sel}}(x)\bigr),\\
\delta S_{\mathrm{sel}}(x)
  &=\operatorname{SignedCount.ofNat}\!\bigl(q_{\mathrm{sel}}(x)\bigr).
\end{aligned}
\]
So the current PDE-form and action-form realizations are not merely the same
scalar residual field. They are both the signed-count scalarization of one
concrete selected quadratic density on the selected state space.
\end{theorem}

\begin{proof}
The density is defined directly by the governing selected operator:
\[
q_{\mathrm{sel}}(x)=\langle x,G_{\mathrm{sel}}x\rangle.
\]
The forced selected residual is then exactly its signed-count scalarization,
\[
r_{\mathrm{sel}}(x)=\operatorname{SignedCount.ofNat}\!\bigl(q_{\mathrm{sel}}(x)\bigr).
\]
Since the current canonical PDE-form realization uses \(r_{\mathrm{sel}}\) as
its equation field and the current canonical action-form realization uses that
same \(r_{\mathrm{sel}}\) as its Euler--Lagrange residual, both realization
languages are pointwise the same scalarization of that one density.

This is stronger than the previous theorem, but it does not yet
force a spatial differential operator or a full action functional. It says
only that the current scalar flagship form already comes from one explicit
quadratic density on the selected state space.
\end{proof}

\begin{theorem}[The selected operator law already has a canonical no-hidden-crime realization ledger]
\label{thm:the-selected-operator-law-already-has-a-canonical-no-hidden-crime-realization-ledger}\lean{ClosureCurrent.LocalEventFourStateLaw.selectedRealizationLaw, ClosureCurrent.LocalEventFourStateLaw.selectedRealizationChain, ClosureCurrent.SelectedLedgerSurface, ClosureCurrent.LocalEventFourStateLaw.selectedLedgerSurface}
On the current detached selected cut, the uniquely forced selected operator law
already admits a canonical realization-chain presentation with no hidden
realization crime. Concretely:
\begin{enumerate}
\item the continuum residual of the canonical realization law is exactly the
      selected operator \(G_{\mathrm{sel}}x\);
\item every realization-ledger entry vanishes pointwise: projection, geometry,
      quadrature, aliasing, split, linearization, algebraic, boundary, and
      interface crime are all identically zero;
\item therefore the realized residual is exactly the continuum residual and so
      again exactly \(G_{\mathrm{sel}}x\);
\item the selected quadratic density and scalar residual are read directly from
      that exact realized residual:
\[
q_{\mathrm{sel}}(x)
  =\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle,
\qquad
r_{\mathrm{sel}}(x)
  =\operatorname{SignedCount.ofNat}\!\bigl(\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle\bigr).
\]
\end{enumerate}
So the current detached flagship surface is already exact on the host-side
realization ledger as well: the selected law is not merely postulated and then
approximately realized. It already has one canonical no-hidden-crime
realization chain.
\end{theorem}

\begin{proof}
This exact host-side surface is formalized by the canonical realization law
\lean{ClosureCurrent.LocalEventFourStateLaw.selectedRealizationLaw}, the
canonical realization chain
\lean{ClosureCurrent.LocalEventFourStateLaw.selectedRealizationChain}, the
packaged proposition \lean{ClosureCurrent.SelectedLedgerSurface}, and the
theorem \lean{ClosureCurrent.LocalEventFourStateLaw.selectedLedgerSurface}.

The construction is deliberately minimal. The realization law is chosen so
that its continuum residual is exactly the selected operator:
\[
\mathcal R_{\mathrm{cont}}(x)=G_{\mathrm{sel}}x.
\]
The realization chain then takes every realized residual representative to be
that same selected operator. Hence the only issue is whether any hidden ledger
crime remains. The theorem says no: every crime entry vanishes identically, so
the realized residual equals the continuum residual by the rebuilt
no-hidden-crime theorem.

Once that exact realized residual \(\mathcal R_{\mathrm{sel}}(x)\) is in hand,
the current density and scalar residual are read from it directly:
\[
q_{\mathrm{sel}}(x)=\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle,
\qquad
r_{\mathrm{sel}}(x)=\operatorname{SignedCount.ofNat}\!\bigl(q_{\mathrm{sel}}(x)\bigr).
\]
So the present flagship representative is now stronger than a bare residual
equation object and stronger than a bare density statement. It already comes
with an exact realization ledger on the selected state space.
\end{proof}

\begin{theorem}[The selected quadratic density is already an exact adjoint-goal ledger]
\label{thm:the-selected-quadratic-density-is-already-an-exact-adjoint-goal-ledger}\lean{ClosureCurrent.LocalEventFourStateLaw.selectedGoalCertificate, ClosureCurrent.SelectedGoalSurface, ClosureCurrent.LocalEventFourStateLaw.selectedGoalSurface}
On the same detached selected cut, the same selected quadratic density is
already the exact goal-error ledger of a canonical adjoint-goal certificate.
For each selected state \(x\), that certificate has:
\begin{enumerate}
\item exact solved state
\[
u^\ast_{\mathrm{sel}}(x)=x+G_{\mathrm{sel}}x;
\]
\item algebraic residual
\[
\mathcal A_{\mathrm{sel}}(x)=G_{\mathrm{sel}}x;
\]
\item goal error
\[
\eta_{\mathrm{sel}}(x)
  =\langle x,\mathcal A_{\mathrm{sel}}(x)\rangle
  =\langle x,G_{\mathrm{sel}}x\rangle
  =q_{\mathrm{sel}}(x);
\]
\item and therefore scalar residual
\[
r_{\mathrm{sel}}(x)
  =\operatorname{SignedCount.ofNat}\!\bigl(\eta_{\mathrm{sel}}(x)\bigr).
\]
\end{enumerate}
Because the certificate carries a singleton residual ledger, this same goal
error is already the exact weighted residual contribution of that one selected
density term.
\end{theorem}

\begin{proof}
The certificate is chosen with identity operator, computed state \(x\),
right-hand side \(x+G_{\mathrm{sel}}x\), goal vector \(x\), adjoint weight
\(x\), and a singleton residual ledger whose only term is
\(G_{\mathrm{sel}}x\). The adjoint-goal identity then gives the exact two-part
conclusion: the goal error equals the adjoint-weighted algebraic residual, and
the same goal error equals the weighted sum of the listed residual terms. In
this canonical certificate, those two identities become
\[
\eta_{\mathrm{sel}}(x)
  =\langle x,G_{\mathrm{sel}}x\rangle
  =q_{\mathrm{sel}}(x),
\]
and the weighted residual ledger has only that one contribution. The final
scalar residual statement follows by the already established density
scalarization theorem.
\end{proof}

\begin{theorem}[The selected cut already carries one canonical scalar law object]
\label{thm:the-selected-cut-already-carries-one-canonical-scalar-law-object}\lean{ClosureCurrent.SelectedScalarLawSurface, ClosureCurrent.LocalEventFourStateLaw.selectedScalarLawSurface}
On the current detached selected cut, the forced selected equation, the
canonical scalar PDE-form realization, the canonical scalar action-form
realization, the explicit selected quadratic density, the exact no-hidden-crime
realization ledger, and the exact adjoint-goal ledger are already one and the
same scalar law object. Concretely, for each selected state \(x\):
\begin{enumerate}
\item the forced selected equation is exactly
\[
r_{\mathrm{sel}}(x)=0;
\]
\item the canonical PDE-form residual, the canonical Euler--Lagrange residual,
      and the governing selected residual all coincide pointwise;
\item each is the signed-count scalarization of the same density
\[
q_{\mathrm{sel}}(x)=\langle x,G_{\mathrm{sel}}x\rangle;
\]
\item that same density is also read directly from the exact realized residual
      of the no-hidden-crime ledger and from the exact goal error of the
      canonical adjoint-goal certificate:
\[
q_{\mathrm{sel}}(x)=\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle
  =\eta_{\mathrm{sel}}(x);
\]
\item therefore every current scalar presentation has the same zero set. This
      includes the selected equation, the scalar PDE-form realization, the
      scalar action-form realization, the density scalarization, the
      realized-residual scalarization, and the goal-error scalarization.
\end{enumerate}
So before any genuinely differential PDE or full action functional appears,
the detached lane already has one canonical scalar law object.
\end{theorem}

\begin{proof}
This theorem combines the already established selected-equation boundary,
scalar PDE/action existence and equality surface, explicit selected quadratic
density, exact no-hidden-crime realization ledger, and exact adjoint-goal
ledger into one statement.

The forced selected equation, the canonical scalar PDE-form realization, and
the canonical scalar action-form realization already define the same zero set.
The density theorem adds that all three are pointwise the same signed-count
scalarization of the one explicit density
\[
q_{\mathrm{sel}}(x)=\langle x,G_{\mathrm{sel}}x\rangle.
\]
The realization-ledger theorem then identifies that same density with the exact
realized residual readout
\[
q_{\mathrm{sel}}(x)=\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle,
\]
and the adjoint-goal theorem identifies it again with the exact goal error
\[
q_{\mathrm{sel}}(x)=\eta_{\mathrm{sel}}(x).
\]
So the detached selected cut already has one canonical scalar law object
before any further differential realization is attempted.
\end{proof}

\begin{theorem}[The selected cut already carries one canonical first-order law object]
\label{thm:the-selected-cut-already-carries-one-canonical-first-order-law-object}\lean{ClosureCurrent.SelectedFirstOrderLawSurface, ClosureCurrent.LocalEventFourStateLaw.selectedFirstOrderLawSurface}
On the current detached selected cut, the uniquely forced selected
operator-residual law, the exact continuum-bridge continuous effective flow, and the
scalar flagship equation are already one and the same first-order law object.
Concretely, for every stage \(n\) and selected state \(x\):
\begin{enumerate}
\item the exact effective selected flow is already stagewise constant and
      equals the unique selected operator:
\[
\Phi_{\mathrm{sel}}^{(n)}(x)=G_{\mathrm{sel}}x;
\]
\item the governing residual is exactly the signed-count scalarization of the
      pairing of the state with that same flow value, equivalently with the
      same selected operator;
\item the selected equation, the canonical scalar PDE-form realization, and
      the canonical scalar action-form realization all have exactly the same
      zero set as the vanishing of that same flow scalarization.
\end{enumerate}
So the current detached flagship law is already first-order before any
stronger differential PDE or full action-functional realization is attempted.
\end{theorem}

\begin{proof}
This theorem combines three previously established pieces on the same selected
cut:
\begin{enumerate}
\item the uniqueness of the selected operator-residual law;
\item the canonical scalar law object already carried by that law;
\item the exact continuum-bridge-style continuous effective-flow package of the same
      selected governing operator.
\end{enumerate}

The flow theorem identifies every stage of the exact selected effective flow
with the same matched selected operator \(G_{\mathrm{sel}}\). The scalar-law
theorem then identifies the governing residual with the signed-count
scalarization of the selected quadratic density, and the new package rewrites
that density directly through the same exact flow value. Hence the selected
equation
\[
r_{\mathrm{sel}}(x)=0
\]
is already exactly the zero set of the scalar readout of the first-order
selected flow, and the current scalar PDE-form and scalar action-form
realizations are just two presentation languages for that same zero set.
\end{proof}

\begin{theorem}[The selected cut already carries one uniquely forced autonomous evolution law]
\label{thm:the-selected-cut-already-carries-one-uniquely-forced-autonomous-evolution-law}\lean{ClosureCurrent.SelectedEvolutionLawForcingSurface, ClosureCurrent.SelectedEvolutionLawSurface, ClosureCurrent.LocalEventFourStateLaw.selectedEvolutionLaw, ClosureCurrent.LocalEventFourStateLaw.selectedEvolutionLawSurface}
On the current detached selected cut, the canonical first-order law already
packages to one uniquely forced autonomous evolution law. Concretely:
\begin{enumerate}
\item there is one canonical evolution triple
\[
(\Phi_{\mathrm{sel}}^{(n)},G_{\mathrm{sel}},r_{\mathrm{sel}});
\]
\item every stage of the exact selected flow is already the same selected
      generator:
\[
\Phi_{\mathrm{sel}}^{(n)}(x)=G_{\mathrm{sel}}x;
\]
\item the evolution residual is exactly the governing selected residual and is
      the signed-count scalarization of the same generator pairing
\[
r_{\mathrm{sel}}(x)=\operatorname{sc}\!\bigl(\langle x,G_{\mathrm{sel}}x\rangle\bigr);
\]
\item the solution set of this autonomous evolution law is exactly the forced
      selected equation, hence exactly the current scalar PDE-form solution set
      and the current scalar action-form stationary set;
\item any other autonomous evolution law with generator admissible for the
      same forced four-state continuum class, the same governing residual, and
      the same stagewise autonomy already agrees with this one.
\end{enumerate}
So the detached flagship law is not only first-order; it is already a
uniquely forced autonomous evolution law on the selected cut.
\end{theorem}

\begin{proof}
The previously proved first-order theorem already shows that the selected flow
is stagewise constant and equal to the same selected operator. Reading that
fact together with the governing selected residual yields an autonomous
evolution law. The earlier continuum-forcing argument then gives uniqueness:
once the generator lies in the same forced continuum class and the residual is
the same governing selected residual, no other autonomous evolution law
remains.

Finally, because the residual of this evolution law is exactly
\(r_{\mathrm{sel}}\), its solution set is exactly the selected equation
\[
r_{\mathrm{sel}}(x)=0,
\]
and therefore exactly the same zero set already carried by the current scalar
PDE-form and scalar action-form realizations.
\end{proof}

\begin{theorem}[The selected cut already admits one canonical evolution-form realization]
\label{thm:the-selected-cut-already-admits-one-canonical-evolution-form-realization}\lean{ClosureCurrent.EvolutionRealization, ClosureCurrent.SelectedEvolutionRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedEvolutionRealization, ClosureCurrent.LocalEventFourStateLaw.selectedEvolutionRealizationSurface}
On the current detached selected cut, the uniquely forced autonomous evolution
law already admits a canonical evolution-form realization language. Concretely:
\begin{enumerate}
\item there is one canonical realized velocity field, namely the same selected
      generator \(G_{\mathrm{sel}}\);
\item the realized scalar residual is the same governing residual
      \(r_{\mathrm{sel}}\);
\item the realized solution set is exactly the forced selected equation and
      therefore exactly the same zero set already carried by the canonical
      scalar PDE-form and scalar action-form realizations;
\item any other evolution-form realization of the same detached law already
      uses the same velocity field and has the same solution set.
\end{enumerate}
So before any stronger differential flagship form appears, the detached lane
already has a canonical evolution-form realization of its autonomous law.
\end{theorem}

\begin{proof}
The autonomous evolution theorem already provides the uniquely forced law
\[
(\Phi_{\mathrm{sel}}^{(n)},G_{\mathrm{sel}},r_{\mathrm{sel}}).
\]
The present theorem simply reads that same law as a realized velocity
field \(G_{\mathrm{sel}}\) together with the same scalar residual
\(r_{\mathrm{sel}}\). Because the exact zero set is still the selected
equation, the realized solution set already coincides with the current scalar
PDE-form solution set and the current scalar action-form stationary set. So
the detached selected cut already has its canonical evolution-form flagship
language before any stronger differential realization is attempted.
\end{proof}

\begin{theorem}[The selected cut already carries one uniquely forced autonomous scalar law]
\label{thm:the-selected-cut-already-carries-one-uniquely-forced-autonomous-scalar-law}\lean{ClosureCurrent.AutonomousScalarLaw, ClosureCurrent.SelectedAutonomousScalarLawForcingSurface, ClosureCurrent.SelectedAutonomousScalarLawSurface, ClosureCurrent.LocalEventFourStateLaw.selectedAutonomousScalarLaw, ClosureCurrent.LocalEventFourStateLaw.selectedAutonomousScalarLawSurface}
On the current detached selected cut, the autonomous evolution law, the
canonical scalar law object, the exact realization ledger, and the exact
adjoint-goal ledger already collapse to one uniquely forced autonomous scalar
law. Concretely:
\begin{enumerate}
\item there is one canonical law package
\[
(\Phi_{\mathrm{sel}}^{(n)},G_{\mathrm{sel}},q_{\mathrm{sel}},r_{\mathrm{sel}});
\]
\item every stage of the exact selected flow is already the same selected
      generator:
\[
\Phi_{\mathrm{sel}}^{(n)}(x)=G_{\mathrm{sel}}x;
\]
\item the scalar density is simultaneously the selected quadratic density, the
      exact realized-residual pairing, and the exact goal error:
\[
q_{\mathrm{sel}}(x)
 =\langle x,G_{\mathrm{sel}}x\rangle
 =\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle
 =\eta_{\mathrm{sel}}(x);
\]
\item the residual is exactly the signed-count scalarization of that same
      density:
\[
r_{\mathrm{sel}}(x)=\operatorname{sc}\!\bigl(q_{\mathrm{sel}}(x)\bigr);
\]
\item the solution set of this autonomous scalar law is exactly the forced
      selected equation, hence exactly the same zero set already carried by
      the canonical scalar PDE-form realization, the canonical scalar
      action-form realization, and the autonomous evolution law;
\item any other autonomous scalar law whose generator is admissible for the
      same forced four-state continuum class already agrees with this one.
\end{enumerate}
So the detached selected cut already carries one uniquely forced autonomous
scalar law before any stronger differential PDE or full action-functional
realization is attempted.
\end{theorem}

\begin{proof}
The key structural point is that autonomy, density, and scalarization are now
built into the law object itself. So the forcing class no longer needs a
separate residual clause or a separate stage-compatibility clause. It asks
only that the generator lie in the same forced four-state continuum class.
Once that generator is forced, the stagewise flow, the density
\(q_{\mathrm{sel}}\), and the residual \(r_{\mathrm{sel}}\) are forced with
it.

The scalar-law theorem supplies the two exact density identifications
\[
q_{\mathrm{sel}}(x)
 =\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle
 =\eta_{\mathrm{sel}}(x),
\]
while the evolution theorem supplies the common zero set with the selected
equation and with the autonomous evolution law itself. So the detached lane
has already collapsed to one uniquely forced autonomous scalar law before any
stronger differential realization is attempted.
\end{proof}

\begin{theorem}[The selected cut already fixes the visible law data for any later stronger realization]
\label{thm:the-selected-cut-already-fixes-the-public-contract-for-any-later-stronger-flagship-realization}\lean{ClosureCurrent.FlagshipRealization, ClosureCurrent.SelectedFlagshipRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedFlagshipRealization, ClosureCurrent.LocalEventFourStateLaw.selectedFlagshipRealizationSurface}
On the current detached selected cut, any later stronger realization
that exposes a velocity field, a scalar density, a scalar residual, and a
solution set is already forced to agree with the autonomous scalar law on all
four of those visible data. Concretely, every such realization already has:
\begin{enumerate}
\item the same velocity field
\[
V_{\mathrm{sel}}(x)=G_{\mathrm{sel}}x;
\]
\item the same scalar density
\[
Q_{\mathrm{sel}}(x)
 =q_{\mathrm{sel}}(x)
 =\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle
 =\eta_{\mathrm{sel}}(x);
\]
\item the same scalar residual
\[
R_{\mathrm{sel}}(x)=r_{\mathrm{sel}}(x);
\]
\item the same solution set as the autonomous scalar law, hence the same
      selected equation, the same canonical scalar PDE-form solution set, the
      same canonical scalar action-form stationary set, and the same
      autonomous evolution-law solution set.
\end{enumerate}
So any later spatial differential PDE or full action-functional realization
cannot change the visible law data. It can only realize this same already-forced
autonomous scalar law in a stronger analytic language.
\end{theorem}

\begin{proof}
The only genuinely free visible datum in such a realization is its velocity
field. The theorem requires only that this velocity lie in the same forced
four-state continuum class and that the remaining visible quantities be read
directly from it: density as the state--velocity pairing, residual as the
signed-count scalarization of that density, and solution set as the zero set
of that residual on the selected cut. Once the velocity is forced to be
\(G_{\mathrm{sel}}\), the density, residual, and solution set are forced with
it.

The autonomous scalar law theorem then identifies the resulting density and
zero set with the already established selected quadratic density, exact
realized-residual ledger, exact adjoint-goal ledger, scalar PDE/action zero
sets, and autonomous evolution-law zero set. So any later stronger
realization is now constrained to present this same visible law data rather
than a different law.
\end{proof}

\begin{theorem}[The selected cut already fixes the exact realization-ledger and adjoint-goal data for any later stronger realization]
\label{thm:the-selected-cut-already-fixes-the-exact-realization-ledger-adjoint-goal-contract-for-any-later-stronger-flagship-realization}\lean{ClosureCurrent.LedgerGoalFlagshipRealization, ClosureCurrent.SelectedLedgerGoalFlagshipRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedLedgerGoalFlagshipRealization, ClosureCurrent.LocalEventFourStateLaw.selectedLedgerGoalFlagshipRealizationSurface}
On the current detached selected cut, any later stronger realization
that claims an exact no-hidden-crime realization chain and an exact
adjoint-goal certificate for that same selected law is already forced to agree
with the selected cut on those host-side ledgers themselves. Concretely, every
such realization already has:
\begin{enumerate}
\item the same continuum residual and the same terminal realized residual,
      both equal to the selected operator
\[
G_{\mathrm{sel}}x;
\]
\item the same realized density pairing
\[
\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle=q_{\mathrm{sel}}(x);
\]
\item the same exact solved state
\[
x+G_{\mathrm{sel}}x;
\]
\item the same algebraic residual
\[
G_{\mathrm{sel}}x;
\]
\item the same exact goal error
\[
\eta_{\mathrm{sel}}(x)
 =q_{\mathrm{sel}}(x)
 =\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle;
\]
\item the same solution set as the autonomous scalar law, hence the same
      selected equation and the same canonical scalar PDE/action zero sets.
\end{enumerate}
So any later stronger realization language that reaches the exact host-side
realization ledger cannot change even those realized residual and goal-error
data. It must present the same selected host ledger already carried by the
detached selected cut.
\end{theorem}

\begin{proof}
The realization interface extends the earlier visible-data theorem by
requiring:
\begin{enumerate}
\item one exact no-hidden-crime realization chain for the canonical selected
      realization law;
\item one exact adjoint-goal certificate;
\item exact identification of the continuum residual and the algebraic
      residual with the same realized velocity field;
\item exact identification of the goal error with the same realized
      density.
\end{enumerate}
Because the velocity is already forced to be \(G_{\mathrm{sel}}\), the
continuum residual is forced with it. Exact no-hidden-crime then forces the
terminal realized residual to be the same selected operator. Because the
density is already forced to be
\[
q_{\mathrm{sel}}(x)
 =\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle
 =\eta_{\mathrm{sel}}(x),
\]
the solved state, algebraic residual, and exact goal error are forced with it
as well. So any later stronger realization is constrained not only at the
visible-law level, but also at the exact host-side realization-ledger and
adjoint-goal level.
\end{proof}

\begin{theorem}[The selected cut already fixes the differential-flow data for any later stronger realization]
\label{thm:the-selected-cut-already-fixes-the-differential-flow-contract-for-any-later-stronger-flagship-realization}\lean{ClosureCurrent.DifferentialFlagshipRealization, ClosureCurrent.SelectedDifferentialFlagshipRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedDifferentialFlagshipRealization, ClosureCurrent.LocalEventFourStateLaw.selectedDifferentialFlagshipRealizationSurface}
On the current detached selected cut, any later stronger realization
that claims a continuum-bridge-style differential-flow presentation is already forced
to agree with the selected cut on the differential-flow data themselves.
Concretely, every such realization already has:
\begin{enumerate}
\item the same block operator as the selected differential package;
\item the same \(PP\) block, namely the selected generator;
\item the same vanishing \(PQ\), \(QP\), and \(QQ\) blocks;
\item the same exact effective flow
\[
\mathcal F_{\mathrm{sel}}^{(n)}(x)=G_{\mathrm{sel}}x;
\]
\item the same solution set as the autonomous scalar law, hence the same
      selected equation and the same canonical scalar PDE/action zero sets.
\end{enumerate}
So any later PDE-like realization cannot change even the current
differential-flow data. It must realize the same selected block-derivative
and effective-flow data already carried by the detached selected cut.
\end{theorem}

\begin{proof}
The realization interface extends the earlier visible-data theorem by requiring:
\begin{enumerate}
\item one concrete continuous block-derivative presentation;
\item one concrete continuous effective-flow presentation;
\item exact identification of the block operator, the \(PP\) block, and the
      effective flow with the same realized velocity field;
\item exact vanishing of the \(PQ\), \(QP\), and \(QQ\) blocks.
\end{enumerate}
Once the velocity is already forced to be \(G_{\mathrm{sel}}\), the
operator and all four blocks are forced with it, and the effective flow is
forced stagewise as the same selected generator. So any later differential
realization is constrained not only at the zero-set level, but also
at the exact selected block-derivative and effective-flow level.
\end{proof}

\begin{theorem}[The selected cut already fixes the derivative-subsampling data for any later stronger realization]
\label{thm:the-selected-cut-already-fixes-the-derivative-subsampling-contract-for-any-later-stronger-flagship-realization}\lean{ClosureCurrent.DerivativeSubsamplingFlagshipRealization, ClosureCurrent.SelectedDerivativeSubsamplingFlagshipSurface, ClosureCurrent.LocalEventFourStateLaw.selectedDerivativeSubsamplingFlagshipRealization, ClosureCurrent.LocalEventFourStateLaw.selectedDerivativeSubsamplingFlagshipSurface}
On the current detached selected cut, any later stronger realization
that claims a continuum-bridge-style classical derivative-subsampling presentation is
already forced to agree with the selected cut on that derivative data
themselves. Concretely, every such realization already has:
\begin{enumerate}
\item the same stagewise selected projection family
\[
P_{\mathrm{sel}}^{(n)}(x)=P_{\mathrm{sel}}x;
\]
\item the same derivative field
\[
\partial_{\mathrm{sel}}x=G_{\mathrm{sel}}x;
\]
\item the same stagewise observed restriction
\[
O_{\mathrm{sel}}^{(n)}(x)=P_{\mathrm{sel}}(G_{\mathrm{sel}}x);
\]
\item the same vanishing defect
\[
D_{\mathrm{sel}}^{(n)}(x)=0;
\]
\item the same solution set as the autonomous scalar law, hence the same
      selected equation and the same canonical scalar PDE/action zero sets.
\end{enumerate}
So any later PDE-like realization cannot change even the current
derivative-subsampling data. It must realize the same selected
projection/derivative/observation data already carried by the detached
selected cut.
\end{theorem}

\begin{proof}
The realization interface extends the earlier visible-data theorem by requiring:
\begin{enumerate}
\item one stagewise projection family;
\item one derivative field;
\item one observed restriction family, identified with the observed stagewise
      readout of that derivative through the selected projection;
\item one defect family, required to vanish exactly on the selected cut.
\end{enumerate}
Once the velocity is already forced to be \(G_{\mathrm{sel}}\), the
derivative is forced with it. Once the selected cut itself is fixed, the
projection family is forced to be the constant selected projection, and the
observed restriction is forced to be the selected projection of the same
selected generator. The defect then collapses identically to zero. So any
later derivative-like realization is constrained not only at the
zero-set level and not only at the block-flow level, but also at this first
classical derivative-subsampling level.
\end{proof}

\begin{theorem}[The selected cut already fixes the variational data for any later stronger realization]
\label{thm:the-selected-cut-already-fixes-the-variational-contract-for-any-later-stronger-flagship-realization}\lean{ClosureCurrent.VariationalFlagshipRealization, ClosureCurrent.SelectedVariationalFlagshipRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedVariationalFlagshipRealization, ClosureCurrent.LocalEventFourStateLaw.selectedVariationalFlagshipRealizationSurface}
On the current detached selected cut, any later stronger realization
that claims a Chapter~7-style variational / observer / Hamilton--Jacobi
presentation is already forced to agree with the selected cut on those
residual fields themselves. Concretely, every such realization already has:
\begin{enumerate}
\item the same Lagrangian residual;
\item the same Hamiltonian residual;
\item the same characteristic residual;
\item the same Eulerian residual, the same observer-side Lagrangian residual,
      and the same observer-side characteristic residual;
\item the same observer-side Hamilton--Jacobi characteristic residual;
\item the same solution set as the autonomous scalar law, hence the same
      selected equation and the same canonical scalar PDE/action zero sets.
\end{enumerate}
So any later action-like realization cannot change even the current
variational / observer / Hamilton--Jacobi data. It must realize the same
selected residual triad already carried by the detached selected cut.
\end{theorem}

\begin{proof}
The realization interface extends the earlier visible-data theorem by requiring:
\begin{enumerate}
\item one regular variational system;
\item one observer-side conservative transport datum;
\item one Hamilton--Jacobi projection bridge;
\item exact identification of every residual in those three formulations with the
      same realized residual.
\end{enumerate}
Once the residual is already forced to be \(r_{\mathrm{sel}}\), every
residual in the dynamics-side variational triad and every residual in the
observer-side transport/Hamilton--Jacobi bridge is forced with it. So any
later action-like realization is constrained not only at the common
zero-set level, but also at the exact variational / observer / Hamilton--Jacobi
residual level.
\end{proof}

\begin{theorem}[The selected cut already fixes the combined pre-PDE data for any later stronger realization]
\label{thm:the-selected-cut-already-fixes-the-exact-combined-pre-pde-contract-for-any-later-stronger-flagship-realization}\lean{ClosureCurrent.CompositeFlagshipRealization, ClosureCurrent.SelectedCompositeFlagshipRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedCompositeFlagshipRealization, ClosureCurrent.LocalEventFourStateLaw.selectedCompositeFlagshipRealizationSurface}
On the current detached selected cut, any later stronger realization
that carries the current visible-data language, the exact realization-ledger /
adjoint-goal language, the differential-flow language, the
derivative-subsampling language, and the variational / observer /
Hamilton--Jacobi language on one same selected realization is already forced
to collapse to one common pre-PDE law statement. Concretely, every such
realization already has:
\begin{enumerate}
\item one common operator
\[
\mathcal R_{\mathrm{sel}}(x)
 =\mathcal C_{\mathrm{sel}}(x)
 =\mathcal B_{\mathrm{sel}}(x)
 =\partial_{\mathrm{sel}}x
 =V_{\mathrm{sel}}(x)
 =G_{\mathrm{sel}}x;
\]
\item one common density
\[
Q_{\mathrm{sel}}(x)
 =\langle x,\mathcal R_{\mathrm{sel}}(x)\rangle
 =\eta_{\mathrm{sel}}(x)
 =q_{\mathrm{sel}}(x);
\]
\item one common scalar residual
\[
R_{\mathrm{sel}}(x)
 =L_{\mathrm{sel}}(x)
 =H_{\mathrm{sel}}(x)
 =\chi_{\mathrm{sel}}(x)
 =E_{\mathrm{sel}}(x)
 =r_{\mathrm{sel}}(x);
\]
\item one common zero set: the selected equation, the autonomous scalar-law
      solution set, the canonical scalar PDE-form solution set, the canonical
      scalar action-form stationary set, and the autonomous evolution-law
      solution set all coincide.
\end{enumerate}
So the remaining task is no longer to determine the law carried by a later
spatial differential PDE or a later full action functional. It is only to
realize this already-fixed combined contract in that stronger language.
\end{theorem}

\begin{proof}
The input is not a new primitive. It is one later stronger realization language
that carries, on one same selected realization, all of the exact contract
layers already established separately:
\begin{enumerate}
\item the visible-data theorem;
\item the exact realization-ledger / adjoint-goal theorem;
\item the continuum-bridge differential-flow theorem;
\item the continuum-bridge derivative-subsampling theorem;
\item the Chapter~7 variational / observer / Hamilton--Jacobi theorem.
\end{enumerate}
Each earlier theorem had already forced its own visible data to agree with
the selected cut. The new theorem then shows that, once all those languages
are required to live on the same selected realization, they do not carry
independent law data anymore. They collapse jointly to one operator, one
density, one scalar residual, and one zero set. So the remaining boundary
before a final spatial differential PDE or full action functional is now a
pure realization problem, not a remaining law-choice problem.
\end{proof}

\begin{theorem}[The selected cut already fixes the eventual realized form up to differential language]
\label{thm:the-selected-cut-already-fixes-the-eventual-realized-form-up-to-differential-language}\lean{ClosureCurrent.SelectedRealizedFormSurface, ClosureCurrent.LocalEventFourStateLaw.selectedRealizedFormSurface}
On the current detached selected cut, any later stronger realization
that carries the current visible, host-ledger, differential-flow,
derivative-subsampling, and variational data on one same selected
realization is already forced to present one common realized form. Concretely,
for every stage \(n\) and state \(x\), every such realization already has:
\begin{enumerate}
\item one common first-order generator
\[
V_{\mathrm{sel}}(x)
 =\mathcal B_{\mathrm{sel}}(x)
 =\partial_{\mathrm{sel}}x
 =\Phi_{\mathrm{sel}}^{(n)}(x)
 =G_{\mathrm{sel}}x;
\]
\item one exact block-diagonal differential presentation
\[
\mathcal B_{\mathrm{sel}}^{PP}(n,x)=G_{\mathrm{sel}}x,\qquad
\mathcal B_{\mathrm{sel}}^{PQ}(n,x)
 =\mathcal B_{\mathrm{sel}}^{QP}(n,x)
 =\mathcal B_{\mathrm{sel}}^{QQ}(n,x)=0;
\]
\item one defect-free selected observed restriction
\[
\rho_{\mathrm{sel}}(\partial_{\mathrm{sel}}x),\qquad
\delta_{\mathrm{sel}}^{(n)}(x)=0;
\]
\item one common quadratic density and scalar residual
\[
Q_{\mathrm{sel}}(x)
 =\langle x,G_{\mathrm{sel}}x\rangle
 =q_{\mathrm{sel}}(x),\qquad
R_{\mathrm{sel}}(x)
 =\operatorname{sc}\!\bigl(\langle x,G_{\mathrm{sel}}x\rangle\bigr)
 =r_{\mathrm{sel}}(x);
\]
\item one common zero set: the flagship solution set, the selected equation,
      the canonical scalar PDE-form solution set, the canonical scalar
      action-form stationary set, and the autonomous evolution-law solution set
      all coincide.
\end{enumerate}
So the remaining step to a final spatial differential PDE or full action
functional is no longer to determine the law-shape. It is to realize this
already fixed first-order autonomous form in a stronger analytic language.
\end{theorem}

\begin{proof}
The previous combined theorem had already shown that once the visible,
host-ledger, differential-flow, derivative-subsampling, and variational
data all live on one same selected realization, they collapse jointly to
one operator, one density, one scalar residual, and one zero set. The present
theorem sharpens that collapse to its explicit realized form:
\begin{enumerate}
\item the visible velocity, the block operator, the derivative field, and the
      effective flow are all the same selected generator \(G_{\mathrm{sel}}\);
\item the mixed and hidden differential blocks vanish exactly, and the
      derivative defect vanishes exactly, so the realized differential form
      is already block-diagonal and defect-free on the selected cut;
\item the common density is exactly the selected quadratic pairing
      \(\langle x,G_{\mathrm{sel}}x\rangle\), and the common scalar residual is
      exactly its signed-count scalarization;
\item the solution set is therefore exactly the same selected
      equation and hence exactly the same scalar PDE/action and evolution zero
      sets already forced earlier.
\end{enumerate}
This theorem fixes the strongest current answer to the realized-form question
before a final spatial differential PDE or full action functional is written
down: the law is already forced to be first-order, autonomous, quadratic, and
selected-cut exact.
\end{proof}

\begin{theorem}[The detached selected law already has one underlying state object]
\label{thm:the-detached-selected-law-already-has-one-underlying-state-object}\lean{ClosureCurrent.SelectedStateObject, ClosureCurrent.SelectedStateObjectSurface, ClosureCurrent.LocalEventFourStateLaw.selectedStateObject, ClosureCurrent.LocalEventFourStateLaw.selectedStateObjectSurface}
On the current detached selected cut, the law is already carried by one
underlying selected state object on the concrete four-coordinate carrier
\(\mathrm{State}\). Concretely:
\begin{enumerate}
\item the underlying visible object is one selected projection
      \(P_{\mathrm{sel}} : \mathrm{State}\to\mathrm{State}\);
\item the law of motion is one selected generator
      \(G_{\mathrm{sel}} : \mathrm{State}\to\mathrm{State}\);
\item the density, scalar residual, and selected equation are read directly
      from that same object by
\[
q_{\mathrm{sel}}(x)=\langle x,G_{\mathrm{sel}}x\rangle,\qquad
r_{\mathrm{sel}}(x)=\operatorname{sc}(q_{\mathrm{sel}}(x)),\qquad
x \text{ solves the selected equation } \Longleftrightarrow
      r_{\mathrm{sel}}(x)=0;
\]
\item any later stronger realization already agrees with this same
      state object on generator, density, scalar residual, and zero set.
\end{enumerate}
So the present unification target is not one scalar quantity. It is one
underlying state object with several derived readouts.
\end{theorem}

\begin{proof}
The key point is that the detached selected cut already carries one canonical
state object on the explicit carrier \(\mathrm{State}\), not merely several
parallel law formulations. Its projection is the selected cut projection, its
generator is the same selected generator \(G_{\mathrm{sel}}\), its density is
the same selected quadratic pairing, its scalar residual is the same
signed-count scalarization, and its zero set is the same selected equation.
The theorem then adds the realization-side rigidity: any later stronger
realization already agrees with that same state object on its visible
law data. So the various current law formulations are not separate physical
things. They are different readouts of one common selected state object.
\end{proof}

\paragraph{Best current expectation.}
The two theorems above are boundary theorems, not yet existence theorems for a
genuinely spatial differential PDE. But they now make the current best
candidate very sharp: the eventual stronger realization should be a direct
differential presentation of this same first-order autonomous selected state
object, with generator \(G_{\mathrm{sel}}\), density
\(q_{\mathrm{sel}}(x)=\langle x,G_{\mathrm{sel}}x\rangle\), scalar residual
\(r_{\mathrm{sel}}(x)=\operatorname{sc}(q_{\mathrm{sel}}(x))\), and the
recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and Einstein forms
appearing downstream as selected endpoint faces of that one law rather than as
independent primitive equations.

\begin{theorem}[Split completion target closes the completion chain]
\label{thm:split-completion-bridge-recovers-the-no-stage-completion-law}\lean{ClosureCurrent.FourStateReadout, ClosureCurrent.FourStateReadoutTarget, ClosureCurrent.ExactifierRealizationTarget, ClosureCurrent.FourStateReadout.readoutTarget, ClosureCurrent.FourStateReadout.toFourStateAssembly, ClosureCurrent.FourStateReadout.assemblyTargetOfExactifierTarget, ClosureCurrent.FourStateAssembly, ClosureCurrent.FourStateAssemblyTarget, ClosureCurrent.FourStateAssembly.readoutTarget, ClosureCurrent.FourStateAssembly.exactifierRealizationTarget, ClosureCurrent.FourStateAssembly.assemblyTarget, ClosureCurrent.CompletionClassificationTarget, ClosureCurrent.CompletionRigidity, ClosureCurrent.CompletionRigidityTarget, ClosureCurrent.CompletionRigidity.rigidityTarget, ClosureCurrent.CanonicalRepresentatives, ClosureCurrent.CanonicalRepresentativeTarget, ClosureCurrent.CanonicalRepresentatives.surface, ClosureCurrent.CompletionAlignment, ClosureCurrent.CompletionAlignment.toClassification, ClosureCurrent.CompletionAlignment.toCompletionRigidity, ClosureCurrent.CompletionAlignment.toCanonicalRepresentatives, ClosureCurrent.CompletionAlignment.toRigidityPrinciple, ClosureCurrent.CompletionAlignment.toNaturalOperatorCompletion, ClosureCurrent.CompletionAlignment.sameSelectedSelection, ClosureCurrent.CompletionAlignment.samePhysicalPrinciple, ClosureCurrent.CompletionAlignmentTarget, ClosureCurrent.CompletionAlignment.classificationTarget, ClosureCurrent.CompletionAlignment.rigidityTarget, ClosureCurrent.CompletionAlignment.canonicalRepresentativeTarget, ClosureCurrent.CompletionAlignment.alignmentTarget, ClosureCurrent.CompletionAlignment.ofParts, ClosureCurrent.CompletionSplitWitness, ClosureCurrent.CompletionSplitTarget, ClosureCurrent.CompletionSplitWitness.bridgeTarget, ClosureCurrent.CompletionSplitWitness.bridgeTargetSurface, ClosureCurrent.CompletionSplitWitness.completionTarget, ClosureCurrent.CompletionSplitWitness.completionTargetSurface, ClosureCurrent.ConstructiveSectorLaw.toIntrinsicSectorGeneration, ClosureCurrent.ConstructiveSectorLaw.fourStateAssemblyTargetOfParts, ClosureCurrent.ConstructiveSectorLaw.completionAlignmentTargetOfParts, ClosureCurrent.ConstructiveSectorLaw.completionSplitTarget, ClosureCurrent.ConstructiveSectorLaw.completionSplitTargetOfTargets, ClosureCurrent.ConstructiveSectorLaw.completionSplitTargetOfSplitData, ClosureCurrent.FourStateAssembly.toNoStageCompletionBridge, ClosureCurrent.ConstructiveSectorLaw.completionBridgeTarget, ClosureCurrent.ConstructiveSectorLaw.completionBridgeTargetOfTargets, ClosureCurrent.ConstructiveSectorLaw.completionBridgeTargetOfSplitData, ClosureCurrent.ConstructiveSectorLaw.completionTarget, ClosureCurrent.ConstructiveSectorLaw.completionTargetOfTargets, ClosureCurrent.ConstructiveSectorLaw.completionTargetOfSplitData, ClosureCurrent.ConstructiveSectorLaw.completionBridgeTargetSurface, ClosureCurrent.ConstructiveSectorLaw.completionBridgeTargetSurfaceOfTargets, ClosureCurrent.ConstructiveSectorLaw.completionBridgeTargetSurfaceOfSplitData, ClosureCurrent.ConstructiveSectorLaw.completionTargetSurface, ClosureCurrent.ConstructiveSectorLaw.completionTargetSurfaceOfTargets, ClosureCurrent.ConstructiveSectorLaw.completionTargetSurfaceOfSplitData, ClosureCurrent.NoStageCompletionBridgeTarget, ClosureCurrent.MicroscopicClosureLaw.completionTargetOfBridge, ClosureCurrent.MicroscopicClosureLaw.completionBridgeTargetSurface, ClosureCurrent.MicroscopicClosureLaw.completionBridgeTargetOfSplitTarget, ClosureCurrent.MicroscopicClosureLaw.completionTargetOfSplitTarget, ClosureCurrent.MicroscopicClosureLaw.completionBridgeTargetSurfaceOfSplitTarget, ClosureCurrent.MicroscopicClosureLaw.completionTargetSurfaceOfSplitTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.toConstructiveSectorLaw, ClosureCurrent.LocalEventFourStateCompletionLaw.toFourStateReadout, ClosureCurrent.LocalEventFourStateCompletionLaw.toFourStateAssembly, ClosureCurrent.LocalEventFourStateCompletionLaw.toCompletionRigidity, ClosureCurrent.LocalEventFourStateCompletionLaw.toCanonicalRepresentatives, ClosureCurrent.LocalEventFourStateCompletionLaw.toCompletionAlignment, ClosureCurrent.LocalEventFourStateCompletionLaw.fourStateReadoutTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.exactifierRealizationTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.fourStateAssemblyTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.completionClassificationTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.completionRigidityTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.canonicalRepresentativeTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.completionAlignmentTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.completionSplitTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.completionBridgeTargetOfSplitData, ClosureCurrent.LocalEventFourStateCompletionLaw.completionBridgeTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.completionBridgeTargetSurface, ClosureCurrent.LocalEventFourStateCompletionLaw.completionTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.completionTargetSurface}
Assume:
\begin{enumerate}
\item a self-contained constructive sector law on the detached current side;
\item a signed readout and genuine four-leg frame on that law;
\item the exactifier/generator intertwining identity on the assembled hidden
      state determined by that readout and frame;
\item a Step~4 rigidity datum intrinsic to that same sector
      generation;
\item reduced representative data on those sectors: four
      endpoint-sensitive canonical representatives together with the already
      classified kinetic face.
\end{enumerate}
Then, above that fixed constructive sector law, the second and third items
already realize the exact four-state assembly target, while the fifth item
already forces the weaker carrier-classification target and, together with the
fourth item, realizes the exact aligned Step~4 completion target.
More sharply, those same four constructive and Step~4 pieces already
realize one exact split completion target above the underlying microscopic law.
That split target itself retains only rigidity and the reduced representative
data on the Step~4 side, since carrier classification is recovered from it.
Equivalently, above the fixed constructive sector law they already force the
no-stage completion target directly. That smaller law-level target also yields
the exact completion-side bridge target, so the underlying microscopic law
admits one split completion bridge on that same datum. Therefore the no-stage
completion target is forced from this smaller split completion target, without
taking the already-assembled no-stage completion law itself as primitive input.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[No-stage completion law closes on its own selected datum]
\label{thm:matched-no-stage-continuum-law-closes-on-the-active-selected-datum}\lean{ClosureCurrent.SelectedSchurHFT2Surface, ClosureCurrent.selectedSchurHFT2Surface, ClosureCurrent.LocalEventFourStateCompletionLaw, ClosureCurrent.LocalEventFourStateCompletionLaw.toClassification, ClosureCurrent.LocalEventFourStateCompletionLaw.toNaturalOperatorCompletion, ClosureCurrent.LocalEventFourStateCompletionLaw.attachedSurface}
Assume a no-stage local-event four-state completion law on one selected datum.
Then no extra attachment stage remains:
\begin{enumerate}
\item the intrinsic selected-bundle and intrinsic sector-generation structures
      are already recovered on that same selected datum;
\item the matched detached generator still carries the bedrock law and is
      autonomous on that selected cut;
\item the forced four-state continuum law and the forced reduced hidden
      continuum law both live on that same selected datum;
\item the selected datum already carries the exact selected Schur/HFT-2
      closure statement;
\item therefore the full active completion statement closes there
      with no separate completion datum and no separate bridge-matching
      hypothesis.
\end{enumerate}
So the detached continuum extension now genuinely closes back into the active
selected-cut completion machinery from that same law alone rather than
merely resembling that machinery or matching to it externally.
Within that same datum, carrier classification is already recovered from the
canonical representative identities, so no separate classification datum is
stored at this stage.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[No-stage completion law reduces the remaining boundary target to the four endpoint frontiers]
\label{thm:no-stage-completion-law-reduces-the-remaining-flagship-seam-to-the-four-endpoint-frontiers}\lean{ClosureCurrent.LocalEventFourStateCompletionLaw.frontierBoundarySurface}
Assume a no-stage local-event four-state completion law.
Then:
\begin{enumerate}
\item the active completion statement is already internal to that same
      law;
\item once the exact phase, wave, gauge, and geometric endpoint frontiers are
      read on the one intrinsically selected bundle generated by that law,
      the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
      Einstein identities already follow;
\item no extra completion datum, no extra selected-datum matching, and no
      further common closure hypothesis remain beyond those four
      carrier-specific endpoint frontier data.
\end{enumerate}
So after the no-stage completion law is closed on its own selected datum, the
remaining endpoint burden is exactly the four frontier data and
nothing else.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[The remaining boundary target has an exact endpoint-witness form]
\label{thm:the-remaining-flagship-seam-has-an-exact-endpoint-witness-form}\lean{ClosureCurrent.PhaseEndpointWitness, ClosureCurrent.WaveEndpointWitness, ClosureCurrent.GaugeEndpointWitness, ClosureCurrent.GeometricEndpointWitness, ClosureCurrent.FlagshipEndpointWitnesses, ClosureCurrent.PhaseEndpointWitnessTarget, ClosureCurrent.WaveEndpointWitnessTarget, ClosureCurrent.GaugeEndpointWitnessTarget, ClosureCurrent.GeometricEndpointWitnessTarget, ClosureCurrent.FlagshipExactBoundaryTarget, ClosureCurrent.FlagshipExactTarget, ClosureCurrent.LocalEventFourStateCompletionLaw.endpointWitnessBoundarySurface, ClosureCurrent.NoStageCompletionWitness.phaseEndpointWitnessTargetOfFrontierTarget, ClosureCurrent.NoStageCompletionWitness.waveEndpointWitnessTargetOfFrontierTarget, ClosureCurrent.NoStageCompletionWitness.gaugeEndpointWitnessTargetOfFrontierTarget, ClosureCurrent.NoStageCompletionWitness.geometricEndpointWitnessTargetOfFrontierTarget, ClosureCurrent.NoStageCompletionWitness.flagshipExactBoundaryTargetOfLaneTargets, ClosureCurrent.NoStageCompletionWitness.endpointWitnessTargetOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.flagshipBoundaryTargetOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.flagshipExactBoundaryTargetOfBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.endpointWitnessTargetOfLaneTargets, ClosureCurrent.NoStageCompletionWitness.endpointWitnessTargetOfFrontierTargets, ClosureCurrent.NoStageCompletionWitness.flagshipSurfaceOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.flagshipSurfaceOfFrontierTargets, ClosureCurrent.NoStageCompletionWitness.normalFormTargetOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetSurfaceOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetOfEndpointLaneTargets, ClosureCurrent.NoStageCompletionWitness.normalFormTargetSurfaceOfEndpointLaneTargets, ClosureCurrent.NoStageCompletionWitness.normalFormTargetOfEndpointWitnessTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetSurfaceOfEndpointWitnessTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipExactTargetOfExactBoundaryTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipExactTargetOfBoundaryTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipTargetOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipSurfaceOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.normalFormTargetOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.normalFormTargetSurfaceOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.normalFormTargetOfFlagshipTarget, ClosureCurrent.MicroscopicClosureLaw.normalFormTargetSurfaceOfFlagshipTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipExactBoundaryTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipExactTarget}
Assume a no-stage local-event four-state completion law.
Then the remaining explicit boundary burden can be written in exact
carrier-specific witness form:
\begin{enumerate}
\item phase: endpoint collapse, phase-compatible Schur-tower data, and
      observable self-adjoint scalarization;
\item wave: endpoint collapse, selected-channel transport generation,
      scalar recursion, local internal datum, and admissible transport;
\item gauge: endpoint collapse and selected-channel gauge covariance;
\item geometry: endpoint collapse and orthogonal symmetric-tensor
      scalarization.
\end{enumerate}
Once these exact endpoint witnesses are read on the one intrinsically selected
bundle generated by the no-stage completion law, the recognizable
Schr\"odinger, wave/Klein--Gordon, Maxwell, and Einstein identities already
follow, with no additional common completion datum and no further
selected-datum matching. Equivalently, on a fixed no-stage completion witness,
the four exact carrier-specific endpoint-witness targets already reassemble
one exact fixed-witness boundary target, hence the aggregate endpoint-witness
target and therefore the direct normal-form conclusion; and, conversely, the
four frontier targets on that same witness already realize those exact
carrier-specific endpoint-witness targets and hence the same exact
fixed-witness boundary target. At the existence level,
one such fixed-witness exact boundary target already reassembles one
existence-level exact endpoint-witness target above the same microscopic law;
that exact target already yields the existence-level frontier target, the
endpoint-complete field statement, and the direct normal-form conclusion.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Exact target closes the full detached closure chain]
\label{cor:exact-target-closes-the-full-detached-closure-capstone}\lean{ClosureCurrent.FlagshipExactTarget, ClosureCurrent.FlagshipRecognizableTarget, ClosureCurrent.MicroscopicClosureLaw.completionTargetOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.originClosureTargetOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.sectorClosureTargetOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipRecognizableTargetOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.exactTargetFullClosureWitnessSurface, ClosureCurrent.MicroscopicClosureLaw.exactTargetFullNormalFormSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipExactTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.fullClosureWitnessSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.fullNormalFormSurface}
Assume:
\begin{enumerate}
\item a smaller microscopic closure law;
\item the existence-level exact endpoint-witness target above that same law.
\end{enumerate}
Then the second item already carries a no-stage completion witness on that same
law, and that witness already forces origin closure and sector closure there.
Hence both the full detached closure statement and the full detached
normal-form statement follow on one common no-stage completion witness. So the
exact target already suffices for both detached conclusions,
already subsumes the smaller recognizable target, and avoids both any separate
origin- or sector-closure hypothesis and any routing through the stronger
frontier presentation.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[Frontier targets yield the recognizable equation identities]
\label{thm:split-normal-form-bridge-yields-the-flagship-identities}\lean{ClosureCurrent.FlagshipNormalForms, ClosureCurrent.NormalFormTarget, ClosureCurrent.FlagshipRecognizableBoundaryTarget, ClosureCurrent.FlagshipRecognizableTarget, ClosureCurrent.FlagshipBoundaryTarget, ClosureCurrent.FlagshipExactBoundaryTarget, ClosureCurrent.FlagshipExactTarget, ClosureCurrent.FlagshipFrontierTarget, ClosureCurrent.PhaseFrontierTarget, ClosureCurrent.WaveFrontierTarget, ClosureCurrent.GaugeFrontierTarget, ClosureCurrent.GeometricFrontierTarget, ClosureCurrent.PhaseRecognizableTarget, ClosureCurrent.WaveRecognizableTarget, ClosureCurrent.GaugeRecognizableTarget, ClosureCurrent.GeometricRecognizableTarget, ClosureCurrent.NoStageCompletionWitness.flagshipRecognizableBoundaryTargetOfRecognizableTargets, ClosureCurrent.NoStageCompletionWitness.flagshipRecognizableBoundaryTargetOfFrontierTargets, ClosureCurrent.NoStageCompletionWitness.flagshipRecognizableBoundaryTargetOfBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.flagshipRecognizableBoundaryTargetOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.flagshipBoundaryTargetOfFrontierTargets, ClosureCurrent.NoStageCompletionWitness.flagshipExactBoundaryTargetOfBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.flagshipBoundaryTargetOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.endpointWitnessTargetOfBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.endpointWitnessTargetOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.flagshipSurfaceOfBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.flagshipSurfaceOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.phaseRecognizableTargetOfFrontierTarget, ClosureCurrent.NoStageCompletionWitness.waveRecognizableTargetOfFrontierTarget, ClosureCurrent.NoStageCompletionWitness.gaugeRecognizableTargetOfFrontierTarget, ClosureCurrent.NoStageCompletionWitness.geometricRecognizableTargetOfFrontierTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetOfRecognizableTargets, ClosureCurrent.NoStageCompletionWitness.normalFormTargetSurfaceOfRecognizableTargets, ClosureCurrent.NoStageCompletionWitness.normalFormTargetOfRecognizableBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetSurfaceOfRecognizableBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetSurfaceOfExactBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetOfBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetSurfaceOfBoundaryTarget, ClosureCurrent.NoStageCompletionWitness.normalFormTargetOfFrontierTargets, ClosureCurrent.NoStageCompletionWitness.normalFormTargetSurfaceOfFrontierTargets, ClosureCurrent.MicroscopicClosureLaw.flagshipRecognizableTargetOfRecognizableBoundaryTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipRecognizableTargetOfBoundaryTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipRecognizableTargetOfExactBoundaryTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipRecognizableTargetOfExactTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipRecognizableTargetOfFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipFrontierTargetOfBoundaryTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipTargetOfFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipExactTargetOfFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.flagshipSurfaceOfFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.normalFormTargetOfRecognizableTarget, ClosureCurrent.MicroscopicClosureLaw.normalFormTargetSurfaceOfRecognizableTarget, ClosureCurrent.MicroscopicClosureLaw.normalFormTargetOfFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.normalFormTargetSurfaceOfFrontierTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.phaseFrontierTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.waveFrontierTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.gaugeFrontierTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.geometricFrontierTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipRecognizableBoundaryTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipRecognizableTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipExactBoundaryTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipBoundaryTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipFrontierTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.normalFormTargetOfRecognizableTargets, ClosureCurrent.LocalEventFourStateFlagshipLaw.normalFormTargetOfFrontierTargets}
Assume:
\begin{enumerate}
\item a no-stage completion witness on the detached current side;
\item a phase endpoint frontier read on that witness's own selected bundle;
\item a wave endpoint frontier read on that same selected bundle;
\item a gauge endpoint frontier read on that same selected bundle;
\item a geometric endpoint frontier read on that same selected bundle.
\end{enumerate}
Then the second through fifth assumptions already realize the exact phase, wave,
gauge, and geometric frontier targets above that fixed no-stage completion
witness, hence one exact fixed-witness boundary target on that same selected
datum. That boundary target already yields the aggregate endpoint-witness
target and the direct normal-form conclusion above that fixed
witness. Equivalently, that same boundary target can be rewritten in exact
endpoint-witness form as one exact fixed-witness boundary target built
from the four carrier-specific endpoint-witness targets, and that exact form
already yields the same aggregate endpoint-witness target and the same direct
normal-form target. The no-stage completion law converts those same frontier
targets into the smaller recognizable carrier targets, and those four smaller
recognizable targets already reassemble one smaller fixed-witness recognizable
boundary target. That smaller recognizable boundary target already forces the
recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and Einstein
identities on that same selected datum. So the direct normal-form conclusion
is forced from either fixed-witness boundary form or from the smaller
recognizable boundary form, without taking the exact endpoint-witness data or
the older sector-rigidity data themselves as primitive input. At the
existence level, one such fixed-witness boundary target already reassembles
the existence-level frontier target, and one such fixed-witness recognizable
boundary target already reassembles a smaller
existence-level recognizable target. The frontier target therefore yields the
existence-level exact endpoint-witness target, hence also the smaller
existence-level recognizable target, and therefore the direct normal-form
target above the same microscopic law. The smaller recognizable target still
already suffices for the direct normal-form target alone.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Frontier target closes the full detached chain]
\label{cor:frontier-target-closes-the-full-detached-capstone}\lean{ClosureCurrent.FlagshipFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.completionTargetOfFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.originClosureTargetOfFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.sectorClosureTargetOfFrontierTarget, ClosureCurrent.MicroscopicClosureLaw.frontierTargetFullClosureWitnessSurface, ClosureCurrent.MicroscopicClosureLaw.frontierTargetFullNormalFormSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipFrontierTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.fullClosureWitnessSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.fullNormalFormSurface}
Assume:
\begin{enumerate}
\item a smaller microscopic closure law;
\item the existence-level frontier target above that same law.
\end{enumerate}
Then the second item already carries a no-stage completion witness on that same
law, and that witness already forces origin closure and sector closure there.
Hence both the full detached closure statement and the full detached
normal-form statement follow on one common no-stage completion witness. So the
existence-level frontier target is now the single remaining law-level input for
closing both detached conclusions on the optional upstream route.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Recognizable target closes the full detached normal-form chain]
\label{cor:recognizable-target-closes-the-full-detached-normal-form-capstone}\lean{ClosureCurrent.FlagshipRecognizableTarget, ClosureCurrent.MicroscopicClosureLaw.completionTargetOfRecognizableTarget, ClosureCurrent.MicroscopicClosureLaw.originClosureTargetOfRecognizableTarget, ClosureCurrent.MicroscopicClosureLaw.sectorClosureTargetOfRecognizableTarget, ClosureCurrent.MicroscopicClosureLaw.recognizableTargetFullNormalFormSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.flagshipRecognizableTarget, ClosureCurrent.LocalEventFourStateFlagshipLaw.fullNormalFormSurface}
Assume:
\begin{enumerate}
\item a smaller microscopic closure law;
\item the existence-level recognizable target above that same law.
\end{enumerate}
Then the second item already carries a no-stage completion witness on that same
law, and that witness already forces origin closure and sector closure there.
Hence the full detached normal-form statement follows on one common no-stage
completion witness. So the frontier target is stronger than
necessary for the normal-form conclusion: the smaller recognizable target
already suffices on its own.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[Detached completion datum closes the completion-side chain]
\label{thm:endpoint-complete-no-stage-law-closes-the-remaining-flagship-seam}\lean{ClosureCurrent.DetachedFlagshipPackage.completionNormalFormSurface, ClosureCurrent.DetachedFlagshipPackage.targetSurface, ClosureCurrent.DetachedFlagshipPackage.fullClosureWitnessSurface, ClosureCurrent.DetachedFlagshipPackage.fullNormalFormSurface}
Assume a detached completion datum. Then no explicit boundary hypothesis
remains within that detached presentation, because the same datum already
determines its own completion-side normal form and with it the
canonical-origin and completion statements:
\begin{enumerate}
\item the underlying proposition-level microscopic law already carries the
      theorem-bearing canonical-origin law, so the selected anchor, visible
      origin, and coherent selected-cut closure transport are no longer
      external witness inputs;
\item the active completion statement closes internally;
\item the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
       Einstein identities all follow directly;
\item no separate frontier data, no extra completion datum, and no further
       selected-datum matching input remain in the theorem statement.
\end{enumerate}
So this detached datum above the Part~II law is enough to carry the exact
completion-side closure chain on one selected datum.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[No-stage completion law forces the recognizable equation identities]
\label{thm:no-stage-completion-law-forces-the-recognizable-flagship-identities}\lean{ClosureCurrent.PhaseFrontier, ClosureCurrent.WaveFrontier, ClosureCurrent.GaugeFrontier, ClosureCurrent.GeometricFrontier, ClosureCurrent.FlagshipFrontiers, ClosureCurrent.LocalEventFourStateCompletionLaw.phaseSurface, ClosureCurrent.LocalEventFourStateCompletionLaw.waveSurface, ClosureCurrent.LocalEventFourStateCompletionLaw.gaugeSurface, ClosureCurrent.LocalEventFourStateCompletionLaw.geometricSurface, ClosureCurrent.LocalEventFourStateCompletionLaw.flagshipSurface}
Assume a no-stage local-event four-state completion law. Assume further that
the exact phase, wave, gauge, and geometric endpoint frontiers are all read on
the one intrinsically selected bundle carried by that same law.
Then:
\begin{enumerate}
\item the active completion statement still closes on that same datum;
\item the common selected closure law forces the recognizable Schr\"odinger
      identity on the phase carrier;
\item the same selected closure law forces the recognizable
      wave/Klein--Gordon identity on the wave carrier;
\item the same selected closure law forces the recognizable Maxwell identity
      on the gauge carrier;
\item the same selected closure law forces the recognizable Einstein identity
      on the geometric carrier.
\end{enumerate}
Thus once the detached no-stage law is closed and the exact endpoint
frontiers are read on its own intrinsically selected bundle, the standard
equations appear as recognizable carrier identities rather than as
independently postulated laws.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\paragraph{Constructive reading of the alternative normal form.}
The direct route through
Theorem~\ref{thm:endpoint-completion-law-recovers-the-strong-microscopic-package}
already suffices for the exact physical field. The present paragraph records
the alternative completion-side normal form.

At this point the late completion-side route of Part~II is best read constructively
rather than historically. The temporal realization law first fixes the
selected-cut realization theorem. A detached completion datum may then
determine the completion-side normal form. The chain now runs:
\[
\begin{aligned}
&\text{temporal realization law}
\;\Longrightarrow\;
\text{coherent realization theorem}
\;\Longrightarrow\;
\text{selected-cut closure}
\\
&\Longrightarrow\;
\text{completion datum}
\;\Longrightarrow\;
\text{completion-side normal form}
\;\Longrightarrow\;
\text{selected quadratic representative}
\\
&\Longrightarrow\;
\text{selected governing operator}
\;\Longrightarrow\;
\text{selected state-field law on }\mathrm{State}
\\
&\Longrightarrow\;
\text{one characteristic field on a horizon complex}
\;\Longrightarrow\;
\text{exact physical equation field.}
\end{aligned}
\]
The recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and Einstein
identities then appear as carrier realizations of that one field. The next theorem
states this chain in grouped form; the subsequent corollaries record its
successive formulations.

\begin{theorem}[Detached completion datum yields the physical field]
\label{thm:endpoint-complete-no-stage-law-already-carries-the-strongest-current-analytic-flagship-surface}\lean{ClosureCurrent.DetachedFlagshipPackage.analyticSurface, ClosureCurrent.DetachedFlagshipPackage.physicalEquationSurface}
Assume a detached completion datum.
Then on one and the same intrinsically selected datum:
\begin{enumerate}
\item the active completion statement closes internally, and the
      recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and Einstein
      identities all hold on that datum;
\item the law already determines one canonical selected quadratic
      representative, one least-motion stationary cut, one exact selected law,
      one matched selected generator, and hence one common
      selected governing operator together with its exact continuum-bridge
      structure and constitutive collapse;
\item that same governing law already collapses to one uniquely forced
      operator-residual law, one canonical scalar/first-order/evolution
      law chain, one exact realization ledger, one exact
      adjoint-goal ledger, and one common compatibility statement for every later
      differential, derivative-subsampling, or variational formulation;
\item all those formulations already live on one selected state object and one
      canonical selected state-field law on the concrete carrier
      \(\mathrm{State}\), and the current realization languages
      already present that same law exactly.
\end{enumerate}
Thus this detached completion datum already yields one exact \(\mathrm{State}\)-valued
physical field. The standard equations are recognizable endpoint realizations of that
one field rather than separate primitive laws, and the only remaining step is
a final external PDE/action presentation of this already-fixed object.
\end{theorem}

\begin{proof}
By the completion-side normal-form theorem, the detached completion datum
already determines the endpoint-complete no-stage law on the same selected
datum. The grouped field statement then follows on that datum, and
the exact physical equation field is read from that same selected state-field
law. Therefore this detached datum yields the whole current physical
field statement without introducing any second primitive law beside that
realized law. The additional datum is thereby isolated exactly.
\end{proof}

The next corollaries should therefore be read as successive formulations of the
same object, not as additional law discovery. They name,
in order, the shared selected state, the selected state-field law, the unified
differential field, the classwise boundary field, and finally the exact
physical equation field. The detailed reformulations are left to
Appendix~\ref{sec:appendix-dynamics}; the theorem-level content does not change.

\paragraph{Shared state and shared law.}
The first group isolates the common carrier and the common law before any
further boundary or realization presentation is named.

\begin{corollary}[Endpoint-complete no-stage law places the standard equations on one common selected state-field law]
\label{cor:endpoint-complete-no-stage-law-puts-the-flagship-equations-on-one-shared-selected-state}\lean{ClosureCurrent.FlagshipSharedStateSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.sharedStateSurface}
Assume the endpoint-complete no-stage law. Then:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
      Einstein identities all hold on one and the same intrinsically selected
      datum;
\item that same datum already carries one selected state object on the
      concrete carrier \(\mathrm{State}\);
\item every current realization formulation on that datum reads the same
      generator, block operator, derivative field, density, residual, and
      zero set from that same selected state object.
\end{enumerate}
So within the present hypotheses, the standard equations do not carry
separate primitive state variables; they are read on one common selected
state-field law.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Selected cut already carries the canonical state-field law]
\label{cor:detached-selected-cut-already-carries-one-canonical-selected-state-field-law}\lean{ClosureCurrent.SelectedStateFieldLaw, ClosureCurrent.LocalEventFourStateLaw.selectedStateFieldLawSurface}
Assume the no-stage local-event four-state law. Then the selected cut already
carries one canonical selected state-field law on the concrete carrier
\(\mathrm{State}\), namely:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item one selected projection;
\item one exact autonomous flow;
\item one common generator;
\item one quadratic density;
\item one scalar residual;
\item one common zero set.
\end{enumerate}
Moreover, every admitted formulation already agrees pointwise
with that same selected state-field law. So the remaining PDE/action problem is
not to discover another law object, but to realize this one in stronger
differential language.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Admitted formulations already realize the same state-field law]
\label{cor:current-stronger-realization-languages-already-present-one-same-selected-state-field-law}\lean{ClosureCurrent.SelectedStateFieldRealizationSurface, ClosureCurrent.LocalEventFourStateLaw.selectedStateFieldRealizationSurface}
Assume the no-stage local-event four-state law. Then the admitted stronger
formulations on the selected cut do not target different
underlying laws. The differential-flow formulation, the derivative-subsampling
formulation, and the variational/observer/Hamilton--Jacobi formulation all
present one and the same canonical selected state-field law on
\(\mathrm{State}\), with the same selected projection, the same generator, the
same residual, and the same common zero set.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Common state-field law for the standard equations]
\label{cor:endpoint-complete-no-stage-law-puts-the-flagship-equations-on-one-shared-selected-state-field-law}\lean{ClosureCurrent.FlagshipSharedStateFieldSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.sharedStateFieldSurface}
Assume the endpoint-complete no-stage law. Then:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
      Einstein identities all hold on one and the same selected realization;
\item that realization already carries one selected state-field law on the concrete
      carrier \(\mathrm{State}\);
\item the current stronger realization languages already present exactly that
      same selected state-field law.
\end{enumerate}
So within the present hypotheses, the standard equations do not merely
share one hidden selected state; they already sit on one same selected
state-field law.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\paragraph{Unified differential and boundary field.}
The next group names the same object at successively stronger formulations:
first as a unified field, then as a differential field, then as a transport
field, then as a boundary field, and finally as a classwise boundary field.

\begin{corollary}[Endpoint-complete no-stage law yields the unified field]
\label{cor:endpoint-complete-no-stage-law-already-yields-one-unified-field-package}\lean{ClosureCurrent.UnifiedField, ClosureCurrent.UnifiedFieldSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.unifiedFieldSurface}
Assume the endpoint-complete no-stage law. Then there is one explicit
unified field, namely:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item one canonical selected state-field law on the concrete carrier
      \(\mathrm{State}\);
\item the exact realization theorem showing that the differential,
      derivative, and variational formulations already present
      that same law;
\item the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
      Einstein identities as four carrier realizations of that same selected
      realization.
\end{enumerate}
So within the present hypotheses, the unified field is already given by one
explicit object, even though the final spatial differential PDE or full
action functional has not yet been
constructed.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Endpoint-complete no-stage law yields the unified differential field]
\label{cor:endpoint-complete-no-stage-law-already-yields-one-unified-differential-field-package}\lean{ClosureCurrent.UnifiedDifferentialField, ClosureCurrent.UnifiedDifferentialFieldSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.unifiedDifferentialFieldSurface}
Assume the endpoint-complete no-stage law. Then there is one explicit
unified differential field, namely:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item the unified field on the concrete carrier \(\mathrm{State}\);
\item one exact continuous block-derivative structure on that same carrier;
\item one exact effective-flow structure on that same carrier;
\item the derivative-subsampling and variational realization theorems
      as exact presentations of that same differential object.
\end{enumerate}
So the strongest realized form is not merely one shared hidden
state or one shared selected law, but one shared state-valued differential field whose
phase, wave, gauge, and geometric faces are already fixed on the same selected
realization. The remaining spatial-PDE step is now only to present this same
differential field in a final carrier language.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Endpoint-complete no-stage law leaves no new primitive carrier in the present scope]
\label{cor:endpoint-complete-no-stage-law-leaves-no-new-primitive-carrier-on-the-detached-flagship-surface}\lean{ClosureCurrent.NoNewPrimitiveCarrier, ClosureCurrent.StateCarrierRigiditySurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.noNewPrimitiveCarrier, ClosureCurrent.LocalEventFourStateFlagshipLaw.stateCarrierRigiditySurface}
Assume the endpoint-complete no-stage law. Then the present hypotheses already
leave no new primitive carrier choice:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item the unified differential field already lives on the concrete carrier
      \(\mathrm{State}\);
\item every admitted stronger realization language already collapses pointwise
      to the same selected generator, quadratic density, scalar residual, and
      zero set on that same carrier;
\item so any later spatial differential PDE or full action-functional
      presentation is a realization of that same \(\mathrm{State}\)-carried
      law, not a new primitive carrier law.
\end{enumerate}
This is exactly where the earlier structural chapters and the
continuum bridge enter: the differential,
derivative-subsampling, effective-flow, and variational interfaces already fix
the carrier-level language on \(\mathrm{State}\), so there is no remaining room
left to enlarge the primitive carrier while preserving the present hypotheses.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Endpoint-complete no-stage law yields the unified transport field]
\label{cor:endpoint-complete-no-stage-law-already-yields-one-unified-transport-field}\lean{ClosureCurrent.UnifiedTransportField, ClosureCurrent.UnifiedTransportFieldSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.unifiedTransportFieldSurface}
Assume the endpoint-complete no-stage law. Then there is one explicit
unified transport field on the concrete carrier \(\mathrm{State}\),
namely:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item the unified differential field on \(\mathrm{State}\);
\item the selected datum's concrete characteristic horizon realization and
      selected horizon;
\item the exact observer-side conservative transport triad on that same
      carrier;
\item the exact Hamilton--Jacobi projection bridge on that same carrier.
\end{enumerate}
So the present hypotheses are already attached to the earlier structural and
continuum-bridge boundary/transport grammar on one carrier. What remains is not a
new law or a new primitive carrier. It is only the final spatial differential
or action-functional presentation of that same \(\mathrm{State}\)-valued
transport field.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Endpoint-complete no-stage law yields the unified boundary field]
\label{cor:endpoint-complete-no-stage-law-already-yields-one-unified-boundary-field}\lean{ClosureCurrent.UnifiedBoundaryField, ClosureCurrent.UnifiedBoundaryFieldSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.unifiedBoundaryFieldSurface}
Assume the endpoint-complete no-stage law. Then the same
\(\mathrm{State}\)-valued unified transport field already carries one explicit
selected-horizon boundary field, consisting of:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item the unified transport field on \(\mathrm{State}\);
\item the identity of the selected cut with the realized horizon cut;
\item the observed boundary \(d_{\mathrm{obs}}\), leakage \(\ell\), return
      \(r\), and defect \(\delta\) maps on that same cut;
\item the exact identities
      \[
      d^2 = 0,\qquad
      d_{\mathrm{obs}}^2 = -\,\delta,\qquad
      \delta = r \circ \ell;
      \]
\item for every selected state \(u\) with \(\Pi_{\mathrm{sel}}u=u\),
      \[
      d u = d_{\mathrm{obs}}u + \ell u;
      \]
\item transport of the observed boundary and defect by the same selected
      evolution:
      \[
      U_t d_{\mathrm{obs}} = d_{\mathrm{obs}} U_t,\qquad
      U_t \delta = \delta U_t.
      \]
\end{enumerate}
So the present hypotheses already give not only one shared
\(\mathrm{State}\)-valued transport field, but one shared selected-horizon
boundary field on that same carrier. What remains is only to present that
already-fixed field in a final external differential or action-functional
language.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Endpoint-complete no-stage law yields the classwise boundary field]
\label{cor:endpoint-complete-no-stage-law-already-yields-one-classwise-unified-boundary-field}\lean{ClosureCurrent.UnifiedBoundaryClass, ClosureCurrent.UnifiedBoundaryClassSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.unifiedBoundaryClassSurface}
Assume the endpoint-complete no-stage law. Then the same selected-horizon
boundary field is already canonical across the whole admissible realized class
carried by the selected bridge:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item the least-motion selected datum is one root of an admissible realized
      class;
\item every datum in that class has the same selected horizon;
\item the same selected observed law is transported across the class by the
      horizon-preserving equivalences;
\item the same observed boundary and the same defect are transported across
      the class by those same equivalences.
\end{enumerate}
So the remaining external PDE/action step is not even a choice of selected
datum inside the admissible class. It is only a final presentation of one
already-fixed classwise \(\mathrm{State}\)-valued boundary field.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\paragraph{Final abstract closure.}
The last two corollaries state the final abstract conclusion:
the recognizable equations are carrier realizations of one physical field, and
that same field already comes with its exact realization and adjoint-goal ledgers.

\begin{corollary}[Endpoint-complete no-stage law yields the physical field]
\label{cor:endpoint-complete-no-stage-law-already-yields-one-physical-field}\lean{ClosureCurrent.PhysicalFieldSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.physicalFieldSurface}
Assume the endpoint-complete no-stage law. Then there is one
classwise \(\mathrm{State}\)-valued physical field on the present scope:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item one canonical selected-horizon boundary field across the whole
      admissible realized class;
\item the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
      Einstein identities on that same selected datum.
\end{enumerate}
So the present hypotheses no longer say only that the standard equations
share one state or one law. They are already carrier realizations of one same
classwise boundary field on the concrete carrier \(\mathrm{State}\). The
remaining PDE/action step is only to present that already-fixed field in a
final external language.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Endpoint-complete no-stage law yields an exact physical equation field]
\label{cor:endpoint-complete-no-stage-law-already-yields-one-exact-physical-equation-field}\lean{ClosureCurrent.PhysicalEquationField, ClosureCurrent.PhysicalEquationSurface, ClosureCurrent.LocalEventFourStateFlagshipLaw.physicalEquationSurface}
Assume the endpoint-complete no-stage law. Then there is one exact
\(\mathrm{State}\)-valued physical equation field on the present scope:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item one canonical selected-horizon boundary field across the whole
      admissible realized class;
\item one exact realization chain whose realized residual is
      exactly the generator of that same selected state-field law;
\item one exact adjoint-goal ledger whose goal error is exactly the density of
      that same selected state-field law;
\item the recognizable Schr\"odinger, wave/Klein--Gordon, Maxwell, and
      Einstein identities on that same selected realization.
\end{enumerate}
These are the standard external Schr\"odinger, Klein--Gordon, Maxwell, and
Einstein forms
\cite{Schrodinger1926,Klein1926,Maxwell1865,Einstein1915,Wald1984},
viewed as carrier realizations of one common field.
In the language of Part~I, this means the endpoint-complete microscopic
law already yields one characteristic field on a horizon complex, and the
recognizable equations are standard carrier realizations of that one field. We
therefore write the field in horizon-complex notation,
introducing \(\mathcal E_{\cH}\) for its PDE-form residual and
\(\delta S_{\cH}\) for its action-form Euler--Lagrange residual on
that same field:
\begin{tcolorbox}[colback=black!2, colframe=black!60, boxrule=0.8pt, title={Unified characteristic residual equation}]
\[
\begin{aligned}
\mathcal E_{\cH}(U)
  &= \delta S_{\cH}(U)
   = r_{\cH}(U) \\
  &= \operatorname{sc}\!\bigl(\langle U,G_{\cH}U\rangle_{\mathrm{cl}}\bigr),\\
r_{\cH}(U) &= 0.
\end{aligned}
\]
\end{tcolorbox}
Here \(U\) is the characteristic field on the horizon complex \(\cH\), and
\(G_{\cH}\) is its induced generator. This is the strongest external
PDE/action presentation currently certified: the PDE-form residual, the
action-form Euler--Lagrange residual, and the characteristic residual are
pointwise one same field, and the stronger variational, observer-side
transport, and Hamilton--Jacobi residual formulations collapse to that same field
in the present hypotheses. In the present coordinate
realization this is exactly the selected equation
\[
\begin{aligned}
\mathcal E_{\mathrm{sel}}(x)
  &= \delta S_{\mathrm{sel}}(x)
   = r_{\mathrm{sel}}(x) \\
  &= \operatorname{sc}\!\bigl(\langle x,G_{\mathrm{sel}}x\rangle_{\mathrm{cl}}\bigr),\\
r_{\mathrm{sel}}(x) &= 0.
\end{aligned}
\]
So the abstract closure statement is now complete. The remaining PDE/action step is no longer to
determine the field, the law, or the state. It is only to write this
already-fixed exact physical equation field in a final external language.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Microscopic selected-bundle data]
\label{def:microscopic-selected-bundle-readout}\lean{ClosureCurrent.BundleReadout}
Fix one selected datum together with its selected continuum closure class.
\emph{Microscopic selected-bundle data} consist of four visible carrier
realizations, phase, wave, gauge, and geometric, all read on that same
selected bundle, together with one common continuum-closure transport law on
that same selected cut. Its role is to replace carrier-by-carrier selected-cut and
closure-class hypotheses by one common transport law on the selected bundle.
\end{definition}

\begin{theorem}[Microscopic selected-bundle data force carrier closure transport]
\label{thm:microscopic-selected-bundle-readout-forces-carrier-closure-transport}\lean{ClosureCurrent.SelectedBundleForcing.readoutSurface}
Assume a detached bridge datum together with a selected-bundle assembly and
microscopic selected-bundle data on the same selected cut. Then every
phase, wave, gauge, or geometric carrier realized on that bundle inherits the
same selected physical law, exact visibility on that cut, and the forced
continuum singleton for the selected closure law. Thus exact carrier closure
becomes a uniform consequence of one common selected-bundle
transport law rather than four separate carrier-specific hypotheses.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[Detached microscopic datum determines the forcing conclusion]
\label{thm:detached-microscopic-forcing-interface}\lean{ClosureCurrent.forcingSurface}
If the detached microscopic law supplies the selected-bundle data
and the intrinsic sector-generation clauses, then the forcing conclusion follows: one
obtains nonempty intrinsic selected-bundle existence, nonempty intrinsic
sector generation, a matched selected generator carrying the bedrock law,
autonomy and fiber invariance on the selected cut, generation from the
intrinsic channel algebra, minimal compatible realizations only, and the
canonical logical profile \([3,2,1]\).
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Role-indexed microscopic carrier family]
\label{def:role-indexed-microscopic-carrier-family}\lean{ClosureCurrent.VisibleCarrierRole, ClosureCurrent.RoleReadoutFamily}
A \emph{role-indexed microscopic carrier family} is one visible carrier family
indexed by the four present carrier roles
\[
\mathrm{phase},\qquad \mathrm{wave},\qquad \mathrm{gauge},\qquad \mathrm{geometric},
\]
such that every role is read on the same selected bundle. This replaces four
independent carrier-specific selected-cut predicates by one common role-indexed
carrier law.
\end{definition}

\begin{theorem}[Role-indexed microscopic law yields selected-bundle closure transport]
\label{thm:role-indexed-microscopic-law-forces-selected-bundle-closure-readout}\lean{ClosureCurrent.MicroscopicBundleLaw.surface}
Assume a detached microscopic selected-bundle law consisting of one matched
bridge datum, one selected-bundle assembly, one role-indexed microscopic
carrier family, and one common continuum-closure transport law on the same
selected cut. Then intrinsic selected-bundle existence holds,
the matched generator carries the bedrock law, the selected cut is autonomous
and fiber-invariant for that generator, and every visible carrier role read
from the microscopic family inherits the same selected physical law, exact
visibility on that cut, and the forced continuum singleton for the selected
closure law.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[Role-indexed microscopic sector law determines the forcing conclusion]
\label{thm:role-indexed-microscopic-sector-law-closes-current-forcing-seam}\lean{ClosureCurrent.MicroscopicSectorLaw.surface}
If the role-indexed microscopic selected-bundle law is supplemented by the
intrinsic sector-generation clauses, then the forcing conclusion follows: intrinsic
selected-bundle existence, intrinsic sector generation, selected-cut autonomy
and fiber invariance, role-indexed carrier closure transport, generation from
the intrinsic channel algebra, minimal compatible realizations only, and the
canonical logical profile \([3,2,1]\) all follow.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Detached exact exchange current law]
\label{def:detached-exact-exchange-current-law}\lean{ClosureCurrent.ExactExchangeCurrentLaw}
A \emph{detached exact exchange current law} consists of one matched selected
bridge datum, one bundle-first assembly law on the same selected bundle, one
common structural witness, one hidden exact exchange current with
conserved stock and direct/return compatibility, one role-indexed visible
carrier family read on that bundle, and one common continuum-closure transport
law on the same selected cut.
\end{definition}

\begin{definition}[Detached event exactification and autonomy law]
\label{def:detached-event-exactification-autonomy-law}\lean{ClosureCurrent.EventExactificationLaw}
A \emph{detached event exactification and autonomy law} is a detached exact
exchange current law together with local lossless exactification,
relabeling equivariance, autonomous primitive visible realization, visible
residual given by returned defect, and the intrinsic selected-bundle clauses
removing carrier-wise visibility as a separate hypothesis.
\end{definition}

\begin{theorem}[Two-law detached microscopic datum yields the selected-bundle conclusion]
\label{thm:two-law-detached-microscopic-package-forces-role-indexed-selected-bundle-surface}\lean{ClosureCurrent.EventExactificationLaw.surface}
The detached exact exchange current law together with the detached event
exactification/autonomy law already force the role-indexed microscopic
selected-bundle conclusion: intrinsic selected-bundle existence holds,
the matched selected generator carries the bedrock law, the selected cut is
autonomous and fiber-invariant for that generator, and every role in the
visible carrier family inherits the same selected physical law, exact
visibility on that cut, and the forced continuum singleton for the selected
closure law.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Two-law detached microscopic datum plus intrinsic sector clauses determines the forcing conclusion]
\label{cor:two-law-detached-microscopic-package-plus-intrinsic-sector-clauses-closes-current-forcing-seam}\lean{ClosureCurrent.EventExactificationSectorLaw.surface}
If the two-law detached microscopic datum is supplemented by the intrinsic
sector-generation clauses, then the forcing conclusion follows: intrinsic selected-bundle
existence, intrinsic sector generation, selected-cut autonomy, role-indexed
carrier closure transport, generation from the intrinsic channel algebra,
minimal compatible realizations only, and the canonical logical profile
\([3,2,1]\) all follow.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Detached local-event closure-current law]
\label{def:detached-local-event-closure-current-law}\lean{ClosureCurrent.LocalEventCurrentLaw}
A \emph{detached local-event closure-current law} consists of one matched
selected bridge datum, one selected visible physical law on the same
selected cut, one common structural witness, one selected observed bundle
with its five bundle sectors, and one hidden exact exchange current carried on
the oriented pair-comparison slots of the first closure-stable bulk event. The
same local datum also determines the bundle-first assembly, the role-indexed
visible carrier family, and the common continuum-closure transport law on that
selected cut.
\end{definition}

\begin{definition}[Detached local-event exactification/autonomy law]
\label{def:detached-local-event-exactification-autonomy-law}\lean{ClosureCurrent.LocalEventExactificationLaw}
A \emph{detached local-event exactification/autonomy law} is a detached
local-event closure-current law together with relabeling-equivariant local
lossless exactification, autonomous primitive visible realization, returned defect
as the visible residual, and the intrinsic selected-bundle clauses removing
carrier-wise visibility as a separate hypothesis.
\end{definition}

\begin{theorem}[Local-event microscopic law yields the selected-bundle conclusion]
\label{thm:local-event-microscopic-law-recovers-selected-bundle-surface}\lean{ClosureCurrent.LocalEventExactificationLaw.surface}
The detached local-event closure-current law together with the detached
local-event exactification/autonomy law already determine the bundle-first
assembly, the role-indexed visible carrier family, and the common
continuum-closure transport required by the earlier two-law microscopic
datum. Consequently the selected-bundle conclusion follows: intrinsic
selected-bundle existence holds, the matched selected generator
carries the bedrock law, the selected cut is autonomous and fiber-invariant
for that generator, and every visible carrier role read from the local-event
family inherits the same selected physical law, exact visibility on that cut,
and the forced continuum singleton for the selected closure law.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Local-event microscopic sector law determines the forcing conclusion]
\label{cor:local-event-microscopic-sector-law-closes-current-forcing-seam}\lean{ClosureCurrent.LocalEventSectorLaw.surface}
If the detached local-event exactification/autonomy law is supplemented by the
intrinsic sector-generation clauses, then the forcing conclusion follows from
that smaller local event/current
datum: intrinsic selected-bundle existence, intrinsic sector generation,
selected-cut autonomy, role-indexed carrier closure transport, generation from
the intrinsic channel algebra, minimal compatible realizations only, and the
canonical logical profile \([3,2,1]\) all follow.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Detached pair-exchange current object]
\label{def:detached-pair-exchange-current-object}\lean{ClosureCurrent.PairExchangeCarrier, ClosureCurrent.PairExchangeCurrent, ClosureCurrent.EventExactifier, ClosureCurrent.VisibleQuotient, ClosureCurrent.LocalEventObject}
A \emph{detached pair-exchange current object} consists of:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item one pair-exchange carrier with a neutral current value, a direct/return
      reversal involution, and a stock observable;
\item one local pair current on the event legs, vanishing on the diagonal and
      changing orientation by reversal under leg exchange;
\item one local event exactifier carrying exactification and returned-defect
      data on that current;
\item one visible quotient object for each present visible carrier role.
\end{enumerate}
The detached local-event closure-current law is then recovered by reading the
selected bundle, the role-indexed visible family, and the common continuum
closure transport from that object-level datum.
\end{definition}

\begin{theorem}[Detached pair-exchange current object recovers the local-event law]
\label{thm:detached-pair-exchange-current-object-recovers-local-event-law}\lean{ClosureCurrent.LocalEventObject.surface, ClosureCurrent.LocalEventObject.toLocalEventExactificationLaw}
The detached pair-exchange current object already supplies a genuine
mathematical representative of the detached microscopic proposal. In
particular it
provides a nonempty local pair current, direct/return compatibility on the
hidden carrier, autonomous visible quotient objects for the visible roles, and
local exactification with returned defect. Reading the selected-bundle data
from that object recovers the detached local-event exactification/autonomy law,
and therefore the same selected-bundle conclusion as before.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Detached pair-exchange current object determines the current forcing statement]
\label{cor:detached-pair-exchange-current-object-closes-current-forcing-seam}\lean{ClosureCurrent.LocalEventSectorObject.surface}
If the detached pair-exchange current object is supplemented by the intrinsic
non-dictionary sector-generation clauses, then the current upstream
law-completion statement is determined from that object-level datum: intrinsic
selected-bundle existence, intrinsic sector generation, the canonical logical
profile \([3,2,1]\), direct/return compatibility, and autonomous visible
quotient objects for the hidden current all follow.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Observer-realized detached current object]
\label{def:observer-realized-detached-current-object}\lean{ClosureCurrent.VisibleObserverRealization, ClosureCurrent.ObservedCurrentObject}
An \emph{observer-realized detached current object} is a detached
pair-exchange current object together with one observer-side realization of the
visible quotient values on the selected cut. The role-indexed selected-bundle
visibility predicates are then no longer primitive fields: they are induced by
feeding the current quotient value for each visible role through that observer
realization.
\end{definition}

\begin{theorem}[Observer-realized detached current object yields the selected-bundle conclusion]
\label{thm:observer-realized-detached-current-object-derives-selected-bundle-surface}\lean{ClosureCurrent.ObservedCurrentObject.surface, ClosureCurrent.ObservedCurrentObject.toLocalEventObject}
The observer-realized detached current object derives the selected-bundle
conclusion from the quotient object and its observer realization: the direct
visible sectors are witnessed by the current quotient values themselves, the
kinetic sector is witnessed by stock on a distinguished local leg, and the
role-indexed selected-bundle visibility predicates are induced by the observer
realization rather than stored independently. Consequently one recovers the
detached local-event object and nonempty intrinsic selected-bundle existence.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Observer-realized detached current sector object determines the reduced forcing statement]
\label{cor:observer-realized-detached-current-sector-object-closes-the-reduced-seam}\lean{ClosureCurrent.ObservedCurrentSectorObject.surface}
If the observer-realized detached current object is supplemented by the
intrinsic non-dictionary sector-generation clauses, then the reduced forcing
statement is determined from that smaller datum: one obtains a nonempty local
pair current, direct/return compatibility, autonomous minimal visible
quotients, intrinsic selected-bundle existence, intrinsic sector generation,
and the canonical logical profile \([3,2,1]\).
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Selected-observer current anchor]
\label{def:selected-observer-current-anchor}\lean{ClosureCurrent.CurrentAnchor}
A \emph{selected-observer current anchor} is the smallest present observer-side
datum for the detached current law: it keeps the hidden current object, the
visible quotient objects, and the closure identity at the selected bridge
observer itself, but it does not yet transport that closure identity to every
observer on the selected cut.
\end{definition}

\begin{theorem}[Selected-observer current anchor forces exact anchored closure]
\label{thm:selected-observer-current-anchor-forces-exact-anchored-closure}\lean{ClosureCurrent.CurrentAnchor.surface, ClosureCurrent.AnchoredCurrentObject.anchorSurface}
The selected-observer current anchor already carries the exact selected-observer
closure data: one obtains a nonempty local pair current, direct/return
compatibility, autonomous minimal visible quotients, exact visibility on the
selected bridge observer, and the forced continuum singleton on that anchored
observer. Thus the remaining observer-side burden is not “an observer
realization” in general; it is only the transport from that anchor to the full
selected cut.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Anchored current transport]
\label{def:anchored-current-transport}\lean{ClosureCurrent.AnchoredCurrentTransport}
\emph{Anchored current transport} is the next layer above the selected-observer
current anchor: it adds exactly the statement that the selected-law continuum
closure class transports to every observer reading the same selected cut.
\end{definition}

\begin{theorem}[Anchored current transport extends exact anchored closure to the full selected cut]
\label{thm:anchored-current-transport-extends-exact-anchored-closure-to-the-full-selected-cut}\lean{ClosureCurrent.AnchoredCurrentTransport.surface, ClosureCurrent.AnchoredCurrentObject.transportSurface}
Anchored current transport adds one and only one new conclusion above the
selected-observer current anchor: the full selected-cut closure transport law.
The current-side facts themselves are unchanged. Thus the observer-side
boundary
splits cleanly into exact anchored closure first, then transport from that
anchor to the whole selected cut.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Anchored detached current object]
\label{def:anchored-detached-current-object}\lean{ClosureCurrent.AnchoredCurrentObject}
An \emph{anchored detached current object} compresses the observer side further:
the visible quotient values are read at the selected bridge observer itself,
adds to the selected-observer current anchor the common selected-cut
continuum-closure transport law, and then supplements that transported
anchor by the remaining bundle-intrinsicity clauses needed to recover the
observer-realized detached current object.
\end{definition}

\begin{theorem}[Anchored detached current object recovers the observer-realized conclusion]
\label{thm:anchored-detached-current-object-recovers-the-observer-realized-surface}\lean{ClosureCurrent.AnchoredCurrentObject.surface, ClosureCurrent.AnchoredCurrentObject.toObservedCurrentObject}
The anchored detached current object already suffices to recover the
observer-realized detached current object. Thus the reduced current boundary
does
not need an independent observer family, fiber, or function-level observation
field: one selected bridge observer together with common closure transport
already yields a nonempty local pair current, direct/return compatibility,
autonomous minimal visible quotients, and nonempty intrinsic selected-bundle
existence.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Anchored detached current sector object determines the reduced forcing statement]
\label{cor:anchored-detached-current-sector-object-closes-the-reduced-seam}\lean{ClosureCurrent.AnchoredCurrentSectorObject.surface}
If the anchored detached current object is supplemented by the intrinsic
dictionary-free sector-generation clauses, then the reduced forcing statement is
determined from that still smaller datum: one obtains a nonempty local pair
current, direct/return compatibility, autonomous minimal visible quotients,
intrinsic selected-bundle existence, intrinsic sector generation, and the
canonical logical profile \([3,2,1]\).
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[Origin-observation target closes the origin seam]
\label{thm:origin-readout-law-forces-origin-closure}\lean{ClosureCurrent.OriginReadoutAnchor, ClosureCurrent.OriginReadoutAnchorTarget, ClosureCurrent.OriginReadoutClosureTarget, ClosureCurrent.OriginReadoutTransport, ClosureCurrent.OriginReadoutTransportTarget, ClosureCurrent.OriginReadoutTransport.ofParts, ClosureCurrent.OriginReadoutTransport.anchorTarget, ClosureCurrent.OriginReadoutTransport.closureTarget, ClosureCurrent.OriginReadoutClauses, ClosureCurrent.OriginReadoutClausesTarget, ClosureCurrent.OriginReadoutLaw, ClosureCurrent.OriginReadoutLaw.anchorTarget, ClosureCurrent.OriginReadoutLaw.closureTarget, ClosureCurrent.OriginReadoutLaw.transportTarget, ClosureCurrent.OriginReadoutLaw.clausesTarget, ClosureCurrent.OriginReadoutLaw.readoutTarget, ClosureCurrent.OriginReadoutLaw.ofParts, ClosureCurrent.OriginReadoutLaw.toOriginClosureWitness, ClosureCurrent.OriginReadoutTarget, ClosureCurrent.MicroscopicClosureLaw.originReadoutTransportTargetOfParts, ClosureCurrent.MicroscopicClosureLaw.originReadoutTargetOfParts, ClosureCurrent.MicroscopicClosureLaw.originClosureTargetOfReadout, ClosureCurrent.MicroscopicClosureLaw.originReadoutTargetSurface, ClosureCurrent.MicroscopicClosureLaw.originReadoutTargetSurfaceOfParts}
Fix one detached microscopic closure law. The remaining origin descent splits
into three smaller pieces: a selected-anchor current/quotient datum, a
selected-cut closure-transport law, and a common structural/intrinsicity
datum. The first two determine the selected-anchor transport law, and that
transport law together with the clauses datum determines the full
origin-observation law. Once that law is available, selected-bundle existence
is forced. Hence the detached selected-bundle forcing statement follows from
this smaller origin-observation target with no additional origin witness
input.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[Local-event exactification law reduces the origin seam to anchor data]
\label{thm:local-event-exactification-law-reduces-origin-seam-to-transport}\lean{ClosureCurrent.ConstructiveAnchorCurrentTarget, ClosureCurrent.LocalEventExactificationLaw.toMicroscopicClosureLaw, ClosureCurrent.LocalEventExactificationLaw.toOriginReadoutClauses, ClosureCurrent.LocalEventExactificationLaw.clausesTarget, ClosureCurrent.LocalEventExactificationLaw.closureTarget, ClosureCurrent.LocalEventExactificationLaw.originReadoutTransportTargetOfAnchor, ClosureCurrent.LocalEventExactificationLaw.originReadoutTargetOfAnchor, ClosureCurrent.LocalEventExactificationLaw.originClosureTargetOfAnchor, ClosureCurrent.LocalEventExactificationLaw.originTargetSurfaceOfAnchor, ClosureCurrent.LocalEventExactificationLaw.toConstructiveMicroscopicClauses, ClosureCurrent.LocalEventExactificationLaw.constructiveMicroscopicClausesTarget, ClosureCurrent.LocalEventExactificationLaw.constructiveCurrentTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.LocalEventExactificationLaw.constructiveMicroscopicTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.LocalEventExactificationLaw.originReadoutTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.LocalEventExactificationLaw.originClosureTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.LocalEventExactificationLaw.originTargetSurfaceOfConstructiveAnchorCurrentTarget}
Fix one detached local-event exactification law. It already determines the
smaller proposition-level microscopic closure law on the same bridge and
selected physical law, together with the exact common
structural/intrinsicity target and the exact selected-cut closure-transport
target for that smaller law. Therefore the remaining origin seam is exactly
the selected-anchor current/quotient target. Once that target is met, the
selected-anchor transport target, the origin-observation target, the
origin-closure target, and the detached selected-bundle forcing statement
follow immediately. In the sharper constructive formulation, the same
exactification law already realizes the exact selected-cut closure-transport
target and the exact structural/intrinsicity target for the constructive
microscopic layer, so the remaining constructive origin seam is exactly the
constructive anchor-current target. Once that target is met, the constructive
current target, the constructive microscopic target, the origin-observation
target, the origin-closure target, and the detached selected-bundle forcing
statement again follow immediately.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{theorem}[Canonical-origin microscopic law forces origin closure]
\label{thm:constructive-microscopic-law-forces-origin-closure}\lean{ClosureCurrent.CanonicalOriginLaw, ClosureCurrent.CanonicalOriginLaw.target, ClosureCurrent.CanonicalOriginLaw.originClosureTarget, ClosureCurrent.CanonicalOriginLaw.canonicalOriginSurface, ClosureCurrent.CanonicalOriginLaw.surface, ClosureCurrent.StrongMicroscopicLaw.toCanonicalOriginLaw, ClosureCurrent.ConstructiveAnchorCurrentLaw, ClosureCurrent.ConstructiveAnchorCurrentTarget, ClosureCurrent.OriginReadoutClosureTarget, ClosureCurrent.ConstructiveCurrentLaw, ClosureCurrent.ConstructiveCurrentTarget, ClosureCurrent.ConstructiveMicroscopicClauses, ClosureCurrent.ConstructiveMicroscopicClausesTarget, ClosureCurrent.ConstructiveMicroscopicLaw, ClosureCurrent.ConstructiveMicroscopicTarget, ClosureCurrent.ConstructiveAnchorCurrentLaw.toMicroscopicClosureLaw, ClosureCurrent.ConstructiveAnchorCurrentLaw.toOriginReadoutAnchor, ClosureCurrent.ConstructiveAnchorCurrentLaw.originReadoutAnchorTarget, ClosureCurrent.ConstructiveAnchorCurrentLaw.toConstructiveCurrentLaw, ClosureCurrent.ConstructiveAnchorCurrentLaw.target, ClosureCurrent.ConstructiveCurrentLaw.toMicroscopicClosureLaw, ClosureCurrent.ConstructiveCurrentLaw.toOriginReadoutTransport, ClosureCurrent.ConstructiveCurrentLaw.toConstructiveAnchorCurrentLaw, ClosureCurrent.ConstructiveCurrentLaw.originReadoutClosureTarget, ClosureCurrent.ConstructiveCurrentLaw.originReadoutTransportTarget, ClosureCurrent.ConstructiveCurrentLaw.anchorCurrentTarget, ClosureCurrent.ConstructiveCurrentLaw.target, ClosureCurrent.ConstructiveMicroscopicClauses.toOriginReadoutClauses, ClosureCurrent.ConstructiveMicroscopicClauses.originReadoutClausesTarget, ClosureCurrent.ConstructiveMicroscopicClauses.target, ClosureCurrent.ConstructiveMicroscopicLaw.toConstructiveCurrentLaw, ClosureCurrent.ConstructiveMicroscopicLaw.toConstructiveMicroscopicClauses, ClosureCurrent.ConstructiveMicroscopicLaw.toMicroscopicClosureLaw, ClosureCurrent.ConstructiveMicroscopicLaw.toOriginReadoutLaw, ClosureCurrent.ConstructiveMicroscopicLaw.originReadoutClosureTarget, ClosureCurrent.ConstructiveMicroscopicLaw.anchorCurrentTarget, ClosureCurrent.ConstructiveMicroscopicLaw.currentTarget, ClosureCurrent.ConstructiveMicroscopicLaw.clausesTarget, ClosureCurrent.ConstructiveMicroscopicLaw.originReadoutTarget, ClosureCurrent.ConstructiveMicroscopicLaw.originClosureTarget, ClosureCurrent.ConstructiveMicroscopicLaw.originTargetSurface, ClosureCurrent.MicroscopicClosureLaw.constructiveCurrentTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.originReadoutAnchorTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.originReadoutTransportTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.originReadoutTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.originClosureTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.originTargetSurfaceOfConstructiveAnchorCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.constructiveMicroscopicTargetOfConstructiveAnchorCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.constructiveAnchorCurrentTargetOfConstructiveCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.originReadoutTransportTargetOfConstructiveCurrentTarget, ClosureCurrent.MicroscopicClosureLaw.originReadoutClausesTargetOfConstructiveMicroscopicClausesTarget, ClosureCurrent.MicroscopicClosureLaw.originReadoutTargetOfConstructiveParts, ClosureCurrent.MicroscopicClosureLaw.originClosureTargetOfConstructiveParts, ClosureCurrent.MicroscopicClosureLaw.originTargetSurfaceOfConstructiveParts, ClosureCurrent.MicroscopicClosureLaw.constructiveMicroscopicTargetOfParts, ClosureCurrent.MicroscopicClosureLaw.constructiveCurrentTargetOfConstructiveMicroscopicTarget, ClosureCurrent.MicroscopicClosureLaw.constructiveAnchorCurrentTargetOfConstructiveMicroscopicTarget, ClosureCurrent.MicroscopicClosureLaw.constructiveMicroscopicClausesTargetOfConstructiveMicroscopicTarget, ClosureCurrent.MicroscopicClosureLaw.originReadoutTargetOfConstructiveMicroscopicTarget, ClosureCurrent.MicroscopicClosureLaw.originClosureTargetOfConstructiveMicroscopicTarget, ClosureCurrent.MicroscopicClosureLaw.originTargetSurfaceOfConstructiveMicroscopicTarget, ClosureCurrent.AnchoredCurrentObject.toConstructiveMicroscopicLaw}
If the detached microscopic law is read at the first constructive level that
already carries its own selected anchor, visible origin, coherent
selected-cut closure transport, exactifier, and bundle-intrinsic structure on
one selected datum, then existence of the selected bundle is no longer an
extra hypothesis. In
particular, every anchored detached current object determines such a
canonical-origin microscopic law by forgetting only its distinguished leg.
This canonical-origin law already determines:
\begin{enumerate}
\item the smaller proposition-level microscopic closure law on the same bridge
      and selected physical law;
\item the still smaller constructive anchor-current law, the still smaller
      constructive current law, and the still smaller common
      structural/intrinsicity clause datum on that same microscopic law;
\item therefore the exact constructive anchor-current target, the exact
      constructive current target, and the exact structural/intrinsicity target
      for that law;
\item therefore the exact selected-anchor transport target and the exact
      origin-observation clauses target for that law;
\item therefore the exact origin-observation target for that law;
\item therefore the origin-closure target for that law;
\item hence the detached selected-bundle forcing statement, with no additional
      origin witness input.
\end{enumerate}
Equivalently, the remaining law-level origin descent splits into three pieces:
a constructive anchor-current realization, a selected-cut closure-transport
law, and a common structural/intrinsicity datum on the same selected datum.
Once these are present, the origin-observation target, the origin-closure
target, and the detached selected-bundle forcing statement follow directly;
they also recover the intermediate constructive current target and hence the
constructive microscopic law. Thus selected-bundle existence is forced by this
self-contained constructive law, through the anchor-current target, the
closure target, the clauses target, and then the origin-observation layer.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Constructive sector law forces sector closure]
\label{cor:constructive-sector-law-forces-sector-closure}\lean{ClosureCurrent.ConstructiveSectorLaw, ClosureCurrent.ConstructiveSectorTarget, ClosureCurrent.ConstructiveSectorLaw.target, ClosureCurrent.AnchoredCurrentSectorObject.toConstructiveSectorLaw, ClosureCurrent.ConstructiveSectorLaw.toConstructiveMicroscopicLaw, ClosureCurrent.ConstructiveSectorLaw.sectorClosureTarget, ClosureCurrent.ConstructiveSectorLaw.sectorTargetSurface, ClosureCurrent.MicroscopicClosureLaw.constructiveMicroscopicTargetOfConstructiveSectorTarget, ClosureCurrent.MicroscopicClosureLaw.originClosureTargetOfConstructiveSectorTarget, ClosureCurrent.MicroscopicClosureLaw.sectorClosureTargetOfConstructiveSectorTarget, ClosureCurrent.MicroscopicClosureLaw.sectorTargetSurfaceOfConstructiveSectorTarget}
If that self-contained constructive microscopic law is supplemented by the
canonical generation datum and the two intrinsic sector-generation clauses,
then the sector-closure target is forced as well. In particular, every
anchored current sector object descends to such a constructive sector law by
forgetting only its distinguished leg.
Equivalently, the exact law-level Step~3 descent target is now one
constructive sector realization on the same selected datum: once the bare
detached microscopic law admits that realization, the constructive microscopic
target, the origin-closure target, the sector-closure target, and the detached
Step~3 forcing statement follow formally.
Therefore the detached Step~3 forcing statement already follows from that
constructive sector law with no extra origin- or sector-witness hypotheses.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Observation-field detached current object]
\label{def:observation-field-detached-current-object}\lean{ClosureCurrent.VisibleObservationField, ClosureCurrent.ObservationFieldObject}
An \emph{observation-field detached current object} replaces the predicate
formulation of the observer realization by a family of selected observers
together with a role-indexed observation field assigning a visible quotient
value to each selected observer. The earlier predicate formulation is then
recovered from that observation field.
\end{definition}

\begin{theorem}[Observation-field detached current object recovers the observer realization]
\label{thm:observation-field-detached-current-object-recovers-the-observer-realized-surface}\lean{ClosureCurrent.ObservationFieldObject.surface, ClosureCurrent.ObservationFieldObject.toObservedCurrentObject}
The observation-field detached current object recovers the observer-realized
detached current object. Thus the predicate formulation of the observer
realization is no longer primitive: it is induced by a family of selected
observers and a role-indexed observation field. Consequently one still
obtains a nonempty local pair current, direct/return compatibility,
autonomous minimal visible quotients, and nonempty intrinsic selected-bundle
existence.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Observation-field detached current sector object determines the reduced forcing statement]
\label{cor:observation-field-detached-current-sector-object-closes-the-reduced-seam}\lean{ClosureCurrent.ObservationFieldSectorObject.surface}
If the observation-field detached current object is supplemented by the
intrinsic dictionary-free sector-generation clauses, then the reduced forcing
statement is determined from that observation field: one obtains a nonempty
local pair current, direct/return compatibility, autonomous minimal visible
quotients, intrinsic selected-bundle existence, intrinsic sector generation,
and the canonical logical profile \([3,2,1]\).
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{definition}[Observer-fiber detached current object]
\label{def:observer-fiber-detached-current-object}\lean{ClosureCurrent.SelectedObserverFiber, ClosureCurrent.FiberObservationField, ClosureCurrent.FiberObservationObject}
An \emph{observer-fiber detached current object} replaces the
observation-field formulation by a fiber of selected observers on the chosen
cut together with a role-indexed observation map on that fiber. The earlier
predicate formulation of the observer realization is then read directly from
the fiber points, without first rebuilding an observation field.
\end{definition}

\begin{theorem}[Observer-fiber detached current object recovers the observer realization]
\label{thm:observer-fiber-detached-current-object-recovers-the-observer-realized-surface}\lean{ClosureCurrent.FiberObservationObject.surface, ClosureCurrent.FiberObservationObject.toObservedCurrentObject}
The observer-fiber detached current object already suffices to recover the
observer-realized detached current object. Thus the reduced current boundary
does not need the stronger observation-field interface: a fiber of selected
observers together with a role-indexed observation map already yields a
nonempty local pair current, direct/return compatibility, autonomous minimal
visible quotients, and nonempty intrinsic selected-bundle existence.
\end{theorem}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{corollary}[Observer-fiber detached current sector object determines the reduced forcing statement]
\label{cor:observer-fiber-detached-current-sector-object-closes-the-reduced-seam}\lean{ClosureCurrent.FiberObservationSectorObject.surface}
If the observer-fiber detached current object is supplemented by the intrinsic
dictionary-free sector-generation clauses, then the reduced forcing statement
is determined from that fiber datum: one obtains a nonempty local pair
current, direct/return compatibility, autonomous minimal visible quotients,
intrinsic selected-bundle existence, intrinsic sector generation, and the
canonical logical profile \([3,2,1]\).
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

