% ============================================================
\section{External Realizations of the Pre-Dynamical Interface}
\label{sec:temporal-interface-portability}
% ============================================================

This chapter isolates the exact interface on which the Part~II temporal
realization surface acts. The earlier chapters furnish one internal
derivation of that interface from the monograph's own bedrock route. The
present point is that the same Part~II law surface can then be read on any
external host that realizes the same ordered-persistence datum, faithful cut
class, selected visible law, and residual-return grammar. The claim is
therefore one of portability.

Internal derivation and external realization play distinct roles. The
monograph derives the pre-dynamical temporal interface from its own theorem
chain. An external continuum, operator, Hilbert, or coarse-grained host may
instantiate that same interface under explicit hypotheses. Once the interface
is present, the temporal realization surface acts on it unchanged, and the
detached flagship theorem remains conditional only on that law surface
together with its explicit completion datum.
Accordingly, the Part~II physical-law surface is not tied to a literal thesis
that the physical host must first be accepted as fundamentally discrete. It is
stated at the exported interface level and may be imposed on any host carrying
that interface under explicit hypotheses.

\subsection{The Exported Interface Package}

\begin{definition}[Pre-dynamical temporal interface package]
\label{def:pre-dynamical-temporal-interface-package}\lean{PartIVExportedTemporalInterfaceDatum, SelectedVisibleEffectiveLaw, SelectedSchur.ExactResidue}
Fix a realized family on which the structural and continuum bridge data of the
earlier chapters are available. A \emph{pre-dynamical temporal interface package}
for that family consists of:
\begin{enumerate}[label=(\roman*), leftmargin=2em, itemsep=0.2em]
\item a temporal interface datum in the sense of
      Definition~\ref{def:temporal-interface-datum}, equivalently an exported
      ordering datum \((D=3,[\Theta])\) as in
      Corollary~\ref{cor:temporal-interface-precedes-physical-time};
\item a nonempty admissible class of faithful visible cuts carrying that same
      ordered persistence, together with the horizon-preserving equivalence
      relation by which observer changes are compared on that class;
\item on each admissible cut, a coherent operator on one coherent bundle and
      the corresponding selected visible effective law of
      Definition~\ref{def:selected-visible-effective-law}, obtained by exact
      internal elimination on that same bundle;
\item on each admissible cut, the same exact residual-return / Schur grammar,
      together with the inherited selected endpoint closure class furnished by
      Corollary~\ref{cor:inherited-minimal-order-closure-class}.
\end{enumerate}
\end{definition}

Definition~\ref{def:pre-dynamical-temporal-interface-package} is
\emph{pre-dynamical} in the precise sense that it does not yet identify the
exported order datum with physical before/after and does not yet select the
physically realized cut. Those are the tasks of the Part~II temporal
realization surface.

\begin{proposition}[Internal derivation of the pre-dynamical interface]
\label{prop:monograph-factors-through-interface-package}\lean{partIV_temporal_interface_from_d3, partIV_temporal_interface_precedes_physical_time, canonical_selected_schur_realization}
On the present scope, the earlier theorem chain together with the selected-cut
structures assembled in Part~II furnish a pre-dynamical temporal interface
package in the sense of
Definition~\ref{def:pre-dynamical-temporal-interface-package}.
\end{proposition}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\subsection{External Hosts}

\begin{definition}[External host realization of the interface package]
\label{def:external-host-realization-interface-package}\lean{PartIVExportedTemporalInterfaceDatum, SelectedVisibleEffectiveLaw}
An \emph{external host realization} of the pre-dynamical temporal interface
package is any classical continuum, Hilbert, operator, or coarse-grained
framework that explicitly realizes the four items of
Definition~\ref{def:pre-dynamical-temporal-interface-package} on one and the
same host family.
\end{definition}

Definition~\ref{def:external-host-realization-interface-package} records only
that the four interface items are present on one host family. Once they are
given, the preceding Part~II law-side development no longer depends on the
route by which that interface was obtained.

\begin{corollary}[Portability of temporal realization and common grammar]
\label{cor:portability-of-temporal-realization-and-common-grammar}\lean{PhysicalRealizationPrinciple, physical_realization_principle}
Let an external host realization in the sense of
Definition~\ref{def:external-host-realization-interface-package} be given. If
the Part~II temporal realization surface is then imposed on that host, the
common law-side development of the preceding Part~II chapters applies
unchanged on that host family: the physically realized cut is selected within
the host's faithful cut class, the observable dynamics are the selected
visible effective law on that cut, admissible visible forcing is only
returned residual from the same coherent bundle, and no exogenous constitutive
completion is admitted on that cut. Any later carrier result whose hypotheses
mention only this interface package together with carrier-local compatibility
and endpoint conditions may then be read on that same host as well.
\end{corollary}

(Proof in Appendix~\ref{sec:appendix-dynamics}.)

\begin{tcolorbox}[colback=white, colframe=black!70, title={Portability Claim of This Chapter}]
\begin{itemize}[itemsep=0.2em, leftmargin=1.5em]
\item The earlier theorem chain furnishes one internal derivation of the
      pre-dynamical temporal interface.
\item Any external host realizing that same interface carries the Part~II
      temporal realization surface and its common selected-cut grammar
      unchanged.
\item This portability statement leaves the narrower bedrock-certified claim
      untouched: the certified bedrock route remains the rebuilt
      bedrock-and-tower lane.
\item The detached flagship completion lane is portable as well, provided its
      explicit extra completion datum is imposed on the same realized host.
\end{itemize}
\end{tcolorbox}

This is the level at which the Part~II physical law surface is stated.
Internally, the monograph derives the interface from Constancy, Existence,
Incidence, Closure Balance, realized models, and the continuum bridge.
Externally, the same law may be tested on any host that carries the same
interface. The resulting statement is that the Part~II temporal realization
surface is a portable closure law on a pre-dynamical temporal interface, one
derivation of which is furnished by the monograph itself.

The included one-way validation lane recorded in
Appendix~\ref{subsec:formal-mathlib-bridge} already supports this reading at
the level of standard mathematical realizability: several bridge-side,
Hilbert-side, and operator-side components of the exported interface package
now admit explicit mathlib realizations without feeding any extra axioms back
into the bedrock-certified spine.
