\section*{References}

\begin{thebibliography}{99}

\bibitem{AdamsFournier2003}
R.~A.~Adams and J.~J.~F.~Fournier,
\emph{Sobolev Spaces},
2nd ed., Academic Press, Amsterdam, 2003.

\bibitem{Arnold1989}
V.~I.~Arnold,
\emph{Mathematical Methods of Classical Mechanics},
2nd ed., Springer, New York, 1989.

\bibitem{Antoulas2005}
A.~C.~Antoulas,
\emph{Approximation of Large-Scale Dynamical Systems},
SIAM, Philadelphia, 2005.

\bibitem{ArnoldFalkWinther2006}
D.~N.~Arnold, R.~S.~Falk, and R.~Winther,
``Finite element exterior calculus, homological techniques, and applications,''
\emph{Acta Numerica} 15 (2006), 1--155.

\bibitem{ArvanitakisHohmHullLekeu2020}
A.~S.~Arvanitakis, O.~Hohm, C.~Hull, and V.~Lekeu,
``Homotopy Transfer and Effective Field Theory I: Tree-level,''
\emph{Fortschritte der Physik} 70 (2022), 2200003; arXiv:2007.07942.

\bibitem{BobbinEtAl2024}
M.~P.~Bobbin, S.~Sharlin, P.~Feyzishendi, A.~H.~Dang, C.~M.~Wraback, and T.~R.~Josephson,
``Formalizing chemical physics using the Lean theorem prover,''
\emph{Digital Discovery} 3 (2024), 264--280.

\bibitem{Bombieri2000}
E.~Bombieri,
\emph{Problems of the Millennium: The Riemann Hypothesis},
Clay Mathematics Institute, 2000.

\bibitem{BreuerPetruccione2002}
H.-P.~Breuer and F.~Petruccione,
\emph{The Theory of Open Quantum Systems},
Oxford University Press, Oxford, 2002.

\bibitem{BriggsHensonMcCormick2000}
W.~L.~Briggs, V.~E.~Henson, and S.~F.~McCormick,
\emph{A Multigrid Tutorial},
2nd ed., SIAM, Philadelphia, 2000.

\bibitem{Brillouin1953}
L.~Brillouin,
\emph{Wave Propagation in Periodic Structures},
Dover, New York, 1953.

\bibitem{Bishop1967}
E.~Bishop,
\emph{Foundations of Constructive Analysis},
McGraw-Hill, New York, 1967.

\bibitem{Cercignani1988}
C.~Cercignani,
\emph{The Boltzmann Equation and Its Applications},
Springer, New York, 1988.

\bibitem{ChapmanCowling1970}
S.~Chapman and T.~G.~Cowling,
\emph{The Mathematical Theory of Non-Uniform Gases},
3rd ed., Cambridge University Press, Cambridge, 1970.

\bibitem{ChorinHaldKupferman2000}
A.~J.~Chorin, O.~H.~Hald, and R.~Kupferman,
``Optimal prediction and the Mori--Zwanzig representation of irreversible processes,''
\emph{Proceedings of the National Academy of Sciences of the USA} 97 (2000), 2968--2973.

\bibitem{Daubechies1992}
I.~Daubechies,
\emph{Ten Lectures on Wavelets},
SIAM, Philadelphia, 1992.

\bibitem{deMouraKongAvigadEtAl2015}
L.~de Moura, S.~Kong, J.~Avigad, F.~van Doorn, and J.~von Raumer,
``The Lean theorem prover (system description),''
in \emph{Automated Deduction---CADE-25},
Lecture Notes in Computer Science 9195,
Springer, Cham, 2015, pp.~378--388.

\bibitem{Dedekind1888}
R.~Dedekind,
\emph{Was sind und was sollen die Zahlen?},
Vieweg, Braunschweig, 1888.

\bibitem{Doob1953}
J.~L.~Doob,
\emph{Stochastic Processes},
Wiley, New York, 1953.

\bibitem{Dyson2004Fermi}
F.~Dyson,
``A meeting with Enrico Fermi,''
\emph{Nature} 427(6972) (2004), 297.
doi:\href{https://doi.org/10.1038/427297a}{10.1038/427297a}.

\bibitem{Eckmann1944}
B.~Eckmann,
``Harmonische Funktionen und Randwertaufgaben in einem Komplex,''
\emph{Commentarii Mathematici Helvetici} 17 (1944), 240--255.

\bibitem{EckartYoung1936}
C.~Eckart and G.~Young,
``The approximation of one matrix by another of lower rank,''
\emph{Psychometrika} 1 (1936), 211--218.

\bibitem{Einstein1915}
A.~Einstein,
``Die Feldgleichungen der Gravitation,''
\emph{Sitzungsberichte der K\"oniglich Preussischen Akademie der Wissenschaften zu Berlin}
(1915), 844--847.

\bibitem{Evans2010}
L.~C.~Evans,
\emph{Partial Differential Equations},
2nd ed., American Mathematical Society, Providence, RI, 2010.

\bibitem{Feshbach1958}
H.~Feshbach,
``Unified theory of nuclear reactions,''
\emph{Annals of Physics} 5 (1958), 357--390.

\bibitem{Feshbach1962}
H.~Feshbach,
``A unified theory of nuclear reactions. II,''
\emph{Annals of Physics} 19 (1962), 287--313.

\bibitem{Folland1999}
G.~B.~Folland,
\emph{Real Analysis: Modern Techniques and Their Applications},
2nd ed., Wiley, New York, 1999.

\bibitem{FultonHarris1991}
W.~Fulton and J.~Harris,
\emph{Representation Theory: A First Course},
Springer, New York, 1991.

\bibitem{Friedman1998}
J.~Friedman,
``Computing Betti numbers via combinatorial Laplacians,''
\emph{Algorithmica} 21 (1998), 331--346.

\bibitem{Goldenfeld1992}
N.~Goldenfeld,
\emph{Lectures on Phase Transitions and the Renormalization Group},
Addison-Wesley, Reading, MA, 1992.

\bibitem{GigaLasicaRybka2025}
Y.~Giga, M.~\L{}asica, and P.~Rybka,
``Mosco convergence framework for singular limits of gradient flows on Hilbert
spaces with applications,''
arXiv:2511.16486, 2025.

\bibitem{Gordon1926}
W.~Gordon,
``Der Comptoneffekt nach der Schr\"odingerschen Theorie,''
\emph{Zeitschrift f\"ur Physik} 40 (1926), 117--133.

\bibitem{Haynsworth1968}
E.~V.~Haynsworth,
``Determination of the inertia of a partitioned Hermitian matrix,''
\emph{Linear Algebra and its Applications} 1 (1968), 73--81.

\bibitem{HorakJost2013}
D.~Horak and J.~Jost,
``Spectra of combinatorial Laplace operators on simplicial complexes,''
\emph{Advances in Mathematics} 244 (2013), 303--336.

\bibitem{Jackson1999}
J.~D.~Jackson,
\emph{Classical Electrodynamics},
3rd ed., Wiley, New York, 1999.

\bibitem{Jacobson1995}
T.~Jacobson,
``Thermodynamics of spacetime: the Einstein equation of state,''
\emph{Physical Review Letters} 75 (1995), 1260--1263.

\bibitem{Kalman1963}
R.~E.~Kalman,
``Mathematical description of linear dynamical systems,''
\emph{Journal of the Society for Industrial and Applied Mathematics Series A: Control}
1 (1963), 152--192.

\bibitem{Kraft1949}
L.~G.~Kraft,
``A device for quantizing, grouping, and coding amplitude-modulated pulses,''
M.S. thesis, Department of Electrical Engineering, Massachusetts Institute of
Technology, Cambridge, MA, 1949.

\bibitem{Klein1926}
O.~Klein,
``Quantentheorie und f\"unfdimensionale Relativit\"atstheorie,''
\emph{Zeitschrift f\"ur Physik} 37 (1926), 895--906.

\bibitem{Lovelock1971}
D.~Lovelock,
``The Einstein tensor and its generalizations,''
\emph{Journal of Mathematical Physics} 12 (1971), 498--501.

\bibitem{Mallat1989}
S.~Mallat,
``A theory for multiresolution signal decomposition: the wavelet representation,''
\emph{IEEE Transactions on Pattern Analysis and Machine Intelligence} 11 (1989), 674--693.

\bibitem{Maxwell1865}
J.~C.~Maxwell,
``A dynamical theory of the electromagnetic field,''
\emph{Philosophical Transactions of the Royal Society of London} 155 (1865), 459--512.

\bibitem{mathlibCommunity2020}
The mathlib Community,
``The Lean mathematical library,''
in \emph{Proceedings of the 9th ACM SIGPLAN International Conference on Certified Programs and Proofs},
ACM, New York, 2020, pp.~367--381.

\bibitem{MartinLof1984}
P.~Martin-L\"of,
\emph{Intuitionistic Type Theory},
Bibliopolis, Naples, 1984.

\bibitem{Mori1965}
H.~Mori,
``Transport, collective motion, and Brownian motion,''
\emph{Progress of Theoretical Physics} 33 (1965), 423--455.

\bibitem{Munkres1984}
J.~R.~Munkres,
\emph{Elements of Algebraic Topology},
Addison-Wesley, Menlo Park, CA, 1984.

\bibitem{Mirsky1960}
L.~Mirsky,
``Symmetric gauge functions and unitarily invariant norms,''
\emph{The Quarterly Journal of Mathematics} 11 (1960), 50--59.

\bibitem{Navier1823}
C.-L.~Navier,
``M\'emoire sur les lois du mouvement des fluides,''
\emph{M\'emoires de l'Acad\'emie Royale des Sciences de l'Institut de France}
6 (1823), 389--440.

\bibitem{Nek5000Theory2026}
\emph{Nek5000 documentation: Theory},
\url{https://nek5000.github.io/NekDoc/theory.html},
accessed March 28, 2026.

\bibitem{Nek5000CaseFiles2026}
\emph{Nek5000 documentation: Case Files},
\url{https://nek5000.github.io/NekDoc/problem_setup/case_files.html},
accessed March 28, 2026.

\bibitem{Nek5000Filters2026}
\emph{Nek5000 documentation: Stabilizing Filters},
\url{https://nek5000.github.io/NekDoc/problem_setup/filter.html},
accessed March 28, 2026.

\bibitem{NekNekTutorial2026}
\emph{Nek5000 documentation: Overlapping Overset Grids},
\url{https://nek5000.github.io/NekDoc/tutorials/neknek.html},
accessed March 28, 2026.

\bibitem{NithiarasuCodinaZienkiewicz2006}
P.~Nithiarasu, R.~Codina, and O.~C.~Zienkiewicz,
``The Characteristic-Based Split (CBS) scheme---a unified approach to fluid dynamics,''
\emph{International Journal for Numerical Methods in Engineering} 66 (2006),
1514--1546.

\bibitem{OrnsteinWeiss2007}
D.~Ornstein and B.~Weiss,
``Entropy is the only finitely observable invariant,''
\emph{Journal of Modern Dynamics} 1 (2007), 93--105.

\bibitem{Pope2000}
S.~B.~Pope,
\emph{Turbulent Flows},
Cambridge University Press, Cambridge, 2000.

\bibitem{PeskinSchroeder1995}
M.~E.~Peskin and D.~V.~Schroeder,
\emph{An Introduction to Quantum Field Theory},
Addison-Wesley, Reading, MA, 1995.

\bibitem{ReedSimon1972}
M.~Reed and B.~Simon,
\emph{Methods of Modern Mathematical Physics. I. Functional Analysis},
Academic Press, New York, 1972.

\bibitem{Schrodinger1926}
E.~Schr\"odinger,
``Quantisierung als Eigenwertproblem,''
\emph{Annalen der Physik} 79--81 (1926), four communications.

\bibitem{Shannon1948}
C.~E.~Shannon,
``A mathematical theory of communication,''
\emph{Bell System Technical Journal} 27 (1948), 379--423, 623--656.

\bibitem{Sakurai2020}
J.~J.~Sakurai and J.~Napolitano,
\emph{Modern Quantum Mechanics},
3rd ed., Cambridge University Press, Cambridge, 2020.

\bibitem{Schwarz1995}
G.~Schwarz,
\emph{Hodge Decomposition---A Method for Solving Boundary Value Problems},
Springer, Berlin, 1995.

\bibitem{Stone1932}
M.~H.~Stone,
``On one-parameter unitary groups in Hilbert space,''
\emph{Annals of Mathematics} 33 (1932), 643--648.

\bibitem{Serre1977}
J.-P.~Serre,
\emph{Linear Representations of Finite Groups},
Springer, New York, 1977.

\bibitem{Stokes1845}
G.~G.~Stokes,
``On the theories of the internal friction of fluids in motion, and of the equilibrium and motion of elastic solids,''
\emph{Transactions of the Cambridge Philosophical Society} 8 (1845), 287--305.

\bibitem{ToobySmith2025}
J.~Tooby-Smith,
``HepLean: Digitalising high energy physics,''
\emph{Computer Physics Communications} 308 (2025), 109457.

\bibitem{Triebel1983}
H.~Triebel,
\emph{Theory of Function Spaces},
Birkh\"auser, Basel, 1983.

\bibitem{Wald1984}
R.~M.~Wald,
\emph{General Relativity},
University of Chicago Press, Chicago, 1984.

\bibitem{Warner1983}
F.~W.~Warner,
\emph{Foundations of Differentiable Manifolds and Lie Groups},
Springer, New York, 1983.

\bibitem{Wang2026TriChord}
X.~Wang,
\emph{A Minimal model for causal invariance: path merging via DP-like optimization},
software, Zenodo, version v9.1.0, 2026.
\url{https://doi.org/10.5281/zenodo.19347425}.

\bibitem{Weil1952}
A.~Weil,
``Sur les formules explicites de la th\'eorie des nombres premiers,''
in \emph{Meddelanden fr\aa n Lunds Universitets Matematiska Seminarium, Suppl\'ementband},
1952, pp.~252--265.

\bibitem{Zwanzig1961}
R.~Zwanzig,
``Memory effects in irreversible thermodynamics,''
\emph{Physical Review} 124 (1961), 983--992.

\bibitem{ZhuChristiansenHuHirani2026}
C.~Zhu, S.~H.~Christiansen, K.~Hu, and A.~N.~Hirani,
``Convergence and Stability of Discrete Exterior Calculus for the Hodge
Laplace Problem in Two Dimensions,''
arXiv:2505.08966, 2025.

\bibitem{Zhang2005}
F.~Zhang,
\emph{The Schur Complement and Its Applications},
Springer, New York, 2005.

\end{thebibliography}
